### 2023-11-13 index.qmd
Completed writing the R script (but not finishing annotations)

---
title: "Graded Response Model: A tutorial"
author: "Rizqy Amelia Zein, Hanif Akhtar"
format: html
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2023-11-13 codes.R

@@ -1,0 +1,245 @@
+# Tutorial on running a Graded Response Model, initiated on 09.11.2023
+# by Rizqy Amelia Zein and Hanif Akhtar
+# LMU Munich, Universitas Airlangga (UNAIR), ELTE Eötvös Loránd University, and Universitas Muhammadiyah Malang (UMM)
+
+
+# Welcome to the tutorial!  ------
+# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
+# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
+# examining the performance of a scale with polytomous responses (Likert-type scale).
+
+# To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
+# the right-wing authoritarianism (RWA) scale (Altemeyer). 
+
+
+## Step 1: Install and activate the packages ##  ------
+
+# First of all, we should install the packages we need for the analysis. If you already have these packages  
+# already installed in your device, you can safely skip this step.
+
+# install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
+## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
+
+# package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
+
+devtools::install_github("masurp/ggmirt")
+
+# Now, we activate the package:
+
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+
+## Step 2: Downloading, storing, and preparing the data for analysis ##   ------
+
+# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
+# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
+
+url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
+
+# If you look closely at the .zip folder, there are two files in there; one is a .csv file (this is the dataset),
+# and two, a .txt file (a codebook). Since we need them both, we will extract them and make them readable in R environment.
+
+zip_file_path <- tempfile(fileext = ".zip") # Defining the path to temporarily save the downloaded zip file
+download.file(url, zip_file_path, mode = "wb") # Downloading the zip file
+extracted_files_path <- tempdir() # Defining the path to extract the contents of the zip file
[…]

### 2023-11-14 paper.qmd
R script almost done and Quarto paper is started

---
title: "Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R"
shorttitle: "Graded Response Model Tutorial"
author:
  - name: Rizqy Amelia Zein
    corresponding: true
    orcid: "0000-0001-7840-0299"
    email: "Amelia.Zein@psy.lmu.de"
    affiliations:
      - name: "Ludwig-Maximilians-Universität"
        department: "Psychology"
        address: "Leopoldstraße 13"
        city: "Munich"
        country: "Germany"
        postal-code: "80802"
      - name: "Universitas Airlangga"
        department: "Psychology"
        address: "Jalan Airlangga 4-6"
        city: "Surabaya"
        region: "Jawa Timur"
        country: "Indonesia"
        postal-code: "60286"
  - name: "Hanif Akhtar"
    affiliations:
      - name: "ELTE Eötvös Loránd University"
        department: "Psychology"
        country: "Hungary"
      - name: "Universitas Muhammadiyah Malang"
        department: "Psychology"
        city: "Malang"
        region: "Jawa Timur"
        country: "Indonesia"
abstract: "This tutorial paper introduces the Graded Response Model (GRM), a tool for testing measurement precision under the Item Response Theory (IRT) paradigm. Addressing common problems of measurement imprecision and lack of construct validity, the tutorial guides researchers through a one-dimensional GRM analysis in the R environment, using psych, mirt, and ggmirt packages. GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous items. The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, model fitting, interpretation of results, and dealing with common issues and anomalies that may typically arise in the process."
keywords:
  - graded response model
  - item response theory
  - mirt
  - ggmirt
  - psych
  - R
author-note:
  disclosures:
    conflict-of-interest: "We declare we have no competing interests."
    financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD)."
lang: en
bibliography: references.bib
format:
  apaquarto-docx: default
editor: visual
---

{{< include _extensions/wjschne/apaquarto/_apa_title.qmd >}}

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2023-11-14 paper.tex
R script almost done and Quarto paper is started

\documentclass[
  man,
  a4paper,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

\makeatletter\makeatother\makeatletter\makeatother\makeatletter\@ifpackageloaded{caption}{}{\usepackage{caption}}\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}\makeatother\makeatletter\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}\makeatother\makeatletter\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}\makeatother\makeatletter\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}\makeatother\makeatletter\makeatother\makeatletter\makeatother

% \usepackage[style=apa,backend=biber]{biblatex}
% % \addbibresource{references.bib}
%

\title{Getting Started with the Graded Response Model (GRM): A gentle
introduction and tutorial in R}
\shorttitle{Graded Response Model Tutorial}

\authorsnames[{1},{1}]{
Ana Fulana,Blanca Zutana
}

\authorsaffiliations{
{Department of Psychology, Ludwig-Maximilians-Universität München,
Munich, Germany}}

\date{}
\abstract{Lorem ipsum dolor sit amet, consectetur adipisici elit, sed
eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad
minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid
ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit
esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat
cupiditat non proident, sunt in culpa qui officia deserunt mollit anim
id est laborum.}
% % \addbibresource{references.bib}
% 
\keywords{meta science, replication, multiverse analysis}

\authornote{\par{\addORCIDlink{Ana Fulana}{0000-0000-0000-0000}}
\par{ }
\par{This study was preregistered at OSF at \ldots. Code and data of
this study are available at \ldots{} This article is based on data
published in \ldots{} We declare we have no competing interests. This
research was funded by the German Research Foundation (DFG SCHO \ldots,
Blanca Zutana). We would like to thank Carina Mengana and Dolorita
Perengana for their very helpful comments and discussions on this
project. Because the authors are equal contributors, order of authorship
was determined by a fair coin
toss.  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: \emph{Ana
Fulana}: Conceptualization, Writing - original draft; \emph{Blanca
Zutana}: Project administration}
\par{Correspondence concerning this article should be addressed to Ana
Fulana, Email: sm@example.org}
}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi
\hypertarget{quarto}{%
\subsection{Quarto}\label{quarto}}

Quarto enables you to weave together content and executable code into a
finished document. To learn more about Quarto see
\url{https://quarto.org}.

\hypertarget{running-code}{%
\subsection{Running Code}\label{running-code}}

When you click the \textbf{Render} button a document will be generated
that includes both content and the output of embedded code. You can
embed code like this:

\begin{verbatim}
[1] 2
\end{verbatim}

You can add options to executable code like this

\begin{verbatim}
[1] 4
\end{verbatim}

The \texttt{echo:\ false} option disables the printing of code (only
output is displayed).

\end{document}

### 2023-11-14 codes.R

@@ -20,7 +20,7 @@
 # install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
 ## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
 
-# package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
+# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
 
 devtools::install_github("masurp/ggmirt")
 
@@ -38,30 +38,30 @@ url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of t
 # If you look closely at the .zip folder, there are two files in there; one is a .csv file (this is the dataset),
 # and two, a .txt file (a codebook). Since we need them both, we will extract them and make them readable in R environment.
 
-zip_file_path <- tempfile(fileext = ".zip") # Defining the path to temporarily save the downloaded zip file
-download.file(url, zip_file_path, mode = "wb") # Downloading the zip file
-extracted_files_path <- tempdir() # Defining the path to extract the contents of the zip file
-unzip(zip_file_path, exdir = extracted_files_path) # Unzipping the .zip file
-files <- list.files(extracted_files_path, recursive = TRUE, full.names = TRUE) # List all the files in the extracted directory, including subdirectories
+zip <- tempfile(fileext = ".zip") # Defining the path to temporarily save the downloaded zip file
+download.file(url, zip, mode = "wb") # Downloading the zip file
+do <- tempdir() # Defining the path to extract the contents of the zip file
+unzip(zip, exdir = do) # Unzipping the .zip file
+files <- list.files(do, recursive = TRUE, full.names = TRUE) # List all the files in the extracted directory, including subdirectories
 
-csv_files <- grep("\\.csv$", files, value = TRUE) # Filtering for .csv files
-txt_files <- grep("\\.txt$", files, value = TRUE) # Filtering for .txt files
+csv <- grep("\\.csv$", files, value = TRUE) # Filtering for .csv files
+txt <- grep("\\.txt$", files, value = TRUE) # Filtering for .txt files
 
 
-if (length(csv_files) == 0) {
-  stop("No .csv files found in the zip archive.")
+if (length(csv) == 0) {
+  stop("no .csv found")
 } # now checking if there are any .csv files, and if that's the case, the script gives no error message
[…]

### 2023-11-15 paper.qmd
R script finished!

@@
     corresponding: true
-    orcid: "0000-0001-7840-0299"
-    email: "Amelia.Zein@psy.lmu.de"
+    orcid: 0000-0001-7840-0299
+    email: Amelia.Zein@psy.lmu.de
     affiliations:
-      - name: "Ludwig-Maximilians-Universität"
-        department: "Psychology"
-        address: "Leopoldstraße 13"
-        city: "Munich"
-        country: "Germany"
+      - name: Ludwig-Maximilians-Universität
+        department: Department of Psychology
+        address: Leopoldstraße 13
+        city: Munich
         postal-code: "80802"
-      - name: "Universitas Airlangga"
-        department: "Psychology"
-        address: "Jalan Airlangga 4-6"
-        city: "Surabaya"
-        region: "Jawa Timur"
-        country: "Indonesia"
+      - name: Universitas Airlangga
+        department: Department of Psychology
+        address: Jalan Airlangga 4-6
+        city: Surabaya
+        region: Jawa Timur, Indonesia
         postal-code: "60286"
-  - name: "Hanif Akhtar"
+  - name: Hanif Akhtar
+    orcid: 0000-0002-1388-7347
     affiliations:
-      - name: "ELTE Eötvös Loránd University"
-        department: "Psychology"
-        country: "Hungary"
-      - name: "Universitas Muhammadiyah Malang"
-        department: "Psychology"
-        city: "Malang"
-        region: "Jawa Timur"
-        country: "Indonesia"
+      - name: ELTE Eötvös Loránd University
+        department: Doctoral School of Psychology
+        country: Hungary
+      - name: Universitas Muhammadiyah Malang
+        department: Faculty of Psychology
+        city: Malang
+        region: Jawa Timur, Indonesia
 abstract: "This tutorial paper introduces the Graded Response Model (GRM), a tool for testing measurement precision under the Item Response Theory (IRT) paradigm.
@@
 The `echo: false` option disables the printing of code (only output is displayed).
+
+# References
+
+::: {#refs}
+:::

### 2023-11-15 codes.R

@@ -2,7 +2,6 @@
 # by Rizqy Amelia Zein and Hanif Akhtar
 # LMU Munich, Universitas Airlangga (UNAIR), ELTE Eötvös Loránd University, and Universitas Muhammadiyah Malang (UMM)
 
-
 # Welcome to the tutorial!  ------
 # This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
 # or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
@@ -187,8 +186,7 @@ model <- 'rwa = 1-22' # This script means that our model consists of a latent fa
 # and consists of 22 items (column 1 to column 22).
 
 # Now, we estimate our model...
-fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F) # This script means we're running a GRM analysis 
-# assuming that the RWA scale as a unidimensional construct 
+fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F) # This script means we're running a GRM analysis by assuming that the RWA scale as a unidimensional construct 
 
 # ...and store the model parameters in a data frame.
 coefs <- coef(fit, IRTpars=T, printSE=T) # Storing model parameters in a data frame.
@@ -223,7 +221,7 @@ itemfit(fit) # Yielding item fit statistics.
 # It could be a problem of model misspecification, or something else. We can identify potential problems by
 # looking at local dependency statistics (Step 6) and the plots (Step 7).
 
-## Step 6: Testing local independence assumption (again) using different strategies (local dependency statistics) ##  ------
+## Step 6: Probing model misspecification by examining residuals ##  ------
 
 # While we have evidence that the RWA scale is unidimensional, our model does not fit well with the data.
 # Therefore, let's examine the possibility of model misspecification by looking at model residuals. 
@@ -251,29 +249,56 @@ q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics
 findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlation pairs.
 # As we see here in the console that items Q4, Q5, Q6, Q7, Q11, Q13, Q14, Q15, Q18, Q19, Q21, Q22 are problematic.
 
-## Step 7: Plots (category probability function, item information function, and test information function) ##   ------
+## Step 7: Plots (item characteristics curve, item information curve, and test information curve) ##   ------
 
 # From the previous step, we found some problems with model misspecification. 
[…]

### 2023-11-15 paper.qmd
quarto paper initiated

@@
 
-## Quarto
+```{r, echo=F, include=F}
+#| label: setup
+#| install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
+#| INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+#| devtools::install_github("masurp/ggmirt")
 
-## Running Code
+#| Now, we activate the package:
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
 
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r}
-1 + 1
 ```
 
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
-```
-
-The `echo: false` option disables the printing of code (only output is displayed).
+{{< pagebreak >}}
 

### 2023-11-15 draft_paper.qmd
first attempt rendering the Quarto file (manuscript draft)

--- 2023-11-15 paper.qmd
@@
 #| label: setup
-#| install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
-#| INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
-
-#| devtools::install_github("masurp/ggmirt")
-
-#| Now, we activate the package:
+# install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
+# INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed)
+# devtools::install_github("masurp/ggmirt")
+# Now, we activate the package:
 library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)

### 2023-11-15 draft_paper.qmd
revising number of steps in R script

@@
 title: "Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R"
-shorttitle: "Graded Response Model Tutorial"
+shorttitle: "A Graded Response Model Tutorial"
 author:
@@
 library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+ds <- read.csv("data/data.csv")
 

### 2023-11-15 codes.R

@@ -11,7 +11,7 @@
 # the right-wing authoritarianism (RWA) scale (Altemeyer). 
 
 
-## Step 1: Install and activate the packages ##  ------
+## Step 1a: Preparation - Install and activate the packages ##  ------
 
 # First of all, we should install the packages we need for the analysis. If you already have these packages  
 # already installed in your device, you can safely skip this step.
@@ -27,7 +27,7 @@ devtools::install_github("masurp/ggmirt")
 
 library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
 
-## Step 2: Downloading, storing, and preparing the data for analysis ##   ------
+## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
 
 # Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
 # download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
@@ -78,7 +78,7 @@ rwa <- subset(ds, select = Q1:Q22) # now we subset our data because we are only 
 # Now let's check the structure of our new data frame containing only RWA items.
 str(rwa)
 
-## Step 3: Inspecting key descriptive statistics ##   ------
+## Step 2: Inspecting key descriptive statistics ##   ------
 
 # This part is fairly straightforward. Before performing analysis, it is very important to explore
 # key descriptive statistics of the data. We are using a neat function in `psych` package: (`describe()`)
@@ -126,7 +126,7 @@ psych::describe(rwa)
 # unclear what "0" means (it is safer to assume that it a code for missing responses) and we still 
 # have a sizeable sample (>1000), let's proceed to the next step! 
 
-## Step 4: Examining dimensionality ##  ------
+## Step 3: Examining dimensionality ##  ------
 
 # While now it is computationally possible to run a multidimensional IRT analysis, in general, an IRT model assumes
 # that the items are locally independent. 
@@ -177,7 +177,7 @@ pa$fa.values # Seeing the eigenvalues of each factor.
 # Again, from the plot and the Eigenvalues (11.68/1.18), we can conclude that one latent factor is sufficient, 
 # further substantiates our unidimensionality assumption.
 
-## Step 5: Model estimation, parameters, and fit statistics ##  ------
+## Step 4: Model estimation, parameters, and fit statistics ##  ------
 
 # Now we have evidence that the scale is unidimensional, now it is the time to estimate our model.
[…]

### 2023-11-15 draft_paper.qmd
Paper draft is now with an outline

@@
 
+Measurement lays an important foundation of psychological science.
+
+# A Brief Overview of Item Response Theory
+
+# Graded Response Model
+
+# Assumptions and Key Concepts
+
+# An Illustrative Example of Graded Response Model: The Right Wing Authoritarianism (RWA) Scale
+## A Brief Overview of the Altemeyer's RWA Scale
+## Step 1: Preparation
+## Step 2: Inspecting Key Descriptive Statistics
+## Step 3: Examining Dimensionality
+## Step 4: Model Estimation, Parameters, and Fit Statistics
+## Step 5: Model Residuals
+## Step 6: IRT Plots
+## Step 7: Computing Reliability
+
+# Conclusions
+
 {{< pagebreak >}}

### 2023-11-15 codes.R

@@ -271,7 +271,7 @@ itemInfoPlot(fit, facet=T, theta_range = c(-6,6), title = "Item Information Curv
 testInfoPlot(fit, title="Test Information Curve of the RWA Scale")
 # Apparently, the RWA scale is informative to measure participants with theta levels between -3SD to +2SD.
 
-## Step 7: Estimating reliability ##   ------
+## Step 7: Computing reliability ##   ------
 
 # At last, we want to examine the reliability of the RWA scale. In IRT, there are two ways to estimate reliability,
 # which are: marginal and empirical reliability.

### 2023-11-15 codes.R
small corrections to the script by adding more context to unidimensionality check

@@ -129,7 +129,7 @@ psych::describe(rwa)
 ## Step 3: Examining dimensionality ##  ------
 
 # While now it is computationally possible to run a multidimensional IRT analysis, in general, an IRT model assumes
-# that the items are locally independent. 
+# that the scale is unidimensional. 
 # Bob Altemeyer (1996) argues in his book that while the RWA scale consists of three sub-dimensions,
 # which are submissiveness, aggression, and conventionalism, the RWA scale is essentially unidimensional because these 
 # three sub-dimensions are strongly intercorrelated.
@@ -223,11 +223,12 @@ itemfit(fit) # Yielding item fit statistics.
 
 ## Step 5: Probing model misspecification by examining residuals ##  ------
 
-# While we have evidence that the RWA scale is unidimensional, our model does not fit well with the data.
-# Therefore, let's examine the possibility of model misspecification by looking at model residuals. 
+# While we have evidence that the RWA scale is unidimensional, our model does not fit well with the data. Therefore,
+# it is reasonable to suspect that our model is locally dependent, thus violating IRT assumption.
+
+# We will then further examine the possibility of model misspecification by looking at model residuals. 
 # In this tutorial, we will introduce two ways to examine residuals. First, we will inspect a local dependence 
-# matrix derived from the X2 statistics (Chen & Thissen, 1997), and second, we will look at Yen's Q3
-# statistics. 
+# matrix derived from the X2 statistics (Chen & Thissen, 1997), and second, we will look at Yen's Q3 statistics. 
 
 ld <- residuals(fit, type = "LD") # Running local dependency statistics
 up <- which(upper.tri(ld), arr.ind = T) # Extracting values only on the upper side of the diagonal.

### 2023-11-15 codes.R
A few corrections to the R script

@@ -10,7 +10,6 @@
 # To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
 # the right-wing authoritarianism (RWA) scale (Altemeyer). 
 
-
 ## Step 1a: Preparation - Install and activate the packages ##  ------
 
 # First of all, we should install the packages we need for the analysis. If you already have these packages  
@@ -55,8 +54,8 @@ if (length(txt) == 0) {
   stop("no .txt found")
 } # do the same thing for .txt file
 
-ds <- read.csv(csv[1]) # Read the .csv file into a data frame
-codebook <- readLines(txt[1]) # Read the .txt file into R
+ds <- read.csv(csv[1]) # Importing the .csv file.
+codebook <- readLines(txt[1]) # Importing the .txt file.
 
 unlink(zip)
 unlink(do, recursive = TRUE)
@@ -102,20 +101,20 @@ psych::describe(rwa)
 
 # Let's count how many "0" we have in our data.
 
-zero <- colSums(rwa == 0) / nrow(rwa) # Counting the frequency of "0" in each column.
+zero <- colSums(rwa == 0) / nrow(rwa) # Computing the frequency of "0" in each column.
 print(zero) # The proportion of "0" for each item.
-rm(zero) # Removing the longer needed vector
+rm(zero) # Removing the unused vector
 
 # We have a significant proportion of "0" in several items (Q4, Q6, Q9, Q11, and Q18). 
-# There is no explanation what "0" means, but it is very possible that "0" is used to code a missing response.
+# There is no explanation what "0" means in the codebook, but it is very possible that "0" is used to code a missing response.
 # It is actually still possible to run an IRT analysis with missing data, but we have to ensure that the data are missing
 # at random (MAR). However, with the proportion of missing responses even exceeds 60% for some items,
 # we don't think it's plausible to assume MAR. One solution for this is simply exclude all cases with missing responses.
 # Let's assume then that "0" means missing response, and then delete all cases with missing responses.
 
 rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Replace 0 with NA in all columns.
-  drop_na()  # Remove rows with any NA values.
+  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
+  drop_na()  # Removing cases with any NA values.
 
 # Then let's check our data again.
 psych::describe(rwa)
[…]

### 2023-11-17 codes.R
Minor revisions of the R script

@@ -143,34 +143,35 @@ irt.fa(rwa, nfactors = 1, fm = "minres")
 
 # Alternatively, we can run a parallel analysis also with a polychoric correlation matrix. This approach
 # is, in general, better than EFA because a parallel analysis compares Eigenvalues (a scalar which measures the amount
-# of variance that is accounted for by each latent factor) from a set of simulated data.
+# of variance that is accounted for by each latent factor) from a set of simulated data with Eigenvalues of our data.
 # Again, to perform this, we need to run a simple command:
 
 fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa", cor = "poly")
 
-# However, as we see in the console, there is an error message which tells us that R stopped the analysis.
+# However, as we see in the console, there is an error message telling us that R stopped the analysis.
 # This is because performing parallel analysis or EFA using a polychoric correlation matrix is not needed when we have
 # more than 8 categories (responses) in our scale. This means we can treat our data as continuous (instead of ordinal). 
 # The RWA scale has nine responses so let's do EFA and parallel analysis using a pearson correlation matrix instead.
 
-cor <- cor(rwa,method="pearson") # First, creating cor matrix.
+cor <- cor(rwa,method="pearson") # First, creating a (pearson) correlation matrix.
 efa <- fa(rwa, nfactors=1, fm="minres") # Now, running exploratory factor analysis. 
-# Here, we use minimum residuals (minres) algorithm extract/identify latent factors because it is considered suitable for
+# Here, we use minimum residuals (minres) algorithm to extract/identify latent factors because it is considered suitable for
 # dealing with non-normally distributed data.
 print(efa) # Print the results.
 
-# Let's look at the output. MR1 reflects factor loadings of each item. As we see, all items are strongly loaded to 
+# Let's look at the output. 
+# MR1 reflects factor loadings of each item. As we see, all items are strongly loaded to 
 # the single factor. The rule of thumb is 0.3, and we can see here all the loadings are more than 0.3.
-# We also see that the proportion of total variance that is explained by the factor (see "Proportion Var") shows 0.55,
-# this means that the factor accounts for a significant portion (55%) of the variance of the data.
+# We also see that the proportion of total variance that is explained by the factor (see "Proportion Var") shows 0.53,
[…]

### 2023-11-17 codes.R
A tiny correction of the R script

@@ -191,7 +191,7 @@ model <- 'rwa = 1-22' # This script means that our model consists of a latent fa
 fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F) # This script means we're running a GRM analysis by assuming that the RWA scale as a unidimensional construct 
 
 # ...and store the model parameters in a data frame.
-coefs <- coef(fit, IRTpars=T, printSE=T, simplify=T) # Storing model parameters in a data frame.
+coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
 
 # Let's take a look at the model parameters!
 print(coefs) # Yielding model parameters: item discriminations (a) and threshold (b).

### 2023-11-23 draft_paper.qmd
Total overhaul of the R script. I used a wrong formula to reverse unfav items.

--- 2023-11-15 draft_paper.qmd
@@
     orcid: 0000-0001-7840-0299
-    email: Amelia.Zein@psy.lmu.de
+    email: amelia.zein@psikologi.unair.ac.id
     affiliations:
-      - name: Ludwig-Maximilians-Universität
-        department: Department of Psychology
-        address: Leopoldstraße 13
-        city: Munich
-        postal-code: "80802"
       - name: Universitas Airlangga
@@
         postal-code: "60286"
+      - name: Ludwig-Maximilians-Universität
+        department: Department of Psychology
+        address: Leopoldstraße 13
+        city: Munich
+        postal-code: "80802"
   - name: Hanif Akhtar
@@
 editor: visual
+execute: 
+  warning: false
+  error: false
+  output: false
+  echo: true
 ---
@@
 
-```{r, echo=F, include=F}
-#| label: setup
-# install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
+```{r}
+#| include: false
+#| label: "setup"
+
+# install.packages("flextable", dependencies=TRUE) 
 # INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed)
-# devtools::install_github("masurp/ggmirt")
-# Now, we activate the package:
-library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+library(flextable)
 
 ```
+
+Measurement, undoubtedly, is an important foundation of scientific research. Measurement process start with defining the construct being studied and then determine the assumptions
+
+# A Brief Overview of Item Response Theory
+
+# Graded Response Model
+
+# Assumptions and Key Concepts
+
+# Disclosure
+
+To maximise reproducibility of our analysis, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
+We also include the complete R script for the example we used as a supplementary document.
+The Quarto file (and its corresponding .docx and .pdf output) and R script are publicly available on (a Github repository)\[https://github.com/rameliaz/grm-tutorial-paper\].
+
+# An Illustrative Example of Graded Response Model: The Right Wing Authoritarianism (RWA) Scale
+
+To demonstrate the procedure of running a graded response model, we
+
+## A Brief Overview of the Altemeyer's RWA Scale
+
+## Step 1: Preparation
+
+```{r}
+
+install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE)
+library(tidyverse); library(psych); library(mirt); library(caret)
+```
+
+Blabla
+
+```{r}
+
+# devtools::install_github("masurp/ggmirt")
+library(ggmirt)
+```
+
+Blabla
+
+```{r}
+ds <- read.csv("data/data.csv")
+```
+
+Blabla
+
+```{r}
+str(ds)
+```
+
+Blabla
+
+```{r}
+rwa <- subset(ds, select = Q1:Q22)
+str(rwa)
+```
+
+Blabla
+
+## Step 2: Inspecting Key Descriptive Statistics
+
+```{r}
+psych::describe(rwa)
+```
+
+As we see in {apatb-table1}, nddasjdhajskdhaks
+
+```{r}
+unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
+rwa <- rwa %>% 
+  mutate(across(all_of(unfav), ~ 9 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
+```
+
+Kok ada nilai 0-nya? padahal kan skor minimalnya 1. Coba kita hitung frekuensi nilai 0 di tiap item.
+
+```{r}
+zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the frequency of "0" in each column.
+print(zero) # The proportion of "0" for each item.
+```
+
+```{r}
+rwa <- rwa %>%
+  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
+  drop_na()  # Removing cases with any NA values.
+```
+
+Now let's look again at the descriptive statistics after we removed all NA cases.
+
+```{r}
+psych::describe(rwa)
+```
+
+## Step 3: Examining Dimensionality
+
+```{r}
+#| eval: false
+
+irt.fa(rwa, nfactors = 1, fm = "minres")
+```
+
+```{r}
+#| eval: false
+
+fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa", cor = "poly")
+```
+
+```{r}
+cor <- cor(rwa,method="pearson") # First, creating a (pearson) correlation matrix.
+efa <- fa(rwa, nfactors=1, fm="minres") # Now, running exploratory factor analysis. 
+print(efa) # Print the results.
+```
+
+Scree plot
+
+Now lets do parallel analysis
+
+```{r}
+pa <- fa.parallel(rwa, fm="minres", fa="fa") # Running a parallel analysis.
+pa$fa.values # Seeing the eigenvalues of each factor.
+```
+
+## Step 4: Model Estimation, Parameters, and Fit Statistics
+
+```{r}
+model <- 'rwa = 1-22'
+```
+
+```{r}
+fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F)
+```
+
+```{r}
+coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
+print(coefs) # Yielding model parameters: item discriminations (a) and threshold (b).
+```
+
+```{r}
+summary(fit)
+```
+
+lhalalala
+
+```{r}
+M2(fit, type="C2")
+```
+
+lhalalala
+
+```{r}
+#| include: false
+
+m2_results <- M2(fit, type="C2")
+m2_stat <- m2_results$M2
+df <- m2_results$df
+p_value <- m2_results$p.value
+rmsea <- m2_results$RMSEA
+srmr <- m2_results$SRMR
+tli <- m2_results$TLI
+cfi <- m2_results$CFI
+```
+
+According to our analysis, the model does not fit the data well (*M*(`r df`) = `r m2_stat`, *p* = `r p_value`, *RMSEA* = `r rmsea`, )
+
+```{r}
+item.fit <- itemfit(fit)
+```
+
+## Step 5: Model Residuals
+
+```{r}
+ld <- residuals(fit, type = "LD") # Running local dependency statistics
+up <- which(upper.tri(ld), arr.ind = T) # Extracting values only on the upper side of the diagonal.
+lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # Defining unusually large residuals (>0.2).
+```
+
+lhalalala
+
+```{r}
+for (i in 1:nrow(lar)) {
+  row <- lar[i, 1]
+  col <- lar[i, 2]
+  value <- ld[row, col]
+  cat(sprintf("A large residual correlation is found between item %d and item %d: %f\n", row, col, value))
+} # Now we detect the problematic pairs.
+```
+
+lhalalala
+
+```{r}
+q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics
+findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlation pairs.
+```
+
+## Step 6: IRT Plots
+
+Now spit out the
+
+```{r}
+tracePlot(fit, facet=T, title = "Category Probability Functions of RWA Scale") + labs(color="Response Options")
+```
+
+lhalalala
+
+```{r}
+itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
+```
+
+lhalalala
+
+```{r}
+#| output: false
+
+itemInfoPlot(fit, facet=T, theta_range = c(-6,6), title = "Item Information Curves of the RWA Scale")#
+```
+
+lhalalala
+
+```{r}
+testInfoPlot(fit, title="Test Information Curve of the RWA Scale")
+```
+
+## Step 7: Computing Reliability
+
+```{r}
+theta_se <- fscores(fit, full.scores.SE = T) # Extracting the estimated theta score of each participant.
+e_rel <- empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
+```
+
+lhalalala
+
+```{r}
+m_rel <- marginal_rxx(fit)
+```
+
+lhalalala
+
+```{r}
+omega(rwa)
+```
+
+# Conclusions
 
@@
 :::
+
+{{< pagebreak >}}
+
+```{r apatb-table1}
+#| output: true
+#| echo: false
+#| apa-cap: Descriptive Statistics of RWA Scale
+#| apa-note: SD = Standard Deviation
+#| ft.align: left
+
+# Transforming describe() output into a APA-formatted table
+table1 <- psych::describe(rwa); table1 <- as.data.frame(table1)
+table1 <- table1 %>% 
+  rownames_to_column(var="Item") %>% 
+  select(Item, mean, sd, min, max, range, n) %>% 
+  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
+  flextable() %>%
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table1 <- colformat_double(x=table1, j="Minimum", digits = 0)
+table1 <- colformat_double(x=table1, j="Maximum", digits = 0)
+table1 <- colformat_double(x=table1, j="Range", digits = 0)
+table1 <- colformat_double(x=table1, j="n", digits = 0)
+
+table1
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table2}
+#| output: true
+#| echo: false
+#| apa-cap: Descriptive Statistics of RWA Scale
+#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| ft.align: left
+
+# Transforming describe() output into a APA-formatted table
+unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
+rwa <- rwa %>% 
+  mutate(across(all_of(unfav), ~ 9 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
+
+table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
+table2 <- table2 %>% 
+  rownames_to_column(var="Item") %>% 
+  select(Item, mean, sd, min, max, range, n) %>% 
+  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
+  flextable() %>% 
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
+table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
+table2 <- colformat_double(x=table2, j="Range", digits = 0)
+table2 <- colformat_double(x=table2, j="n", digits = 0)
+
+table2
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table3}
+#| output: true
+#| echo: false
+#| apa-cap: Percentge of Zero in Each Item
+#| ft.align: left
+
+table3 <- as.data.frame(zero)
+
+table3 <- table3 %>% 
+  rownames_to_column(var="Item") %>% 
+  select(Item, zero) %>% 
+  rename(Percentage=zero) %>% 
+  flextable() %>% 
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table3
+
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table4}
+#| output: true
+#| echo: false
+#| apa-cap: Descriptive Statistics of RWA Scale
+#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| ft.align: left
+
+rwa <- rwa %>%
+  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
+  drop_na()  # Removing cases with any NA values.
+
+# Transforming describe() output into a APA-formatted table
+table4 <- psych::describe(rwa); table4 <- as.data.frame(table4)
+table4 <- table4 %>% 
+  rownames_to_column(var="Item") %>% 
+  select(Item, mean, sd, min, max, range, n) %>% 
+  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
+  flextable() %>% 
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table4 <- colformat_double(x=table4, j="Minimum", digits = 0)
+table4 <- colformat_double(x=table4, j="Maximum", digits = 0)
+table4 <- colformat_double(x=table4, j="Range", digits = 0)
+table4 <- colformat_double(x=table4, j="n", digits = 0)
+
+table4
+```
+
+{{< pagebreak >}}
+
+```{r fig1}
+#| output: true
+#| echo: false
+#| label: apafg-fig1
+#| apa-cap: Scree Plot
+#| apa-note: NULL
+
+plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
+abline(h = 1, col = "red", lty = 2) # Add new line to factor 1.
+
+```
+
+{{< pagebreak >}}
+
+```{r fig2}
+#| output: true
+#| echo: false
+#| label: apafg-fig2
+#| apa-cap: Parallel Analysis
+#| apa-note: NULL
+
+plot(pa)
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table5}
+#| output: true
+#| echo: false
+#| apa-cap:  Descriptive Statistics of RWA Scale
+#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| ft.align: left
+
+table5 <- as.data.frame(coefs$items)
+
+table5 <- table5 %>% 
+  rownames_to_column(var="Item") %>% 
+  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8) %>% 
+  rename(α=a, β1=b1, β2=b2, β3=b3, β4=b4, β5=b5, β6=b6, β7=b7, β8=b8) %>% 
+  flextable() %>% 
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table5 <- colformat_double(x=table5, j="α", digits = 2)
+table5 <- colformat_double(x=table5, j="β1", digits = 2)
+table5 <- colformat_double(x=table5, j="β2", digits = 2)
+table5 <- colformat_double(x=table5, j="β3", digits = 2)
+table5 <- colformat_double(x=table5, j="β4", digits = 2)
+table5 <- colformat_double(x=table5, j="β5", digits = 2)
+table5 <- colformat_double(x=table5, j="β6", digits = 2)
+table5 <- colformat_double(x=table5, j="β7", digits = 2)
+table5 <- colformat_double(x=table5, j="β8", digits = 2)
+
+table5
+
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table6}
+#| output: true
+#| echo: false
+#| apa-cap: Descriptive Statistics of RWA Scale
+#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| ft.align: left
+
+table6 <- as.data.frame(item.fit)
+
+table6 <- table6 %>%
+  select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
+  rename(Item=item) %>% 
+  flextable() %>% 
+  theme_apa() %>% 
+  line_spacing(part = "all") %>% 
+  padding(padding.top = 5, padding.bottom = 5)
+
+table6 <- colformat_double(x=table6, j="S_X2", digits = 2)
+table6 <- colformat_double(x=table6, j="df.S_X2", digits = 2)
+table6 <- colformat_double(x=table6, j="RMSEA.S_X2", digits = 2)
+table6 <- colformat_double(x=table6, j="p.S_X2", digits = 2)
+
+table6
+
+```
+
+{{< pagebreak >}}
+
+```{r fig3}
+#| output: true
+#| echo: false
+#| label: apafg-fig3
+#| apa-cap: Category Probability Functions of RWA Scale
+#| apa-note: NULL
+
+tracePlot(fit, facet=T, title = "Category Probability Functions of RWA Scale") + labs(color="Response Options")
+```
+
+{{< pagebreak >}}
+
+```{r fig4}
+#| output: true
+#| echo: false
+#| label: apafg-fig4
+#| apa-cap: Item Information Curves of the RWA Scale
+#| apa-note: NULL
+
+itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
+```
+
+{{< pagebreak >}}
+
+```{r fig5}
+#| output: true
+#| echo: false
+#| label: apafg-fig5
+#| apa-cap:  Item Information Curves of the RWA Scale Ranging from -6 to +6 Standard Deviation
+#| apa-note: NULL
+
+itemInfoPlot(fit, facet=T, theta_range = c(-6,6), title = "Item Information Curves of the RWA Scale")#
+```
+
+{{< pagebreak >}}
+
+```{r fig6}
+#| output: true
+#| echo: false
+#| label: apafg-fig6
+#| apa-cap: Test Information Curve of the RWA Scale
+#| apa-note: NULL
+
+testInfoPlot(fit, title="Test Information Curve of the RWA Scale")
+```
+
+{{< pagebreak >}}
+
+```{r fig7}
+#| output: true
+#| echo: false
+#| label: apafg-fig7
+#| apa-cap: Reliability of the RWA Scale Given to the θ Level
+#| apa-note: NULL
+
+conRelPlot(fit, title="Reliability of the RWA Scale Given to the θ Level")
+```

### 2023-11-23 codes.R

@@ -83,6 +83,26 @@ str(rwa)
 # key descriptive statistics of the data. We are using a neat function in `psych` package: (`describe()`)
 
 psych::describe(rwa)
+# Why there are "0" values in all columns (see column "min")?
+# The items are not supposed to have "0" value because the responses are ranging from 1-9.
+
+# Let's count how many "0" we have in our data.
+
+zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the frequency of "0" in each column.
+print(zero) # The proportion of "0" for each item.
+rm(zero) # Removing the unused vector
+
+# We have a few cases with "0" in all items. 
+# There is no explanation what "0" means in the codebook, but it is very possible that "0" is used to code a missing response.
+# It is actually still possible to run an IRT analysis with missing data, but we have to ensure that the data are missing
+# at random (MAR). One solution for this is simply exclude all cases with missing responses.
+# Let's assume then that "0" means missing response, and then delete all cases with missing responses.
+
+rwa <- rwa %>%
+  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
+  drop_na()  # Removing cases with any NA values.
+
+psych::describe(rwa)
 # As we see here in the console, mean score of the items differ - some items have small mean scores (~2-3), while the
 # others are quite large (~6-7). The reason for this is that the RWA scale has unfavorable items 
 # so to simplify the interpretation, we should reverse their scores.
@@ -91,39 +111,18 @@ psych::describe(rwa)
 
 unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
 rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 9 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
+  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 
+# to reverse code the unfavorable items.
 rm(unfav) # We don't need the vector, so we remove it now to keep our workspace clean.
-
-# Let's see if the items are coded in the same direction now.
-psych::describe(rwa)
-# Yes, the items are coded on the same direction, but why there are "0" values in all columns (see column "min")?
-# The items are not supposed to have "0" value because the responses are ranging from 1-9.
-
-# Let's count how many "0" we have in our data.
[…]

### 2023-12-14 draft_paper.qmd
intro almost done

@@
 
-# install.packages("flextable", dependencies=TRUE) 
-# INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed)
+install.packages("flextable", dependencies=TRUE) 
 library(flextable)
-
 ```
 
-Measurement, undoubtedly, is an important foundation of scientific research. Measurement process start with defining the construct being studied and then determine the assumptions
+A foundation of scientific research is a measurement process, which starts from defining the construct being measured, determining measurement assumptions, and inspecting its measurement validity and precision.
+To illustrate this process, consider a researcher designs a study aiming to identify the association between authoritarian disposition and prejudice toward a social group.
+As the first step, they must clearly define the variables they are interested in and determine a strategy to measure those variables accurately.
+Ensuring that the measurement strategy precisely measure what it is intended to measure often poses a challenge to applied psychology researchers because, most of the time, we have no direct access to observe most psychological constructs.
+Instead, we rely on statistical techniques, which assume that non-observable psychological constructs are "out there," or later we call this variable a *latent construct* or a *manifest variable*.
+More sharply, we create materials, such as scale items, stimulus, tasks, observation check-lists, etc.
+that we *assume* to represent these underlying latent construct (or constructs) being measured.
+
+Relatedly, as most psychological constructs are not directly observable, the questions on whether a scale actually measures what it is intended to measure (i.e., construct validity, see @cronbachConstructValidityPsychological1955) becomes critical.
+Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be sustained by linking test scores to other constructs in which researchers theoretically assume to be related with the construct of interest.
+Further, @cronbachConstructValidityPsychological1955 introduce the notion of "nomological network," which refers to a theoretical framework connecting the measured construct with other (theoretically) related constructs and relevant observations.
+Therefore, validity of the test depends on the behavior of the construct of interest: whether or not it behaves as specified in the theory within this network.
+To scrutinize test validity, researchers correlate the test score with some criterion (i.e., constructs or future/current behaviors theoretically related to the measured construct), and this is a common and widespread practices in psychology [@zumboSettingStageValidity2014].
+
+However, validity theory has evolved over time and been expanded since.
+Rather than a property of a specific test, scholars argue that validity of a scale refers to questions about its consequential aspects [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
+In this sense, a test is deemed valid when researchers can demonstrate evidence for articulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016] in defending test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
+Consequently, scholars argue that scale validity is an ongoing process in which researchers should continually and incrementally gather (and report) the evidence for validity as an important complement to ensure the credibility of their findings [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
+
+Yet in practice, researchers pay far less attention to the validity (and reliability) of their measures.
+According to a study examining articles published in a flagship journal in the field of social and personality psychology shows that only a little more than half (53%) of sample articles cited validity evidence from previous validation studies but 19% of those articles had adapted or modified the measures in various fashions so that the evidence for validity may not extend to the modified scales [@flakeConstructValidationSocial2017].
+A larger study tapping into fifteen commonly used measures in social and personality psychology (e.g., Big Five Inventory, belief in just world scale, need for cognitive closure scale, etc.) even paints a grimmer picture [@husseyHiddenInvalidity152020].
+While majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination (i.e., internal consistency, test-retest reliability, factor structure, and invariance) demonstrated that only 4% of these scales actually possess good validity [@husseyHiddenInvalidity152020].
+Furthermore, applied psychological researchers seem to be less aware of assumptions underlying their chosen method for evaluating scale reliability.
+For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and continuously popular [@mcneishThanksCoefficientAlpha2018], it is unclear that researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, makes its usefulness extremely limited [@sijtsmaUseMisuseVery2008].
+
+With this in mind, it is not surprising that researchers' lack of attention to their measurement quality raises questions about replicability of their findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
+In this sense, a serious doubt about the validity of the measures used in a study can affect the validity of the findings, and the decisions that leads to this doubt is called *questionable measurement practice* (QMP, see @flakeMeasurementSchmeasurementQuestionable2020.
+The difficulty to reach a consensus about the best way to measure a certain construct is also a major downstream consequence of the lack of validity reporting and may become a major obstacle to establish cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+
+Therefore, it is very important to equip applied psychological researchers with practical steps to systematically evaluate their measurement validity and precision.
+By expanding their measurement evaluation toolkit, applied psychological researchers can ensure the quality of their findings and enable them to contribute to cumulative science.
+
+In this article, we aim to gently introduce a graded response model (GRM), a family of item response model,
+
+A meta-communicative cue here---
 
 # A Brief Overview of Item Response Theory
+* Contrasting the concept of validity in IRT and CTT
+* Contrasting the concept of measurement precision in IRT and CTT
+Inserting {apatb-table1}
 
 # Graded Response Model
+Jelasin konsep dasarnya dan plot-plotnya apa aja bedanya sama  inserting {apafg-fig1}
 
-# Assumptions and Key Concepts
+## Assumptions
+Jelasin dua asumsi penting: unidimensionality dan local independence.
 
-# Disclosure
-
+# Disclosure and Data Availability Statements
 To maximise reproducibility of our analysis, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
 We also include the complete R script for the example we used as a supplementary document.
-The Quarto file (and its corresponding .docx and .pdf output) and R script are publicly available on (a Github repository)\[https://github.com/rameliaz/grm-tutorial-paper\].
+The Quarto file (and its corresponding .docx and .pdf output) and R script are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
+To demonstrate the use of GRM, we use a dataset obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which is publicly available.
 
@@
 ```{r}
-
 install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE)
-library(tidyverse); library(psych); library(mirt); library(caret)
+devtools::install_github("masurp/ggmirt") # remote installation through GitHub repository
 ```
@@
 ```{r}
-
-# devtools::install_github("masurp/ggmirt")
-library(ggmirt)
+library(ggmirt); library(tidyverse); library(psych); library(mirt); library(caret)
 ```
@@
 
-As we see in {apatb-table1}, nddasjdhajskdhaks
-
-```{r}
-unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
-rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 9 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
-```
-
-Kok ada nilai 0-nya? padahal kan skor minimalnya 1. Coba kita hitung frekuensi nilai 0 di tiap item.
+As we see in {apatb-table2}, Kok ada nilai 0-nya? padahal kan skor minimalnya 1. Coba kita hitung frekuensi nilai 0 di tiap item.
 
@@
 ```
+
+Kita anggap nilai 0 adalah NA dan kita delete semua case dengan nilai NA
 
@@
 
-Now let's look again at the descriptive statistics after we removed all NA cases.
+Kalau lihat di {apatb-table2}, meannya kok beda2? oh iya karena ada unfavorable items. Ayo kita reverse score dulu ya.
 
 ```{r}
-psych::describe(rwa)
+unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
+rwa <- rwa %>% 
+  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 to reverse code the unfavorable items.
 ```
@@
 
+lalalala
+
 ```{r}
@@
 ```
+
+lalalalal
 
@@
 ```{r}
-pa <- fa.parallel(rwa, fm="minres", fa="fa") # Running a parallel analysis.
-pa$fa.values # Seeing the eigenvalues of each factor.
+pa <- fa.parallel(rwa, fm="minres", fa="fa")
 ```
+
+lalalala
+
+```{r}
+pa$fa.values
+```
+
+Eigenvalues `12.225/0.843`
 
@@
 ```
+
+llalalala
 
@@
 
-lhalalala
+bla bla lhalalala
 
@@
 m2_results <- M2(fit, type="C2")
+m2_results[] <- lapply(m2_results, as.numeric)
 m2_stat <- m2_results$M2
+m2_stat = round(m2_stat, digits = 3)
 df <- m2_results$df
@@
 rmsea <- m2_results$RMSEA
-srmr <- m2_results$SRMR
+rmsea = round(rmsea, digits=3)
+srmsr <- m2_results$SRMSR
+srmsr = round(srmsr, digits=3)
 tli <- m2_results$TLI
+tli = round(tli, digits=3)
 cfi <- m2_results$CFI
+cfi = round(cfi, digits=3)
 ```
@@
 ```{r}
+#| eval: false
+
 for (i in 1:nrow(lar)) {
@@
 itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
-```
-
-lhalalala
-
-```{r}
-#| output: false
-
-itemInfoPlot(fit, facet=T, theta_range = c(-6,6), title = "Item Information Curves of the RWA Scale")#
 ```
@@
 
-```{r apatb-table1}
+```{r}
+#| label: apatb-table1
+#| apa-cap: Comparison Between Common IRT Models
+#| apa-note: NULL
+#| echo: false
+```
+
+| Model                                   | Key Characteristics                                                                                                                                                                                                                                     | Data Type   | Response Options        |
+|-----------------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
+| 1-PL Model (Rasch Model)                | 1.
+Estimates only item difficulties (a).
+2.
+Assumes that all items have the same discrimination parameters (b).
+3.
+Item and person parameters are independent.
+| Dichotomous | Correct/Incorrect (0/1) |
+| 2-PL Model                              | 1.
+Estimates item difficulties (a) and item discriminations (b).
+2.
+Less stringent than 1-PL model since it allows item discrimination parameters (b) to vary.
+| Dichotomous | Correct/Incorrect (0/1) |
+| 3-PL Model                              | 1.
+Estimates item difficulties (a), discriminations (b), and pseudo-guessing parameters (c).
+2.
+Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses.
+| Dichotomous | Correct/Incorrect (0/1) |
+| Graded Response Model (GRM)             | 1.
+Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style).
+2.
+Estimates a discrimination parameter (a) and multiple threshold parameters (b) per item.
+| Polytomous  | Ordered Categories      |
+| Partial Credit Model (PCM)              | 1.
+An extension of the 1-PL (Rasch) model for polytomous items.
+2.
+Estimates thresholds between adjacent categories but assumes equal discrimination across items.
+| Polytomous  | Ordered Categories      |
+| Generalized Partial Credit Model (GPCM) | Extending PCM to allow differential discrimination parameters across items.
+| Polytomous  | Ordered Categories      |
+| Nominal Response Model (NRM)            | 1.
+Appropriate for modeling categorical responses with no order.
+2.
+Estimates discrimination parameters (a) and multiple category-specific parameters (b).
+| Categorical | Unordered Categories    |
+
+{{< pagebreak >}}
+
+```{r}
+#| label: apafg-fig1
+#| apa-cap: An Item Probability Function from a GRM Model
+#| apa-note: NULL
+#| output: true
+#| echo: false
+
+knitr::include_graphics("CPF example.png")
+```
+
+{{< pagebreak >}}
+
+```{r apatb-table2}
 #| output: true
@@
 # Transforming describe() output into a APA-formatted table
+rwa <- subset(ds, select = Q1:Q22)
 table1 <- psych::describe(rwa); table1 <- as.data.frame(table1)
@@
   padding(padding.top = 5, padding.bottom = 5)
-
 table1 <- colformat_double(x=table1, j="Minimum", digits = 0)
@@
 table1 <- colformat_double(x=table1, j="n", digits = 0)
-
 table1
@@
 
-```{r apatb-table2}
+```{r apatb-table3}
 #| output: true
@@
 #| apa-cap: Descriptive Statistics of RWA Scale
-#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| apa-note: Descriptive Statistics After Reversing Unfavorable Items and removing cases with NA. SD = Standard Deviation.
 #| ft.align: left
 
-# Transforming describe() output into a APA-formatted table
+rwa <- rwa %>%
+  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
+  drop_na()  # Removing cases with any NA values.
 unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
 rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 9 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
-
+  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
+# Transforming describe() output into a APA-formatted table
 table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
@@
   padding(padding.top = 5, padding.bottom = 5)
-
 table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
@@
 table2 <- colformat_double(x=table2, j="n", digits = 0)
-
 table2
@@
 
-```{r apatb-table3}
+```{r fig2}
 #| output: true
 #| echo: false
-#| apa-cap: Percentge of Zero in Each Item
-#| ft.align: left
-
-table3 <- as.data.frame(zero)
-
-table3 <- table3 %>% 
-  rownames_to_column(var="Item") %>% 
-  select(Item, zero) %>% 
-  rename(Percentage=zero) %>% 
-  flextable() %>% 
-  theme_apa() %>% 
-  line_spacing(part = "all") %>% 
-  padding(padding.top = 5, padding.bottom = 5)
-
-table3
-
-```
-
-{{< pagebreak >}}
-
-```{r apatb-table4}
-#| output: true
-#| echo: false
-#| apa-cap: Descriptive Statistics of RWA Scale
-#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
-#| ft.align: left
-
-rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
-  drop_na()  # Removing cases with any NA values.
-
-# Transforming describe() output into a APA-formatted table
-table4 <- psych::describe(rwa); table4 <- as.data.frame(table4)
-table4 <- table4 %>% 
-  rownames_to_column(var="Item") %>% 
-  select(Item, mean, sd, min, max, range, n) %>% 
-  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
-  flextable() %>% 
-  theme_apa() %>% 
-  line_spacing(part = "all") %>% 
-  padding(padding.top = 5, padding.bottom = 5)
-
-table4 <- colformat_double(x=table4, j="Minimum", digits = 0)
-table4 <- colformat_double(x=table4, j="Maximum", digits = 0)
-table4 <- colformat_double(x=table4, j="Range", digits = 0)
-table4 <- colformat_double(x=table4, j="n", digits = 0)
-
-table4
-```
-
-{{< pagebreak >}}
-
-```{r fig1}
-#| output: true
-#| echo: false
-#| label: apafg-fig1
+#| label: apafg-fig2
 #| apa-cap: Scree Plot
@@
 
-```{r fig2}
+```{r fig3}
 #| output: true
 #| echo: false
-#| label: apafg-fig2
+#| label: apafg-fig3
 #| apa-cap: Parallel Analysis
@@
 
-```{r apatb-table5}
+```{r}
+#| include: false
+
+sum <- summary(fit) 
+```
+
+```{r apatb-table4}
 #| output: true
 #| echo: false
-#| apa-cap:  Descriptive Statistics of RWA Scale
-#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| apa-cap: Item Parameters
+#| apa-note: λ = Standardized Factor Loadings, h2 = Commonality, α = Discrimination, β1.4 = Response specific difficulty parameters (item threshold).
 #| ft.align: left
+#| column: page
 
-table5 <- as.data.frame(coefs$items)
-
-table5 <- table5 %>% 
+table3 <- as.data.frame(coefs$items)
+load <- as.data.frame(sum$rotF)
+h2 <- as.data.frame(sum$h2)
+table3 <- cbind(table3, load, h2)
+table3 <- table3 %>% 
   rownames_to_column(var="Item") %>% 
-  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8) %>% 
-  rename(α=a, β1=b1, β2=b2, β3=b3, β4=b4, β5=b5, β6=b6, β7=b7, β8=b8) %>% 
+  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, rwa, h2) %>% 
+  rename(α=a, β1=b1, β2=b2, β3=b3, β4=b4, β5=b5, β6=b6, β7=b7, β8=b8, λ=rwa) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-
-table5 <- colformat_double(x=table5, j="α", digits = 2)
-table5 <- colformat_double(x=table5, j="β1", digits = 2)
-table5 <- colformat_double(x=table5, j="β2", digits = 2)
-table5 <- colformat_double(x=table5, j="β3", digits = 2)
-table5 <- colformat_double(x=table5, j="β4", digits = 2)
-table5 <- colformat_double(x=table5, j="β5", digits = 2)
-table5 <- colformat_double(x=table5, j="β6", digits = 2)
-table5 <- colformat_double(x=table5, j="β7", digits = 2)
-table5 <- colformat_double(x=table5, j="β8", digits = 2)
-
-table5
+table3 <- colformat_double(x=table3, j="α", digits = 2)
+table3 <- colformat_double(x=table3, j="β1", digits = 2)
+table3 <- colformat_double(x=table3, j="β2", digits = 2)
+table3 <- colformat_double(x=table3, j="β3", digits = 2)
+table3 <- colformat_double(x=table3, j="β4", digits = 2)
+table3 <- colformat_double(x=table3, j="β5", digits = 2)
+table3 <- colformat_double(x=table3, j="β6", digits = 2)
+table3 <- colformat_double(x=table3, j="β7", digits = 2)
+table3 <- colformat_double(x=table3, j="β8", digits = 2)
+table3
 
@@
 
-```{r apatb-table6}
+```{r apatb-table5}
 #| output: true
 #| echo: false
-#| apa-cap: Descriptive Statistics of RWA Scale
-#| apa-note: SD = Standard Deviation, Descriptive Statistics After Reversing Unfavorable Items
+#| apa-cap: Item Fit Statistics
+#| apa-note: Scaled χ2 Statistics. RMSEA = root mean square error of approximation, CFI = comparative fit index, TLI = Tucker-Lewis index, SRMR = Standardized Root Mean Square Residual.
 #| ft.align: left
 
-table6 <- as.data.frame(item.fit)
-
-table6 <- table6 %>%
+table4 <- as.data.frame(item.fit)
+table4 <- table4 %>%
   select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
-  rename(Item=item) %>% 
+  rename(Item=item, χ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
+table4 <- colformat_double(x=table4, j="χ2", digits = 2)
+table4 <- colformat_double(x=table4, j="df", digits = 2)
+table4 <- colformat_double(x=table4, j="RMSEA", digits = 2)
+table4 <- colformat_double(x=table4, j="p", digits = 2)
+table4
 
-table6 <- colformat_double(x=table6, j="S_X2", digits = 2)
-table6 <- colformat_double(x=table6, j="df.S_X2", digits = 2)
-table6 <- colformat_double(x=table6, j="RMSEA.S_X2", digits = 2)
-table6 <- colformat_double(x=table6, j="p.S_X2", digits = 2)
-
-table6
-
-```
-
-{{< pagebreak >}}
-
-```{r fig3}
-#| output: true
-#| echo: false
-#| label: apafg-fig3
-#| apa-cap: Category Probability Functions of RWA Scale
-#| apa-note: NULL
-
-tracePlot(fit, facet=T, title = "Category Probability Functions of RWA Scale") + labs(color="Response Options")
 ```
@@
 #| label: apafg-fig4
-#| apa-cap: Item Information Curves of the RWA Scale
+#| apa-cap: Item Probability Functions of RWA Scale
 #| apa-note: NULL
 
-itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
+tracePlot(fit, facet=T, title = "Item Probability Functions of RWA Scale") + labs(color="Response Options")
 ```
@@
 #| label: apafg-fig5
-#| apa-cap:  Item Information Curves of the RWA Scale Ranging from -6 to +6 Standard Deviation
+#| apa-cap: Item Information Curves of the RWA Scale
 #| apa-note: NULL
 
-itemInfoPlot(fit, facet=T, theta_range = c(-6,6), title = "Item Information Curves of the RWA Scale")#
+itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
 ```

### 2023-12-14 codes.R

@@ -253,8 +253,8 @@ findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlati
 # From the previous step, we found some problems with model misspecification. 
 # Let's take a look at the curves to closely examine the items.
 
-# Plotting Category Probability Functions (CPF)
-tracePlot(fit, facet=T, title = "Category Probability Functions of RWA Scale") + labs(color="Response Options")
+# Plotting Item Probability Functions (CPF)
+tracePlot(fit, facet=T, title = "Item Probability Functions of RWA Scale") + labs(color="Response Options")
 # All CPFs of RWA items seem to be significantly overlapping, and are peaked on the right side of the curves.
 # This implies that RWA items are more sensitive to differentiate participants with high levels of authoritarian personality.
 

### 2024-01-11 draft_paper.qmd
intro part of the draft almost done

@@
 A foundation of scientific research is a measurement process, which starts from defining the construct being measured, determining measurement assumptions, and inspecting its measurement validity and precision.
-To illustrate this process, consider a researcher designs a study aiming to identify the association between authoritarian disposition and prejudice toward a social group.
+To illustrate this process, consider a researcher who designs a study aiming to identify the association between authoritarian disposition and prejudice toward a social group.
 As the first step, they must clearly define the variables they are interested in and determine a strategy to measure those variables accurately.
-Ensuring that the measurement strategy precisely measure what it is intended to measure often poses a challenge to applied psychology researchers because, most of the time, we have no direct access to observe most psychological constructs.
+Ensuring that the measurement strategy precisely measures what it is intended to measure often poses a challenge to applied psychology researchers because, most of the time, we have no direct access to observe most psychological constructs.
 Instead, we rely on statistical techniques, which assume that non-observable psychological constructs are "out there," or later we call this variable a *latent construct* or a *manifest variable*.
-More sharply, we create materials, such as scale items, stimulus, tasks, observation check-lists, etc.
-that we *assume* to represent these underlying latent construct (or constructs) being measured.
+More sharply, we create materials, such as scale items, stimuli, tasks, observation checklists, etc.
+that we *assume* to represent these underlying latent variables (or constructs) being measured.
 
-Relatedly, as most psychological constructs are not directly observable, the questions on whether a scale actually measures what it is intended to measure (i.e., construct validity, see @cronbachConstructValidityPsychological1955) becomes critical.
-Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be sustained by linking test scores to other constructs in which researchers theoretically assume to be related with the construct of interest.
-Further, @cronbachConstructValidityPsychological1955 introduce the notion of "nomological network," which refers to a theoretical framework connecting the measured construct with other (theoretically) related constructs and relevant observations.
-Therefore, validity of the test depends on the behavior of the construct of interest: whether or not it behaves as specified in the theory within this network.
-To scrutinize test validity, researchers correlate the test score with some criterion (i.e., constructs or future/current behaviors theoretically related to the measured construct), and this is a common and widespread practices in psychology [@zumboSettingStageValidity2014].
+Relatedly, as most psychological constructs are not directly observable, the question on whether a scale actually measures what it is intended to measure (i.e., construct validity, see @cronbachConstructValidityPsychological1955 becomes critical.
+Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be sustained by linking test scores to other constructs which researchers theoretically assume to be related to the construct of interest.
+Further, @cronbachConstructValidityPsychological1955 introduce the notion of a "nomological network," which refers to a theoretical framework connecting the measured construct with other (theoretically) related constructs and relevant observations.
+Therefore, the validity of the test depends on the behavior of the construct of interest: whether or not it behaves as specified in the theory within this network.
+To scrutinize test validity, researchers correlate the test score with some criterion (i.e., constructs or future and/or current behaviors theoretically related to the measured construct), and this is a widespread practice in psychology [@zumboSettingStageValidity2014].
 
-However, validity theory has evolved over time and been expanded since.
-Rather than a property of a specific test, scholars argue that validity of a scale refers to questions about its consequential aspects [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
+However, validity theory has evolved over time and has been expanded since.
+Rather than a property of a specific test, scholars argue that the validity of a scale refers to questions about its consequential aspects [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
 In this sense, a test is deemed valid when researchers can demonstrate evidence for articulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016] in defending test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
-Consequently, scholars argue that scale validity is an ongoing process in which researchers should continually and incrementally gather (and report) the evidence for validity as an important complement to ensure the credibility of their findings [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
+Consequently, scale validity is an ongoing process in which researchers should continually and incrementally gather (and report) the evidence as an important complement to ensure the credibility of their findings [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
 
-Yet in practice, researchers pay far less attention to the validity (and reliability) of their measures.
-According to a study examining articles published in a flagship journal in the field of social and personality psychology shows that only a little more than half (53%) of sample articles cited validity evidence from previous validation studies but 19% of those articles had adapted or modified the measures in various fashions so that the evidence for validity may not extend to the modified scales [@flakeConstructValidationSocial2017].
+Yet in practice, researchers pay far less attention to the quality of their measures.
+According to a study examining articles published in a flagship journal in the field of social and personality psychology, only a little more than half (53%) of sample articles cited validity evidence from previous validation studies but 19% of those articles had adapted or modified the measures in various fashions so that the evidence for validity may not extend to the modified scales [@flakeConstructValidationSocial2017].
 A larger study tapping into fifteen commonly used measures in social and personality psychology (e.g., Big Five Inventory, belief in just world scale, need for cognitive closure scale, etc.) even paints a grimmer picture [@husseyHiddenInvalidity152020].
-While majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination (i.e., internal consistency, test-retest reliability, factor structure, and invariance) demonstrated that only 4% of these scales actually possess good validity [@husseyHiddenInvalidity152020].
-Furthermore, applied psychological researchers seem to be less aware of assumptions underlying their chosen method for evaluating scale reliability.
-For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and continuously popular [@mcneishThanksCoefficientAlpha2018], it is unclear that researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, makes its usefulness extremely limited [@sijtsmaUseMisuseVery2008].
+While the majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination (i.e., internal consistency, test-retest reliability, factor structure, and invariance) revealed that only 4% of these scales actually possess good measurement validity [@husseyHiddenInvalidity152020].
+Furthermore, applied psychological researchers seem to be less aware of the assumptions underlying their chosen method for evaluating scale reliability.
+For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and continuously popular [@mcneishThanksCoefficientAlpha2018], it is unclear that researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, limits its usefulness [@sijtsmaUseMisuseVery2008].
 
-With this in mind, it is not surprising that researchers' lack of attention to their measurement quality raises questions about replicability of their findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
-In this sense, a serious doubt about the validity of the measures used in a study can affect the validity of the findings, and the decisions that leads to this doubt is called *questionable measurement practice* (QMP, see @flakeMeasurementSchmeasurementQuestionable2020.
-The difficulty to reach a consensus about the best way to measure a certain construct is also a major downstream consequence of the lack of validity reporting and may become a major obstacle to establish cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+With this in mind, it is not surprising that researchers' lack of attention to their measurement quality raises questions about the replicability of their findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
+In this sense, a serious doubt about the validity of the measures used in a study can affect the validity of the findings, and the decisions that lead to this doubt are called *questionable measurement practice* (QMP, see @flakeMeasurementSchmeasurementQuestionable2020.
+The difficulty in reaching a consensus about the best way to measure a certain construct is also a major downstream consequence of the lack of validity reporting and may become a major obstacle to establishing cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
 
-Therefore, it is very important to equip applied psychological researchers with practical steps to systematically evaluate their measurement validity and precision.
-By expanding their measurement evaluation toolkit, applied psychological researchers can ensure the quality of their findings and enable them to contribute to cumulative science.
+Therefore, in our view, it is critical to equip applied psychological researchers with practical steps to systematically evaluate their measurement validity and precision.
+Moreover, since construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], applied researchers can contribute evidence for the validity of the scales they use in their research [@floraPurposePracticeExploratory2017] by implementing a GRM model to their data.
 
-In this article, we aim to gently introduce a graded response model (GRM), a family of item response model,
+In this article, we aim to gently introduce a graded response model (GRM), which is a family of item response models, specifically aimed to assess the measurement precision of a polytomous (Likert-style) scale.
+We start this paper by briefly explaining the basics of Item Response Theory (IRT), the theoretical foundation of GRM, as well as contrasting its differences with the widely known Classical True Score Theory (CTT).
+In this paper, we aim to keep our tutorial concise so we do not attempt to cover all IRT concepts in detail.
+Interested readers are referred to available didactic texts on IRT, such as @embretsonItemResponseTheory2000 for an introductory level and @bakerBasicsItemResponse2017 or @deayalaTheoryPracticeItem2022 for a more technical and comprehensive overview.
 
-A meta-communicative cue here---
+Further, we briefly explain what GRM is and how a GRM model is specified.
+In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations (i.e., plots) deriving from GRM analysis.
+In this part, we also further introduce some assumptions underlie a GRM and how to check these assumptions.
+Subsequently, we provide an illustrative example of testing measurement precision using GRM, and in this part, we show how to practically implement GRM analysis and interpret its results.
+We complement the illustrative example with code in the open-source programming language R [@rcoreteamLanguageEnvironmentStatistical2023] so that the readers can implement and reproduce the example presented in this paper.
+Readers with a little experience with R and RStudio can easily follow this tutorial but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials designed by @navarroPsychologicalScience2018.
 
 # A Brief Overview of Item Response Theory
-* Contrasting the concept of validity in IRT and CTT
-* Contrasting the concept of measurement precision in IRT and CTT
-Inserting {apatb-table1}
+To scrutinize their measurement, psychological researchers have relied upon two foundational principles underlying psychological testing (i.e., CTT and IRT) to decompose observed score into its *deterministic* and *random* (stochastic) elements [@zumboValidityFoundationalIssues2006].
+On the one hand, CTT decomposes observed score into *true* score and its *error* components.
+In practice, researchers implement this principle by conducting Structural Equation Modeling (SEM), Exploratory Factor Analysis (EFA), or Confirmatory Factor Analysis (CFA).
+Specifying the measurement part of SEM, or employing EFA and CFA models, allows for the decomposition of the covariance matrix of a given data into latent factors, which represent true score or actual ability or trait level, and error terms (i.e., residuals or unique variances).
+Consequently, the relationship between observed score and true score is *linear*, as true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
+While on the other hand, IRT models this relationship in a *probabilistic* function rather than a linear one.
+More sharply, an IRT model assumes a probabilistic relationship between observed score and the latent trait being measured ($\Theta$), and notably, this probability accounts for the properties of the items, such as item discrimination, difficulty, and if necessary, guessing [@bakerBasicsItemResponse2017].
+
+The most critical distinction between CTT and IRT is how they conceptualize measurement error.
+In CTT, standard deviation of the observed score (*s*) is used to calculate standard error of measurement.
+Since measurement error relies on *s*, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample regardless of their trait level.
+This shortcoming restricts the utility of CTT, especially since psychologists often need to interpret individual scores, not just evaluate the test as a whole.
+Additionally, since the standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is presumed to be equal across different levels of a trait or ability.
+However, researchers frequently encounter situations where a test is excessively difficult for a group of low-performing participants, providing little information beyond indicating that their trait or ability level is significantly lower than what the test can measure.
+
+IRT offers an elegant solution to this issue by enabling the calculation of standard errors for each individual (*SE*~$\theta$~), and test reliability can be inferred from the average of individual standard error across a sample of participants[ @embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
+This approach allows for the estimation of both overall reliability *and* reliability at varying levels of trait or ability.
+Returning to the previous example, when a test is overly challenging for low-performing individuals, IRT analysis can help identify the levels of trait or ability where the test is most reliable.
+A concrete example of this is a study scrutinizing the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
+According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ < $\Theta$ < 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
+Therefore, IRT models offer a more informative and nuanced perspective, proving useful for researchers who wish to closely examine the performance of their measures.
+
+Further, IRT allows researchers to examine the performance of a specific item (hence "item" response theory) by specifying the relationship between item score and $\Theta$ given one-, two-, or three-parameter.
+One-parameter logistic (1PL) or Rasch model, the simplest variant of the IRT models, accounts only item difficulty (*b*) while presuming equal item discrimination (*a*) across items.
+Practically, this model slightly overlaps with CTT in the sense that they assume that all items carry equal informative value thus the estimated $\Theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
+This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measurements remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
+Put simply, the latent trait ($\Theta$) should remain unaffected by specific items used in the test.
+For example, the difference in depression levels between two individuals should be always the same regardless of the scale used to measure their depression levels.
+While this principle reasonably enforces objectivity in measurement practices, it demands a strong theory delineating the construct and strict requirements of data-model fit while both assumptions rarely hold in a real-world scenario, especially in psychological science.
+
+Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing the item ability to differentiate individuals with varying levels of $\Theta$ (i.e., item discrimination parameter - *a*) to differ.
+In some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\Theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false response), and the focus of this article is nonetheless to show the utility of IRT for fitting the ordered (Likert-style) responses.
+The field of IRT has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
+We briefly summarize the features of the most frequently employed IRT models in {apatb-table1}.
 
 # Graded Response Model
-Jelasin konsep dasarnya dan plot-plotnya apa aja bedanya sama  inserting {apafg-fig1}
+GRM is a family of IRT models specifically designed to analyze ordered polytomous (Likert-style) data [@samejimaGradedResponseModel1997; @samejimaGeneralGradedResponse2010; @samejimaGradedResponseModels2016].
+The fundamental idea of GRM is to extend the logic of simpler dichotomous IRT models to polytomous scales by applying a probabilistic function to each response category.
+In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of ($\Theta$), item difficulty, and item discrimination.
+GRM extends this idea by modeling the probability of picking a certain response category or higher on an item (i.e., *step function*) given to item difficulty and discrimination.
+For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\Theta$.
+Therefore, the notion of item difficulty in dichotomous IRT is extended to the step function (i.e., item threshold).
+
+To illustrate the step function, consider a scale measuring sadistic personality (e.g., "*watching a fist-fight excites me*," etc.) with response categories ranging from 1 (*strongly disagree*) to 4 (*strongly agree*).
+Imagine these categories are hierarchically ordered from the lowest category (*strongly disagree*) to the highest (*strongly agree*), like a staircase.
+GRM aims to estimate the level of sadistic personality ($\Theta$) required for "stepping" from one response category to another (e.g., *moderately agree* to *strongly agree*).
+Therefore, a GRM model of a five-point Likert scale calculates four item threshold parameters (*b*): the location of $\Theta$ level where individuals are equally likely to respond 1 or 2 (*b*~1~), 2 or 3 (*b*~2~), 3 or 4 (*b*~3~), and 4 or 5 (*b*~4~).
+Each threshold is exactly the point where a participant is equally likely to respond to either of the adjacent response categories.
+For example, if *b*~1~ = -1.23 for the item *watching a fist-fight excites me*, this means that participants with sadism level 1.23 below the mean are equally likely to either answer *strongly disagree* or *moderately disagree*.
+
+Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item with five response categories.
+{apafg-fig1} consists of five category probability curves, each of which represents the probability of endorsing a response category given $\Theta$.
+Item threshold is exactly a location of $\Theta$ where two adjacent category probability curves cross each other.
 
 ## Assumptions
-Jelasin dua asumsi penting: unidimensionality dan local independence.
+Jelasin tiga asumsi penting: monotonicity, unidimensionality dan local independence.
 
 # Disclosure and Data Availability Statements
-To maximise reproducibility of our analysis, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
+To maximize the reproducibility of our analysis, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
 We also include the complete R script for the example we used as a supplementary document.
 The Quarto file (and its corresponding .docx and .pdf output) and R script are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
-To demonstrate the use of GRM, we use a dataset obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which is publicly available.
+To demonstrate the use of GRM, we use a dataset obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which can be publicly accessed.
 
@@
 coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
-print(coefs) # Yielding model parameters: item discriminations (a) and threshold (b).
+print(coefs) # Yielding model parameters: item discrimination (a) and threshold (b).
 ```
@@
 ```{r}
-theta_se <- fscores(fit, full.scores.SE = T) # Extracting the estimated theta score of each participant.
-e_rel <- empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
+m_rel <- marginal_rxx(fit)
 ```
@@
 ```{r}
-m_rel <- marginal_rxx(fit)
+conRelPlot(fit, title="Reliability of the RWA Scale Given to the θ Level")
+```
+
+lalalala
+
+```{r}
+theta_se <- fscores(fit, full.scores.SE = T) # Extracting the estimated theta score of each participant.
+e_rel <- empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
 ```
@@
 | 1-PL Model (Rasch Model)                | 1.
-Estimates only item difficulties (a).
+Estimates only item difficulties (*b*).
 2.
-Assumes that all items have the same discrimination parameters (b).
+Assumes that all items have equal discrimination parameters (*a*).
 3.
@@
 | 2-PL Model                              | 1.
-Estimates item difficulties (a) and item discriminations (b).
+Estimates item difficulties (*b*) and item discrimination (*a*).
 2.
-Less stringent than 1-PL model since it allows item discrimination parameters (b) to vary.
+Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.
 | Dichotomous | Correct/Incorrect (0/1) |
 | 3-PL Model                              | 1.
-Estimates item difficulties (a), discriminations (b), and pseudo-guessing parameters (c).
+Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*).
 2.
@@
 2.
-Estimates a discrimination parameter (a) and multiple threshold parameters (b) per item.
+Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.
 | Polytomous  | Ordered Categories      |
@@
 2.
-Estimates discrimination parameters (a) and multiple category-specific parameters (b).
+Estimates discrimination parameters (*a*) and multiple category-specific parameters (*b*).
 | Categorical | Unordered Categories    |

### 2024-01-12 draft_paper.qmd
updated .bib

@@
 
-A foundation of scientific research is a measurement process, which starts from defining the construct being measured, determining measurement assumptions, and inspecting its measurement validity and precision.
-To illustrate this process, consider a researcher who designs a study aiming to identify the association between authoritarian disposition and prejudice toward a social group.
-As the first step, they must clearly define the variables they are interested in and determine a strategy to measure those variables accurately.
-Ensuring that the measurement strategy precisely measures what it is intended to measure often poses a challenge to applied psychology researchers because, most of the time, we have no direct access to observe most psychological constructs.
-Instead, we rely on statistical techniques, which assume that non-observable psychological constructs are "out there," or later we call this variable a *latent construct* or a *manifest variable*.
-More sharply, we create materials, such as scale items, stimuli, tasks, observation checklists, etc.
-that we *assume* to represent these underlying latent variables (or constructs) being measured.
+The foundation of scientific research is the measurement process, which involves defining the construct to be measured, determining measurement assumptions, and evaluating measurement validity and precision.
+For instance, a researcher studying the role of authoritarian personality in explaining prejudice must first clearly define these variables, and then, develop a measurement strategy to operationalize the variables.
+This is challenging in applied psychology, as most psychological constructs are not directly observable.
+To ensure a precise measurement, researchers rely on statistical techniques, assuming that these non-observable traits are "out there," or later we name this concept a *latent trait* or a *manifest variable*.
+Researchers then create tools, like scales, stimuli, tasks, observation checklists, etc., which are assumed to represent these these latent traits.
 
-Relatedly, as most psychological constructs are not directly observable, the question on whether a scale actually measures what it is intended to measure (i.e., construct validity, see @cronbachConstructValidityPsychological1955 becomes critical.
-Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be sustained by linking test scores to other constructs which researchers theoretically assume to be related to the construct of interest.
-Further, @cronbachConstructValidityPsychological1955 introduce the notion of a "nomological network," which refers to a theoretical framework connecting the measured construct with other (theoretically) related constructs and relevant observations.
-Therefore, the validity of the test depends on the behavior of the construct of interest: whether or not it behaves as specified in the theory within this network.
-To scrutinize test validity, researchers correlate the test score with some criterion (i.e., constructs or future and/or current behaviors theoretically related to the measured construct), and this is a widespread practice in psychology [@zumboSettingStageValidity2014].
+In psychological research, where variables are often not directly observable, construct validity, which refers to a question on whether a scale measures what it is intended to measure [@cronbachConstructValidityPsychological1955], becomes crucial.
+Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be scrutinized by linking test scores to other related constructs and observations.
+Test validity relies on whether the construct behaves as theory predicts within a "nomological network" [@cronbachConstructValidityPsychological1955].
+In practice, researchers establish validity by correlating the test score with external criterion i.e., other theoretically related traits or behavior [@zumboSettingStageValidity2014].
 
-However, validity theory has evolved over time and has been expanded since.
-Rather than a property of a specific test, scholars argue that the validity of a scale refers to questions about its consequential aspects [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
-In this sense, a test is deemed valid when researchers can demonstrate evidence for articulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016] in defending test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
-Consequently, scale validity is an ongoing process in which researchers should continually and incrementally gather (and report) the evidence as an important complement to ensure the credibility of their findings [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
+Over time, validity theory has evolved and has been expanded.
+Validity is now seen not as a property of a specific test, but rather lies in the consequential aspects of the test use [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
+In this sense, a test is deemed valid when researchers can demonstrate evidence for formulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016], such as causal inference [@rutkowskiCausalInferencesLarge2016], used to defend test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
+This makes construct validity an ongoing process where researchers are advised to continuously gather and report evidence for validity of the measures they use in their research [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
 
-Yet in practice, researchers pay far less attention to the quality of their measures.
-According to a study examining articles published in a flagship journal in the field of social and personality psychology, only a little more than half (53%) of sample articles cited validity evidence from previous validation studies but 19% of those articles had adapted or modified the measures in various fashions so that the evidence for validity may not extend to the modified scales [@flakeConstructValidationSocial2017].
-A larger study tapping into fifteen commonly used measures in social and personality psychology (e.g., Big Five Inventory, belief in just world scale, need for cognitive closure scale, etc.) even paints a grimmer picture [@husseyHiddenInvalidity152020].
-While the majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination (i.e., internal consistency, test-retest reliability, factor structure, and invariance) revealed that only 4% of these scales actually possess good measurement validity [@husseyHiddenInvalidity152020].
-Furthermore, applied psychological researchers seem to be less aware of the assumptions underlying their chosen method for evaluating scale reliability.
-For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and continuously popular [@mcneishThanksCoefficientAlpha2018], it is unclear that researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, limits its usefulness [@sijtsmaUseMisuseVery2008].
+Yet in practice, researchers tend to overlook to the quality of their measures.
+A study reviewing articles published in a social and personality psychology journal found that only a little more than half (53%) of sample articles cited validity evidence from previous validation studies.
+Nineteen percent of those articles, nonetheless, had adapted or modified the measures in many different ways so that the evidence for validity may not extend to these modified versions [@flakeConstructValidationSocial2017].
+Additionally, a larger study examining fifteen commonly used measures in social and personality psychology (e.g., Big Five Inventory, belief in just world scale, need for cognitive closure scale, etc.) even paints a grimmer picture [@husseyHiddenInvalidity152020].
+While the majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination through internal consistency, test-retest reliability, factor structure, and invariance tests revealed that only 4% of these scales possess good measurement validity [@husseyHiddenInvalidity152020].
+Furthermore, applied psychological researchers seem to overlook the assumptions underlying their chosen method for evaluating reliability.
+For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and exceptionally popular [@mcneishThanksCoefficientAlpha2018], it is unclear whether researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, limits its usefulness [@sijtsmaUseMisuseVery2008].
 
-With this in mind, it is not surprising that researchers' lack of attention to their measurement quality raises questions about the replicability of their findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
-In this sense, a serious doubt about the validity of the measures used in a study can affect the validity of the findings, and the decisions that lead to this doubt are called *questionable measurement practice* (QMP, see @flakeMeasurementSchmeasurementQuestionable2020.
-The difficulty in reaching a consensus about the best way to measure a certain construct is also a major downstream consequence of the lack of validity reporting and may become a major obstacle to establishing cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+With this in mind, this oversight in measurement quality can raise reasonable concerns about the replicability of research findings because measurement contributes to the (in)validity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
+Measurement oversight can be identified in decisions that researchers make, which potentially compromise the validity of the measures used in their studies, a phenomenon known as "*questionable measurement practices*" [@flakeMeasurementSchmeasurementQuestionable2020].
+Further, the lack of evidence for measurement validity contributes to the difficulty in reaching a consensus about the best way to measure a construct.
+In the long run, it becomes a major obstacle to establishing cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to assist them in evaluating measurement validity so that they can improve their measurement practices, and thus, the credibility of their findings.
 
-Therefore, in our view, it is critical to equip applied psychological researchers with practical steps to systematically evaluate their measurement validity and precision.
-Moreover, since construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], applied researchers can contribute evidence for the validity of the scales they use in their research [@floraPurposePracticeExploratory2017] by implementing a GRM model to their data.
-
-In this article, we aim to gently introduce a graded response model (GRM), which is a family of item response models, specifically aimed to assess the measurement precision of a polytomous (Likert-style) scale.
+In this article, we aim to gently introduce the graded response model (GRM), which is a family of item response models, specifically aimed to assess the measurement precision of a polytomous (Likert-style) scale.
 We start this paper by briefly explaining the basics of Item Response Theory (IRT), the theoretical foundation of GRM, as well as contrasting its differences with the widely known Classical True Score Theory (CTT).
-In this paper, we aim to keep our tutorial concise so we do not attempt to cover all IRT concepts in detail.
-Interested readers are referred to available didactic texts on IRT, such as @embretsonItemResponseTheory2000 for an introductory level and @bakerBasicsItemResponse2017 or @deayalaTheoryPracticeItem2022 for a more technical and comprehensive overview.
+In this paper, we aim to keep our tutorial concise so we do not cover all IRT concepts in detail.
+Interested readers are referred to available didactic texts on IRT, such as @embretsonItemResponseTheory2000 for the introductory level, and @bakerBasicsItemResponse2017 and @deayalaTheoryPracticeItem2022 for a more technical and comprehensive overview.
 
 Further, we briefly explain what GRM is and how a GRM model is specified.
-In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations (i.e., plots) deriving from GRM analysis.
-In this part, we also further introduce some assumptions underlie a GRM and how to check these assumptions.
+In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations (i.e., plots) derived from a GRM analysis.
+We also introduce three key assumptions underlying a GRM and how to test these assumptions.
 Subsequently, we provide an illustrative example of testing measurement precision using GRM, and in this part, we show how to practically implement GRM analysis and interpret its results.
 We complement the illustrative example with code in the open-source programming language R [@rcoreteamLanguageEnvironmentStatistical2023] so that the readers can implement and reproduce the example presented in this paper.
-Readers with a little experience with R and RStudio can easily follow this tutorial but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials designed by @navarroPsychologicalScience2018.
+Readers with some experience with R and RStudio can easily follow this tutorial, but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials developed by @navarroPsychologicalScience2018.
+At last, we present some concluding remarks to encourage researchers to implement a GRM analysis as a part of their routine.
 
 # A Brief Overview of Item Response Theory
-To scrutinize their measurement, psychological researchers have relied upon two foundational principles underlying psychological testing (i.e., CTT and IRT) to decompose observed score into its *deterministic* and *random* (stochastic) elements [@zumboValidityFoundationalIssues2006].
+
+To scrutinize their measurement quality, psychological researchers have relied upon two foundational principles underlying psychological testing, i.e., CTT and IRT, to decompose observed score into its *deterministic* and *random* or stochastic elements [@zumboValidityFoundationalIssues2006].
 On the one hand, CTT decomposes observed score into *true* score and its *error* components.
@@
 Consequently, the relationship between observed score and true score is *linear*, as true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
-While on the other hand, IRT models this relationship in a *probabilistic* function rather than a linear one.
-More sharply, an IRT model assumes a probabilistic relationship between observed score and the latent trait being measured ($\Theta$), and notably, this probability accounts for the properties of the items, such as item discrimination, difficulty, and if necessary, guessing [@bakerBasicsItemResponse2017].
+IRT, on the other hand, models this relationship in a *probabilistic* rather than a linear fashion.
+More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\Theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, if necessary, guessing [@bakerBasicsItemResponse2017].
 
@@
 This shortcoming restricts the utility of CTT, especially since psychologists often need to interpret individual scores, not just evaluate the test as a whole.
-Additionally, since the standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is presumed to be equal across different levels of a trait or ability.
-However, researchers frequently encounter situations where a test is excessively difficult for a group of low-performing participants, providing little information beyond indicating that their trait or ability level is significantly lower than what the test can measure.
+Additionally, since standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is presumed to be equal across different levels of a trait or ability.
+This is unrealistic since researchers frequently encounter situations where a test is excessively difficult for a group of low-performing participants, providing little information beyond indicating that their trait or ability level is significantly lower than what the test can measure.
 
-IRT offers an elegant solution to this issue by enabling the calculation of standard errors for each individual (*SE*~$\theta$~), and test reliability can be inferred from the average of individual standard error across a sample of participants[ @embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
-This approach allows for the estimation of both overall reliability *and* reliability at varying levels of trait or ability.
-Returning to the previous example, when a test is overly challenging for low-performing individuals, IRT analysis can help identify the levels of trait or ability where the test is most reliable.
+IRT offers an elegant solution to this issue by enabling the calculation of standard errors for each individual (*SE*~$\theta$~), and test reliability can be inferred from the average of *SE*~$\theta$~ across a sample of participants [@embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
+This approach allows for the estimation of reliability at varying levels of trait or ability (i.e., test information function - TIF).
+By doing this, when a test is overly challenging for low-performing individuals or too easy for high-performing individuals, IRT analysis can help identify the levels of trait or ability where the test is most reliable.
 A concrete example of this is a study scrutinizing the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
-According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ < $\Theta$ < 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
+According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\Theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
 Therefore, IRT models offer a more informative and nuanced perspective, proving useful for researchers who wish to closely examine the performance of their measures.
@@
 This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measurements remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
-Put simply, the latent trait ($\Theta$) should remain unaffected by specific items used in the test.
+Put simply, Rasch model assumes that the latent trait ($\Theta$) should remain unaffected by specific items used in the test.
 For example, the difference in depression levels between two individuals should be always the same regardless of the scale used to measure their depression levels.
@@
 
-Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing the item ability to differentiate individuals with varying levels of $\Theta$ (i.e., item discrimination parameter - *a*) to differ.
-In some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\Theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing item ability to differentiate individuals with varying levels of $\Theta$ (i.e., item discrimination parameter - *a*) to differ.
+Additionally, in some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\Theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+The field of IRT has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
 It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false response), and the focus of this article is nonetheless to show the utility of IRT for fitting the ordered (Likert-style) responses.
-The field of IRT has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
 We briefly summarize the features of the most frequently employed IRT models in {apatb-table1}.
@@
 # Graded Response Model
-GRM is a family of IRT models specifically designed to analyze ordered polytomous (Likert-style) data [@samejimaGradedResponseModel1997; @samejimaGeneralGradedResponse2010; @samejimaGradedResponseModels2016].
+
+The GRM is a family of IRT models specifically designed to analyze ordered polytomous (Likert-style) data [@samejimaGradedResponseModel1997; @samejimaGeneralGradedResponse2010; @samejimaGradedResponseModels2016].
 The fundamental idea of GRM is to extend the logic of simpler dichotomous IRT models to polytomous scales by applying a probabilistic function to each response category.
-In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of ($\Theta$), item difficulty, and item discrimination.
+In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\Theta$, item difficulty, and item discrimination.
 GRM extends this idea by modeling the probability of picking a certain response category or higher on an item (i.e., *step function*) given to item difficulty and discrimination.
 For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\Theta$.
-Therefore, the notion of item difficulty in dichotomous IRT is extended to the step function (i.e., item threshold).
+Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold) in order to handle ordered polytomous data.
 
@@
 Each threshold is exactly the point where a participant is equally likely to respond to either of the adjacent response categories.
-For example, if *b*~1~ = -1.23 for the item *watching a fist-fight excites me*, this means that participants with sadism level 1.23 below the mean are equally likely to either answer *strongly disagree* or *moderately disagree*.
+For example, if *b*~1~ = -1.23 for the item "*watching a fist-fight excites me*", it implies that participants with sadism level 1.23 below the mean are equally likely to either answer *strongly disagree* or *moderately disagree*.
 
-Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item with five response categories.
+Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item of a scale with five response categories.
+In general, IPF describes a relationship between $\Theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\Theta$).
 {apafg-fig1} consists of five category probability curves, each of which represents the probability of endorsing a response category given $\Theta$.
-Item threshold is exactly a location of $\Theta$ where two adjacent category probability curves cross each other.
+Item threshold is exactly the location of $\Theta$ where two adjacent category probability curves cross each other.
 
 ## Assumptions
-Jelasin tiga asumsi penting: monotonicity, unidimensionality dan local independence.
 
-# Disclosure and Data Availability Statements
-To maximize the reproducibility of our analysis, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
-We also include the complete R script for the example we used as a supplementary document.
-The Quarto file (and its corresponding .docx and .pdf output) and R script are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
-To demonstrate the use of GRM, we use a dataset obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which can be publicly accessed.
+Before running an analysis, researchers need to be aware of assumption underlying a GRM model.
+The first key assumption is that $\Theta$ is monotonically correlated with the probability of endorsing a response category.
+In other words, individuals with higher levels of $\Theta$ have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
+For instance, people with higher tendency of sadistic personality have a greater chance of answering "*moderately agree*" or "*strongly agree*" on a sadism scale compared to those with lower levels of sadism.
+
+The second key assumption pertains to unidimensionality of $\Theta$.
+This implies that the item pool tested using a GRM analysis should represent only one latent trait ($\Theta$).
+Although it is indeed possible to account for multiple $\Theta$ in a IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
+To test whether an item pool represents only one $\Theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
+
+Relatedly, a GRM model assumes that the item pool are locally independent, as the third assumption.
+Local independence suggests that participants' responses to one item do not influence their response to another.
+It is important to note that evidence for unidimensionality does not always warrant local independence.
+As an eyeball example - consider a trust in science scale containing these two items: "*I trust scientists working in the natural science*" and "*most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in the natural science are very likely to also trust biologists.
+To inspect whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\Theta$ using residual correlation analysis [@chenLocalDependenceIndexes1997].
 
@@
 
-To demonstrate the procedure of running a graded response model, we
+## A Brief Overview of the Altemeyer's RWA Scale
 
-## A Brief Overview of the Altemeyer's RWA Scale
+To illustrate the application of GRM for analyzing measurement precision of an ordered polytomous scale, we provide an example of a GRM analysis of the RWA scale data [@altemeyerRightwingAuthoritarianism1981; @altemeyerAuthoritarians2006].
+@altemeyerRightwingAuthoritarianism1981 defines RWA as a personality propensity to blindly abide established authorities (i.e., authoritarian submission), to act aggressively toward individuals who are perceived to be punished by these established authorities (i.e., authoritarian aggression), and to uphold traditional values promoted by the authorities (i.e., conventionalism).
+Individuals with higher levels of RWA tend to view the world as a dangerous place [@duckittDualProcessMotivational2017], and thus, to ensure stability and safety, they are motivated to preserve social order by deferring to those whom they perceive as legal, social, or moral authorities; for instance, the government, religious institutions, or political or religious or military leaders [@saundersRightWingAuthoritarianismScale2017].
+The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains as one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors @akramiRightWingAuthoritarianismSocial2006; [@osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
+
+In this paper, we use the latest version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items that participants are asked to respond their agreement to those items on a nine-point scale, ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
+While the RWA scale consists of three sub-dimensions, i.e., submissiveness, aggression, and conventionalism, the RWA scale is (theoretically) unidimensional because [@altemeyerAuthoritarians2006] shows that the sub-dimensions are strongly intercorrelated.
+While some evidence shows otherwise [@duckittMultidimensionalityRightWingAuthoritarian2013], for the purpose of this article, we assume that the RWA scale is unidimensional.
+
+# Disclosure and Data Availability Statements
+
+To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
+We also include the annotated R script file (.R) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
+The Quarto file (and its corresponding .docx and .pdf output) and R script file are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
+The dataset we used in this tutorial paper was obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which is publicly accessible.
 
@@
 
+Since construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], applied researchers can contribute to the cumulative science by reporting evidence for measurement validity [@floraPurposePracticeExploratory2017], and this can be done by implementing and reporting a GRM analysis.
+
 {{< pagebreak >}}
@@
 | Model                                   | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-|-----------------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
-| 1-PL Model (Rasch Model)                | 1.
+|----------|--------------------------------------------|----------|----------|
+| 1-PL Model (Rasch Model)                | 1\.
 Estimates only item difficulties (*b*).
@@
 | Dichotomous | Correct/Incorrect (0/1) |
-| 2-PL Model                              | 1.
+| 2-PL Model                              | 1\.
 Estimates item difficulties (*b*) and item discrimination (*a*).
@@
 | Dichotomous | Correct/Incorrect (0/1) |
-| 3-PL Model                              | 1.
+| 3-PL Model                              | 1\.
 Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*).
@@
 | Dichotomous | Correct/Incorrect (0/1) |
-| Graded Response Model (GRM)             | 1.
+| Graded Response Model (GRM)             | 1\.
 Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style).
@@
 | Polytomous  | Ordered Categories      |
-| Partial Credit Model (PCM)              | 1.
+| Partial Credit Model (PCM)              | 1\.
 An extension of the 1-PL (Rasch) model for polytomous items.
@@
 | Polytomous  | Ordered Categories      |
-| Nominal Response Model (NRM)            | 1.
+| Nominal Response Model (NRM)            | 1\.
 Appropriate for modeling categorical responses with no order.

### 2024-01-12 codes.R

@@ -193,9 +193,9 @@ fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F) # This
 coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
 
 # Let's take a look at the model parameters!
-print(coefs) # Yielding model parameters: item discriminations (a) and threshold (b).
+print(coefs) # Yielding model parameters: item discrimination (a) and threshold (b).
 
-# In the console, now we can see item discriminations (a), which indicates how well an item differentiates
+# In the console, now we can see item discrimination (a), which indicates how well an item differentiates
 # participant with different levels of authoritarian personality. To interpret this, we could use a guideline from 
 # Baker (2017). RWA items, in general, have a moderate to very high ability to differentiate participants with different theta levels.
 # We can see that most items have 8 item threshold each (b1-b8), and this is because we have nine response options.

### 2024-01-15 draft_paper.qmd
Step 3 done!

@@
 Although it is indeed possible to account for multiple $\Theta$ in a IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
+An unidimensional IRT model can still be robustly applied to multidimensional data if multiple latent traits are moderately intercorrelated or when there is a strong general factor (*g*) underlying the data [@reiseEvaluatingImpactMultidimensionality2015].
 To test whether an item pool represents only one $\Theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
@@
 Individuals with higher levels of RWA tend to view the world as a dangerous place [@duckittDualProcessMotivational2017], and thus, to ensure stability and safety, they are motivated to preserve social order by deferring to those whom they perceive as legal, social, or moral authorities; for instance, the government, religious institutions, or political or religious or military leaders [@saundersRightWingAuthoritarianismScale2017].
-The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains as one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors @akramiRightWingAuthoritarianismSocial2006; [@osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
+The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains as one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors [@akramiRightWingAuthoritarianismSocial2006; @osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
 
@@
 
+Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023a], *ggmirt* [@masurGgmirt2023], *tidyverse* [@wickhamWelcomeTidyverse2019], *caret* [@kuhnCaretClassificationRegression2024], and *devtools* [@wickhamDevtoolsToolsMake2022], with these following commands:
+
 ```{r}
@@
 
-Blabla
+The above command also automatically requests to install dependency packages.
+Note that we install `ggmirt` directly from its GitHub repository because `ggmirt` is not yet available in the Comprehensive R Archive Network (CRAN).
+Next, we should activate the R packages by typing a command as follows:
 
 ```{r}
-library(ggmirt); library(tidyverse); library(psych); library(mirt); library(caret)
+library(mirt); library(ggmirt); library(psych); library(tidyverse); library(caret)
 ```
 
-Blabla
+Now after the packages are activated, we need to import the dataset to our R environment.
+The dataset (`data.csv`) and codebook (`codebook.txt`) are available in `data` folder in our repository.
+Readers can download them from our repository and then simply import the dataset with this following command:
 
@@
 
-Blabla
+However, since the dataset is openly accessible in the Open Psychometrics webpage, readers can also directly import the dataset from the Open Psychometrics webpage to their R environment.
+For interested readers, we show how to do this in detail in our annotated R script file.
+
+Next, it is important to examine the structure of the data frame (`ds`) to get a glimpse of its structure.
+By typing `str()` command, readers can examine the variables' name, number of cases, types of variables (integer or character), and the values of each variable.
+Then readers can match the information provided in their R console to the codebook.
 
@@
 
-Blabla
+According the information provided in the codebook, the responses to the RWA scale are denoted in `Q1` to `Q22`, each represents score of each item of the RWA scale.
+Readers can also see the information of `Q1` to `Q22` variables in their R console: these variables are integer and have values ranging from 1 to 9.
+In the codebook, there is no information regarding what these values (i.e., 1-9) mean.
+However, we could reasonably assume that participants who chose "*strongly disagree*" (-4) were scored `1`, and those who opted for "*strongly agree*" (+4) were scored `9`.
+
+Please note that we are only interested in the responses of the RWA scale, so we should subset the dataset to contain only the variables we are interested in, and then, examine the structure again.
+To this end, readers can type these commands:
 
@@
 
-Blabla
+Here, we have a new data frame namely `rwa`, which contains only the responses to the RWA scale (`Q1:Q22`).
+In the data frame `rwa`, we have 22 variables with 9,881 participants.
+Before proceeding to the analysis stage, we recommend readers to inspect descriptive statistics, which we explain the procedure in the next sub-section.
 
 ## Step 2: Inspecting Key Descriptive Statistics
+
+To efficiently examine descriptive statistics, readers can make use of `describe()` function from *psych* package [@revellePsychProceduresPsychological2023] by typing a simple command:
 
@@
 
-As we see in {apatb-table2}, Kok ada nilai 0-nya? padahal kan skor minimalnya 1. Coba kita hitung frekuensi nilai 0 di tiap item.
+This command summarizes key descriptive statistics of a data frame, and the summary is provided in {apatb-table2}.
+As we see in {apatb-table2}, all variables have minimum value of `0`, while the minimum score should be `1`.
+Again, there is no information provided in the codebook regarding what `0` actually represents.
+Therefore, before deciding what we should do next, it is better to find out how many `0` we have in the data frame.
+To this end, we can calculate the percentage of `0` in each item by running these commands:
 
 ```{r}
-zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the frequency of "0" in each column.
-print(zero) # The proportion of "0" for each item.
+zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
+print(zero) # Examining the proportion of "0" for each item.
 ```
 
-Kita anggap nilai 0 adalah NA dan kita delete semua case dengan nilai NA
+After executing these commands, readers can view the percentage of `0` in each items in their R console, which overall are very small, ranging from 0.09% to 0.32% of the total cases.
+Since the percentages are very small, it is very likely that `0` is a code for a missing value.
+It is important to note that *mirt* package uses the Expected-Maximization (EM) algorithm to estimate model parameters, and the EM algorithm can handle missing values [@chalmersMirtMultidimensionalItem2012].
+If we decide to eliminate cases with missing values, we still have a sizable number of cases, nonetheless.
+Therefore, to simplify our analysis, we only keep cases with complete responses by executing these commands:
 
@@
 rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
-  drop_na()  # Removing cases with any NA values.
+  mutate_all(~na_if(., 0)) %>%  # Recoding "0" with "NA" in all columns.
+  drop_na()  # Removing cases with any "NA" values.
 ```
 
-Kalau lihat di {apatb-table2}, meannya kok beda2? oh iya karena ada unfavorable items. Ayo kita reverse score dulu ya.
+If readers prefer to keep cases with missing values, especially when the sample size is low, readers can exclude `drop_na()` command.
+
+Interestingly, if we look {apatb-table2} again, mean score of the items seem to differ drastically.
+Some items have high mean scores, ranging from 6 to 7, but some of those are comparatively low.
+The RWA scale indeed has some unfavorable items but, again, there is no information in the codebook whether these unfavorable items have been reversely coded.
+However, if we look closely at ten items with high mean ($\bar{x}$ > 6), these are the items that are supposed to be unfavorable.
+Therefore, we can reasonably assume that unfavorable items have not been reversed in the original dataset, and we should do so by running these commands:
 
@@
 
+First, we define a vector namely `unfav` to identify which items should be reversed, and then we use `mutate()` function to reverse the score.
+This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
+We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now items' mean do not drastically vary and have `1` as its minimum value.
+
 ## Step 3: Examining Dimensionality
+
+Next, we show the readers the ways of testing a key assumption of an IRT model, namely unidimensionality.
+To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggests three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
+In this tutorial, we decide to use EFA, and *psych* package provides a very efficient way to do this is by calling this simple command:
 
@@
 
-lalalala
+`irt.fa` function is to run an EFA with a polychoric correlation matrix as an input, not a Pearson's correlation matrix, because our data is ordinal.
+The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data [@harmanFactorAnalysisMinimizing1966].
+Alternatively, readers can also run a parallel analysis with a polychoric correlation matrix by calling this following command:
 
@@
 
-fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa", cor = "poly")
+fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa", cor = "poly")
 ```
 
-lalalalal
+A parallel analysis compares the eigenvalues from the data with those yielded from a randomly generated dataset with the same sample size in order to determine the number of factors one should retain in EFA [@guoAssessingDimensionalityIRT2023].
+The codes indicate that we tell R to run a parallel analysis on the data frame `rwa`, with one factor.
+The option `fa="fa"` implies that we want to show the eigenvalues for a EFA, while `cor = "poly"` means that we use a polychoric correlation matrix as an input.
+
+The call to both commands above produces this following error: `Error in polychoric(x): You have more than8 categories for your items, polychoric is probably not needed`.
+Since we have more than eight response categories, we should instead run an EFA with a Pearson's correlation matrix as an input.
+Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run a EFA by calling these following commands:
 
 ```{r}
-cor <- cor(rwa,method="pearson") # First, creating a (pearson) correlation matrix.
-efa <- fa(rwa, nfactors=1, fm="minres") # Now, running exploratory factor analysis. 
+cor <- cor(rwa, method = "pearson") # First, creating a Pearson's correlation matrix.
+efa <- fa(rwa, nfactors = 1, fm = "minres") # Now, running EFA.
 print(efa) # Print the results.
@@
 
-Scree plot
-
-Now lets do parallel analysis
+After calling the commands, readers can find `Proportion Var` in the output, which reflects the amount of variance explained by a latent factor.
+The variance proportion of our EFA model is 0.56, which means that 56% of total variance is explained by a latent factor.
+Since the latent factor can account for more than 50% of variance, we can reasonably assume that the latent factor underlying our data is indeed unidimensional.
+To better visualize the eigenvalues of the EFA, we can draw a scree plot using these following commands:
 
 ```{r}
-pa <- fa.parallel(rwa, fm="minres", fa="fa")
+#| eval: false
+
+plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
+abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
 ```
 
-lalalala
+The first line of code is a function to plot the Eigenvalues (`efa$values`, x-axis) given the number of latent factors (y-axis).
+The option `type = "b"` implies that we ask R to display the Eigenvalues exact points and a line connecting these points along the number of factors.
+The second line of code aims to display a horizontal red line (i.e., a reference line) to see which factors have eigenvalues greater than one, which is a common criterion for factor retention.
+{apafg-fig2} shows that there is a clear break or an "elbow" that displays the location where the Eigenvalues start to level off.
+This implies that factors beyond 1 may not be meaningful and could just represent noise.
+Therefore, the scree plot strengthens our assumption that the item pool is, indeed, unidimensional.
+
+To support unidimensionality assumption, we can also run a parallel analysis by running this following command:
+
+```{r}
+pa <- fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa")
+```
+
+Readers may find a plot similar to {apafg-fig3} should appear right after executing this code, as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
+This means that the parallel analysis suggests that there are six factors underlying our item pool, not one.
+However, according to {apafg-fig3}, we can see clearly that the Eigenvalues from our actual data fall steeply after the first factor.
+To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running this following command:
 
@@
 
-Eigenvalues `12.225/0.843`
+The output shows that the Eigenvalues for the first factor is much larger than the its adjacent factor (`12.225/0.843`), strengthening the evidence for unidimensionality.
 
@@
 #| apa-cap: Item Parameters
-#| apa-note: λ = Standardized Factor Loadings, h2 = Commonality, α = Discrimination, β1.4 = Response specific difficulty parameters (item threshold).
+#| apa-note: λ = Standardized Factor Loadings, h2 = Commonality, a = Discrimination, b1-b8 = Response specific threshold parameters.
 #| ft.align: left
@@
   select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, rwa, h2) %>% 
-  rename(α=a, β1=b1, β2=b2, β3=b3, β4=b4, β5=b5, β6=b6, β7=b7, β8=b8, λ=rwa) %>% 
+  rename(λ=rwa) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table3 <- colformat_double(x=table3, j="α", digits = 2)
-table3 <- colformat_double(x=table3, j="β1", digits = 2)
-table3 <- colformat_double(x=table3, j="β2", digits = 2)
-table3 <- colformat_double(x=table3, j="β3", digits = 2)
-table3 <- colformat_double(x=table3, j="β4", digits = 2)
-table3 <- colformat_double(x=table3, j="β5", digits = 2)
-table3 <- colformat_double(x=table3, j="β6", digits = 2)
-table3 <- colformat_double(x=table3, j="β7", digits = 2)
-table3 <- colformat_double(x=table3, j="β8", digits = 2)
+table3 <- colformat_double(x=table3, j="a", digits = 2)
+table3 <- colformat_double(x=table3, j="b1", digits = 2)
+table3 <- colformat_double(x=table3, j="b2", digits = 2)
+table3 <- colformat_double(x=table3, j="b3", digits = 2)
+table3 <- colformat_double(x=table3, j="b4", digits = 2)
+table3 <- colformat_double(x=table3, j="b5", digits = 2)
+table3 <- colformat_double(x=table3, j="b6", digits = 2)
+table3 <- colformat_double(x=table3, j="b7", digits = 2)
+table3 <- colformat_double(x=table3, j="b8", digits = 2)
 table3
@@
 #| apa-cap: Item Fit Statistics
-#| apa-note: Scaled χ2 Statistics. RMSEA = root mean square error of approximation, CFI = comparative fit index, TLI = Tucker-Lewis index, SRMR = Standardized Root Mean Square Residual.
+#| apa-note: Scaled χ2 Statistics. RMSEA = Root Mean Square Error of Approximation, CFI = Comparative Fit Index, TLI = Tucker-Lewis Index, SRMR = Standardized Root Mean Square Residual.
 #| ft.align: left

### 2024-01-15 codes.R

@@ -167,12 +167,12 @@ print(efa) # Print the results.
 
 # Let's see the scree plot.
 plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
-abline(h = 1, col = "red", lty = 2) # Add new line to factor 1.
+abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
 
 # As we see in the plot, the Eigenvalue significantly levels off after one factor, which further substantiates our assumption.
 # However, let's run a parallel analysis, since this approach is better than running an EFA.
 
-pa <- fa.parallel(rwa, fm="minres", fa="fa") # Running a parallel analysis.
+pa <- fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa") # Running a parallel analysis.
 pa$fa.values # Seeing the eigenvalues of each factor.
 
 # Again, from the plot and the Eigenvalues (12.22/0.84), we can conclude that one latent factor is sufficient, 

### 2024-01-16 draft_paper.qmd
Step 5 done!

@@
 IRT, on the other hand, models this relationship in a *probabilistic* rather than a linear fashion.
-More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\Theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, if necessary, guessing [@bakerBasicsItemResponse2017].
+More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, if necessary, guessing [@bakerBasicsItemResponse2017].
 
@@
 A concrete example of this is a study scrutinizing the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
-According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\Theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
+According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
 Therefore, IRT models offer a more informative and nuanced perspective, proving useful for researchers who wish to closely examine the performance of their measures.
 
-Further, IRT allows researchers to examine the performance of a specific item (hence "item" response theory) by specifying the relationship between item score and $\Theta$ given one-, two-, or three-parameter.
+Further, IRT allows researchers to examine the performance of a specific item (hence "item" response theory) by specifying the relationship between item score and $\theta$ given one-, two-, or three-parameter.
 One-parameter logistic (1PL) or Rasch model, the simplest variant of the IRT models, accounts only item difficulty (*b*) while presuming equal item discrimination (*a*) across items.
-Practically, this model slightly overlaps with CTT in the sense that they assume that all items carry equal informative value thus the estimated $\Theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
+Practically, this model slightly overlaps with CTT in the sense that they assume that all items carry equal informative value thus the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
 This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measurements remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
-Put simply, Rasch model assumes that the latent trait ($\Theta$) should remain unaffected by specific items used in the test.
+Put simply, Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
 For example, the difference in depression levels between two individuals should be always the same regardless of the scale used to measure their depression levels.
@@
 
-Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing item ability to differentiate individuals with varying levels of $\Theta$ (i.e., item discrimination parameter - *a*) to differ.
-Additionally, in some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\Theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*) to differ.
+Additionally, in some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
 The field of IRT has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
@@
 The fundamental idea of GRM is to extend the logic of simpler dichotomous IRT models to polytomous scales by applying a probabilistic function to each response category.
-In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\Theta$, item difficulty, and item discrimination.
+In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\theta$, item difficulty, and item discrimination.
 GRM extends this idea by modeling the probability of picking a certain response category or higher on an item (i.e., *step function*) given to item difficulty and discrimination.
-For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\Theta$.
+For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\theta$.
 Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold) in order to handle ordered polytomous data.
@@
 Imagine these categories are hierarchically ordered from the lowest category (*strongly disagree*) to the highest (*strongly agree*), like a staircase.
-GRM aims to estimate the level of sadistic personality ($\Theta$) required for "stepping" from one response category to another (e.g., *moderately agree* to *strongly agree*).
-Therefore, a GRM model of a five-point Likert scale calculates four item threshold parameters (*b*): the location of $\Theta$ level where individuals are equally likely to respond 1 or 2 (*b*~1~), 2 or 3 (*b*~2~), 3 or 4 (*b*~3~), and 4 or 5 (*b*~4~).
+GRM aims to estimate the level of sadistic personality ($\theta$) required for "stepping" from one response category to another (e.g., *moderately agree* to *strongly agree*).
+Therefore, a GRM model of a five-point Likert scale calculates four item threshold parameters (*b*): the location of $\theta$ level where individuals are equally likely to respond 1 or 2 (*b*~1~), 2 or 3 (*b*~2~), 3 or 4 (*b*~3~), and 4 or 5 (*b*~4~).
 Each threshold is exactly the point where a participant is equally likely to respond to either of the adjacent response categories.
@@
 Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item of a scale with five response categories.
-In general, IPF describes a relationship between $\Theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\Theta$).
-{apafg-fig1} consists of five category probability curves, each of which represents the probability of endorsing a response category given $\Theta$.
-Item threshold is exactly the location of $\Theta$ where two adjacent category probability curves cross each other.
+In general, IPF describes a relationship between $\theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\theta$).
+{apafg-fig1} consists of five category probability curves, each of which represents the probability of endorsing a response category given $\theta$.
+Item threshold is exactly the location of $\theta$ where two adjacent category probability curves cross each other.
 
@@
 Before running an analysis, researchers need to be aware of assumption underlying a GRM model.
-The first key assumption is that $\Theta$ is monotonically correlated with the probability of endorsing a response category.
-In other words, individuals with higher levels of $\Theta$ have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
+The first key assumption is that $\theta$ is monotonically correlated with the probability of endorsing a response category.
+In other words, individuals with higher levels of $\theta$ have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
 For instance, people with higher tendency of sadistic personality have a greater chance of answering "*moderately agree*" or "*strongly agree*" on a sadism scale compared to those with lower levels of sadism.
 
-The second key assumption pertains to unidimensionality of $\Theta$.
-This implies that the item pool tested using a GRM analysis should represent only one latent trait ($\Theta$).
-Although it is indeed possible to account for multiple $\Theta$ in a IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
+The second key assumption pertains to unidimensionality of $\theta$.
+This implies that the item pool tested using a GRM analysis should represent only one latent trait ($\theta$).
+Although it is indeed possible to account for multiple $\theta$ in a IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
 An unidimensional IRT model can still be robustly applied to multidimensional data if multiple latent traits are moderately intercorrelated or when there is a strong general factor (*g*) underlying the data [@reiseEvaluatingImpactMultidimensionality2015].
-To test whether an item pool represents only one $\Theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
+To test whether an item pool represents only one $\theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
 
@@
 As an eyeball example - consider a trust in science scale containing these two items: "*I trust scientists working in the natural science*" and "*most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in the natural science are very likely to also trust biologists.
-To inspect whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\Theta$ using residual correlation analysis [@chenLocalDependenceIndexes1997].
+To inspect whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\theta$ using residual correlation analysis [@chenLocalDependenceIndexes1997].
 
@@
 
-## Step 1: Preparation
+## Step 1: Data Preparation
 
@@
 ```{r}
-install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE)
-devtools::install_github("masurp/ggmirt") # remote installation through GitHub repository
+install.packages("tidyverse", # for data wrangling
+                 "psych", # for descriptive statistics and unidimensionality test
+                 "devtools", # for installing R package that is not available on CRAN
+                 "mirt", # for conducting the main GRM analysis
+                 "caret", # for helping us detecting large residuals correlation (local independence test)
+                 dependencies=TRUE)
+devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
 ```
@@
 The above command also automatically requests to install dependency packages.
-Note that we install `ggmirt` directly from its GitHub repository because `ggmirt` is not yet available in the Comprehensive R Archive Network (CRAN).
+Note that we install *ggmirt* directly from its GitHub repository because *ggmirt* is not yet available in the Comprehensive R Archive Network (CRAN).
 Next, we should activate the R packages by typing a command as follows:
@@
 zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
-print(zero) # Examining the proportion of "0" for each item.
+print(zero) # Showing the percentage of "0" for each item.
 ```
@@
 The variance proportion of our EFA model is 0.56, which means that 56% of total variance is explained by a latent factor.
-Since the latent factor can account for more than 50% of variance, we can reasonably assume that the latent factor underlying our data is indeed unidimensional.
-To better visualize the eigenvalues of the EFA, we can draw a scree plot using these following commands:
+Since the latent factor can account for more than 50% of variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
+To better visualize the Eigenvalues of the EFA, we can draw a scree plot using these following commands:
 
@@
 {apafg-fig2} shows that there is a clear break or an "elbow" that displays the location where the Eigenvalues start to level off.
-This implies that factors beyond 1 may not be meaningful and could just represent noise.
+This implies that factors beyond the first may not be meaningful and could be only noise.
 Therefore, the scree plot strengthens our assumption that the item pool is, indeed, unidimensional.
 
-To support unidimensionality assumption, we can also run a parallel analysis by running this following command:
+To scrutinize unidimensionality assumption, we can also run a parallel analysis by running this following command:
 
@@
 
-Readers may find a plot similar to {apafg-fig3} should appear right after executing this code, as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
+Readers should find a plot similar to {apafg-fig3} appear right after executing this code as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
 This means that the parallel analysis suggests that there are six factors underlying our item pool, not one.
@@
 
+In this step, we start to specify a vector representing our model specification, such as:
+
 ```{r}
@@
 
-lalalala
+This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are column 1 to 22 of the data frame that we are going to use in the analysis.
+Then, we can continue to model fitting by typing this following command:
 
 ```{r}
-fit <- mirt(data=rwa, 1, model=model, itemtype="graded", SE=T, verbose=F)
+fit <- mirt(data = rwa, 1, model = model, itemtype = "graded", SE = TRUE, verbose = FALSE)
 ```
 
-llalalala
+The code above implies that we are fitting an IRT model using data from a data frame namely `rwa` (`data = rwa`).
+The number `1` indicates that we presume that the model contains only one $\theta$, i.e., unidimensional.
+We also set the model specification to `model = model`, which we have previously determined.
+We set `itemtype` to `"graded"` because we want to run a GRM model.
+The `SE` option is set to `TRUE` because we ask R to also estimate the standard error.
+At last, we set the `verbose` option to `FALSE` to avoid R displaying unnecessary information during the model fitting process, so the `mirt()` function can run quietly.
+
+Apart from this tutorial, readers might encounter four common error messages after running `mirt()` function: (a) `EM cycles terminated after 500 iterations`, (b) `Could not invert information matrix; model may not be empirically identified`, (c) `The following items have only one response category and cannot be estimated`, and (d) `Error in [<-(*tmp*, i, nms[[i]], value = items.old[[i]]) : subscript out of bounds`.
+Error messages (a) and (b) correspond to the convergence issue, while (c) and (d) are issues related to the data structure.
+
+*mirt* uses the EM algorithm as a default option.
+In short, the EM algorithm estimates model parameters in two steps: the expectation (E) and the maximization (M) steps.
+In the E step, the algorithm estimates the expected value of the $\theta$, and in the M step, it improves model parameters to maximize the likelihood of the observed data given the expected value of $\theta$.
+The process continues until model parameters are converged in stable values that fit to the data.
+If the error message (a) appears, it means that the package cannot estimate a stable solution for model parameters after 500 iterations.
+As a solution, readers can simply increase the maximum number of iterations to, for instance, 1000 cycles by adding this option `technical = list(NCYCLES = 10000)` to the `mirt()` function.
+
+The solution to error message (b) is less straightforward than (a) because it indicates that the model cannot be identified at all, which can have several causes.
+It could be due to an error in specifying assumptions about the number of latent traits or item properties, or it could be due to insufficient sample size.
+Therefore, when error message (b) appears, it is important to take a step back and think twice about the model assumptions, the fit between the model and the underlying theory, and whether the sample size is large enough to estimate the model properly.
+
+The error message (c) and (d) are easier to solve because both indicate the error are related to the data structure.
+The former means that certain items have no variance, consisting only one response category.
+The solution for this issue is to exclude these items from model estimations.
+The latter indicates a mismatch between the vector of model specification and the data frame, for instance, specifying a vector with ten variables, while in fact, the data frame has only nine columns.
+To solve this issue, readers are suggested to check again whether the specified vector representing the model specification matches the structure of the data frame.
+
+Next, we can ask the package to calculate item discrimination and thresholds by calling these functions below:
 
 ```{r}
-coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
-print(coefs) # Yielding model parameters: item discrimination (a) and threshold (b).
+coefs <- coef(fit, IRTpars=TRUE, simplify=TRUE) # Saving model parameters (item discrimination (a) and threshold (b)) in a data frame.
+print(coefs) # Calling the data frame.
+summary(fit) # Displaying factor loadings and commonality.
 ```
 
-lalalala
+The first line of code indicates that we are calling a `coef()` function to calculate item parameters from `fit` model, and then, store them in a new data frame called `coefs`.
+The `IRTpars` and `simplify` option is set to `TRUE` because we want to display the traditional IRT parameters (*a* and *b*) in a simple, readable format without showing the standard errors.
 
-```{r}
-summary(fit) 
-```
+The output from this procedure is presented in {apatb-table4}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
+To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorize item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
+As we seen in {apatb-table4}, item discrimination parameters of the RWA scale are ranging from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
+All threshold parameters  show a consistent increase, implying that those with higher RWA levels tend towards higher response categories.
+However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
+This might suggest that the RWA scale is less sensitive to measure individuals with a low or very low RWA level.
 
-bla bla lhalalala
+The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which both are also provided in {apatb-table4}.
+Before estimating a graded response model, *mirt* ran an EFA, and now as we can see in the console, we are looking at the EFA results.
+The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
+However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.
+
+Next, we can estimate the model goodness-of-fit (GOF) statistics (*M*~2~) by calling this command below:
 
@@
 ```
-
-lhalalala
-
 ```{r}
@@
 
-According to our analysis, the model does not fit the data well (*M*(`r df`) = `r m2_stat`, *p* = `r p_value`, *RMSEA* = `r rmsea`, )
+We ask the package to calculate the scaled *M*~2~ statistics [@maydeu-olivaresLimitedInformationGoodnessoffit2006] and other GOF indices, such as Root Mean Square Error of Approximation (RMSEA), Comparative Fit Index (CFI), Tucker-Lewis Index (TLI), and Standardized Root-Mean-Square Residual (SRMSR) by running this code above.
+Here, we set the `type` option to `"C2"` because it is suitable for computing *M*~2~ statistics in polytomous models.
+The interpretation of GOF statistics are similar to a general guide of interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003].
+
+According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* = `r p_value`, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), and this may be caused by local dependency between the items.
+We will explore this issue further in the next part.
+
+Next, we calculate item-level fit statistics, i.e., the scaled $\chi$^2^ statistics, by running this following function:
 
 ```{r}
-item.fit <- itemfit(fit)
+item.fit <- itemfit(fit) # Estimating item fit statistics and saving them in a data frame.
+print(item.fit) # Calling the data frame.
 ```
+
+The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
+All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying there is no discrepancy between the model and data.
+In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
 
@@
 #| apa-cap: Item Parameters
-#| apa-note: λ = Standardized Factor Loadings, h2 = Commonality, a = Discrimination, b1-b8 = Response specific threshold parameters.
+#| apa-note: a = Discrimination, b1-b8 = Response specific threshold parameters, λ = Standardized Factor Loadings, h2 = Commonality.
 #| ft.align: left

### 2024-01-16 codes.R

@@ -15,8 +15,16 @@
 # First of all, we should install the packages we need for the analysis. If you already have these packages  
 # already installed in your device, you can safely skip this step.
 
-# install.packages("tidyverse", "psych", "devtools", "mirt", "caret", dependencies=TRUE) 
+# install.packages("tidyverse", # for data wrangling
+# "psych", # for descriptive statistics and unidimensionality test
+# "devtools", # for installing R package that is not available on CRAN
+# "mirt", # for conducting the main GRM analysis
+# "caret", # for helping us detecting large residuals correlation (local independence test)
+# dependencies=TRUE)
+
 ## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
+
+devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
 
 # Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
 
@@ -88,8 +96,8 @@ psych::describe(rwa)
 
 # Let's count how many "0" we have in our data.
 
-zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the frequency of "0" in each column.
-print(zero) # The proportion of "0" for each item.
+zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
+print(zero) # Showing the percentage of "0" for each item.
 rm(zero) # Removing the unused vector
 
 # We have a few cases with "0" in all items. 
@@ -200,11 +208,11 @@ print(coefs) # Yielding model parameters: item discrimination (a) and threshold 
 # Baker (2017). RWA items, in general, have a moderate to very high ability to differentiate participants with different theta levels.
 # We can see that most items have 8 item threshold each (b1-b8), and this is because we have nine response options.
 
-summary(fit) # Yielding factor loadings and communality (h2) from mirt model.
+summary(fit) # Displaying factor loadings and commonality.
 
 # Before estimating a graded response model, mirt ran an EFA, and now as we can see in the console,
 # we are looking at the EFA results. The results are slightly different from our previous EFA analysis,
-# because mirt EFA using a quasi polychoric correlation matrix, while the one we ran earlier used a pearson 
+# because mirt runs EFA using a quasi polychoric correlation matrix, while the one we ran earlier used a pearson 
 # correlation matrix. However, most importantly, we see that all items are significantly loaded to one factor, 
[…]

### 2024-01-17 draft_paper.qmd
Step 6 done!

@@
 ```{r}
-psych::describe(rwa)
+describe(rwa)
 ```
@@
 This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
-We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now items' mean do not drastically vary and have `1` as its minimum value.
+We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items do not drastically vary and have `1` as its minimum value.
 
@@
 
-Next, we show the readers the ways of testing a key assumption of an IRT model, namely unidimensionality.
+Next, we show the readers the ways of testing unidimensionality.
 To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggests three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
-In this tutorial, we decide to use EFA, and *psych* package provides a very efficient way to do this is by calling this simple command:
+In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this is by calling this command:
 
@@
 ```{r}
-pa <- fa.parallel(rwa, nfactors = 1, fm="minres", fa="fa")
+pa <- fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa")
 ```
@@
 
-The output shows that the Eigenvalues for the first factor is much larger than the its adjacent factor (`12.225/0.843`), strengthening the evidence for unidimensionality.
+The output shows that the Eigenvalues for the first factor is much larger than the its adjacent factor (`12.225/0.843`), further supporting for the evidence for unidimensionality.
 
@@
 ```{r}
-coefs <- coef(fit, IRTpars=TRUE, simplify=TRUE) # Saving model parameters (item discrimination (a) and threshold (b)) in a data frame.
+coefs <- coef(fit, IRTpars = TRUE, simplify = TRUE) # Saving model parameters (item discrimination (a) and threshold (b)) in a data frame.
 print(coefs) # Calling the data frame.
@@
 ```{r}
-M2(fit, type="C2")
+M2(fit, type = "C2")
 ```
@@
 The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
-All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying there is no discrepancy between the model and data.
+All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying there is no discrepancy between the observed response pattern with what the model predicts.
 In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
@@
 
+To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of model residuals.
+First, we demonstrate how to run Local Dependency (LD) $\chi$^2^ statistics [@chenLocalDependenceIndexes1997], which looks at the covariance between item pairs after accounting for $\theta$.
+To that end, readers can run two lines of codes as follows:
+
 ```{r}
-ld <- residuals(fit, type = "LD") # Running local dependency statistics
-up <- which(upper.tri(ld), arr.ind = T) # Extracting values only on the upper side of the diagonal.
-lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # Defining unusually large residuals (>0.2).
+ld <- residuals(fit, type = "LD") # Running local dependency (LD) statistics.
+up <- which(upper.tri(ld), arr.ind = TRUE) # Creating a new matrix containing values only on the upper side of the diagonal (correlations).
 ```
 
-lhalalala
+The first line of code aims to extract residuals of `fit` model and store them as a matrix, namely `ld`.
+The `type` option is set to `"LD"` because we ask the package to calculate LD statistics of the `fit` model.
+After running the first line, readers may view a matrix containing residual covariance (in the lower diagonal) and correlations (in the upper diagonal).
+Correlations are more interpretable, so we focus on the upper side of the diagonal.
+Therefore, the second line of code is to create a new matrix containing only correlation values in the upper diagonal.
+
+We are only interested in large correlations between a pair of items because they indicate that responses to one item depend on responses to another item beyond what is explained by $\theta$.
+It is important to note that there is no consensus on a rule of thumb for the cutoff value of residual correlations because LD statistics are contingent to the parameters of a specific dataset [@christensenCriticalValuesYen2017].
+For the purpose of this tutorial, we set |0.2| as an paired correlation value that we want to look closely.
+To do so, we create a vector to define the value of residual correlations that we are interested in:
 
@@
 #| eval: false
+lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # A vector defining unusually large residuals ( > |0.2|).
+```
 
+We can then use the new vector `lar` to ask R to tell us the item pairs with residuals correlations above |0.2| by running this function:
+
+```{r}
+#| eval: false
 for (i in 1:nrow(lar)) {
@@
 
-lhalalala
+After running the function above, readers may encounter an error message: `Error in lar[i, 1] : subscript out of bounds`.
+This message indicates that R does not detect any residual correlation above |0.2|.
+To paint a clearer picture, we may need to use another way to examine model residuals.
+In the next part, we demonstrate the use of Yen's *Q*~3~ statistics [@yenEffectsLocalItem1984], which is considered more powerful for detecting underlying local dependency [@chenLocalDependenceIndexes1997].
+To run Yen's *Q*~3~, readers can type and run this command:
 
 ```{r}
-q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics
-findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlation pairs.
+q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics.
 ```
+
+This code asks R to run `residuals()` function using `"Q3"` as the `type`, and then, keep the value as a new matrix, namely `q3`.
+Again, we are only interested in item pairwise correlations above |0.2|, and to help us flag problematic pairs, we can make use of `findCorrelation()` function from *caret* package [@kuhnCaretClassificationRegression2024] as follows:
+
+```{r}
+findCorrelation(q3, cutoff = 0.2, verbose = T) # Flagging problematic item pairwise correlations.
+```
+
+After running the code, readers may see in their R console that residual correlations between item Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are above |0.2|.
+Interestingly, all of those items, except for Q4, have nonsignificant *S*-$\chi$^2^ statistics (see {apatb-table5}) as well, which tells us that we have to look at these items closely and then decide whether these items have shared characteristics beyond what is explained by the model.
 
@@
 
-Now spit out the
+*mirt* offers features to visualize model parameters but the options for customizing these plots are rather limited.
+*ggmirt* package [@masurGgmirt2023] fills this gap by combining *mirt* and *ggplot2* functions.
+In this tutorial, we demonstrate the use of *ggmirt* to visualize Item Probability Function (IPF), Item Information Function (IIF), Test Information Function (TIF), and conditional probability plot.
+
+To visualize IPF, readers can type and run this function:
 
 ```{r}
-tracePlot(fit, facet=T, title = "Category Probability Functions of RWA Scale") + labs(color="Response Options")
+tracePlot(fit, title = "Item Probability Functions of RWA Scale") + labs(color="Response Categories")
 ```
 
-lhalalala
+The `labs(color)` function is to assign different colors to each curve representing a response category.
+The output of this function is {apafg-fig4}.
+In {apafg-fig4}, we see that as $\theta$ increases, respondents are more likely to choose higher response categories.
+The gradual transition from one response option to the next across the spectrum of $\theta$ values indicates that the items are capturing incremental increases in the RWA level.
+However, all IPFs of RWA items seem to be significantly overlapping and tend to peak on a $\theta$ value close to or higher than the mean.
+This implies that RWA items are more sensitive to differentiate participants with high levels of RWA.
+
+To evaluate the performance of each item in measuring RWA trait, we can visualize the amount of information explained by each item with this simple line of code:
 
 ```{r}
-itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
+itemInfoPlot(fit, facet = TRUE, title = "Item Information Functions of the RWA Scale")
 ```
 
-lhalalala
+The `facet` option is set to `TRUE` so that R displays IIF for each item.
+The output for this function is {apafg-fig5}, where the x-axis represents the range of $\theta$, and the y-axis indicates the amount of information provided by each item.
+Peaks that are higher and narrower indicate items that are very informative for specific levels of $\theta$.
+In our case, most items provide the highest amount of information near the center to the right side of the $\theta$ distribution, indicating they are most useful for individuals with an average to high level of RWA.
+
+It is also possible to evaluate the overall performance of the RWA scale by plotting a TIF, which can be done by running this following code:
 
 ```{r}
-testInfoPlot(fit, title="Test Information Curve of the RWA Scale")
+testInfoPlot(fit, title = "Test Information Function of the RWA Scale")
 ```
+
+The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
 
@@
 ```{r}
-conRelPlot(fit, title="Reliability of the RWA Scale Given to the θ Level")
+conRelPlot(fit, title = "Reliability of the RWA Scale Given to the θ Level")
 ```
 
-lalalala
+{apafg-fig7}
 

### 2024-01-17 codes.R

@@ -90,7 +90,7 @@ str(rwa)
 # This part is fairly straightforward. Before performing analysis, it is very important to explore
 # key descriptive statistics of the data. We are using a neat function in `psych` package: (`describe()`)
 
-psych::describe(rwa)
+describe(rwa)
 # Why there are "0" values in all columns (see column "min")?
 # The items are not supposed to have "0" value because the responses are ranging from 1-9.
 
@@ -238,9 +238,9 @@ itemfit(fit) # Yielding item fit statistics.
 # In this tutorial, we will introduce two ways to examine residuals. First, we will inspect a local dependence 
 # matrix derived from the X2 statistics (Chen & Thissen, 1997), and second, we will look at Yen's Q3 statistics. 
 
-ld <- residuals(fit, type = "LD") # Running local dependency statistics
-up <- which(upper.tri(ld), arr.ind = T) # Extracting values only on the upper side of the diagonal.
-lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # Defining unusually large residuals (>0.2).
+ld <- residuals(fit, type = "LD") # Running local dependency (LD) statistics.
+up <- which(upper.tri(ld), arr.ind = T) # Creating a new matrix containing values only on the upper side of the diagonal (correlations).
+lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # A vector defining unusually large residuals ( > |0.2|).
 
 for (i in 1:nrow(lar)) {
   row <- lar[i, 1]
@@ -253,7 +253,7 @@ for (i in 1:nrow(lar)) {
 
 # Let's see how Yen's Q3 statistics look like.
 q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics
-findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlation pairs.
+findCorrelation(q3, cutoff = 0.2, verbose = T) # Flagging problematic item pairwise correlations.
 # As we see here in the console that items Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are problematic.
 
 ## Step 6: Plots (item characteristics curve, item information curve, and test information curve) ##   ------
@@ -262,16 +262,16 @@ findCorrelation(q3, cutoff = 0.2, verbose = T) # Detecting problematic correlati
 # Let's take a look at the curves to closely examine the items.
 
 # Plotting Item Probability Functions (CPF)
[…]

### 2024-01-17 draft_paper.qmd
All steps done!

@@
 abstract: "This tutorial paper introduces the Graded Response Model (GRM), a tool for testing measurement precision under the Item Response Theory (IRT) paradigm.
-Addressing common problems of measurement imprecision and lack of construct validity, the tutorial guides researchers through a one-dimensional GRM analysis in the R environment, using psych, mirt, and ggmirt packages.
-GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous items.
+Addressing common problems of measurement imprecision and lack of construct validity, the tutorial guides researchers through a unidimensional GRM analysis in the R environment, using psych, mirt, and ggmirt packages.
+GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous (Likert-style) items.
 The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, model fitting, interpretation of results, and dealing with common issues and anomalies that may typically arise in the process."
@@
 The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
-All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying there is no discrepancy between the observed response pattern with what the model predicts.
+All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying that there is no discrepancy between the observed response pattern with what the model predicts.
 In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
@@
 
-The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
+The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring a group of individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
+However, the RWA scale is not optimal for measuring individuals with RWA levels below or beyond this range.
 
@@
 
+The heart of an IRT analysis is to estimate the precision of the measure, which can vary given different levels of   $\theta$.
+*mirt* provides two strategies to compute reliability that differs in their assumption regarding the distribution of $\theta$.
+First, readers may calculate marginal reliability by running this simple command:
+
 ```{r}
+marginal_rxx(fit)
+```
+```{r}
+#| include: false
+
 m_rel <- marginal_rxx(fit)
+m_rel = round(m_rel, digits=3)
 ```
 
-lhalalala
+The output of the above code is `r m_rel`, which indicates that the RWA scale as a whole is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
+Since reliability can vary across different levels of $\theta$, readers can also visualize the scale's reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
 
@@
 
-{apafg-fig7}
+The output of this code is {apafg-fig7}, which shows that the RWA scale can measure individuals with $\theta$ levels between -2*SD* and +4*SD* with sufficient reliability, i.e., *r*~xx~ $\geq$ 0.75.
+
+Second, *mirt* can also calculate the RWA scale overall reliability using $\theta$ predicted by the model.
+To compute empirical reliability, one needs to calculate estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
+To do this, readers can run these two lines of codes:
 
 ```{r}
-theta_se <- fscores(fit, full.scores.SE = T) # Extracting the estimated theta score of each participant.
-e_rel <- empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
+theta_se <- fscores(fit, full.scores.SE = TRUE) # Extracting the estimated theta score of each participant.
+empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
+```
+```{r}
+#| include: false
+
+e_rel <- empirical_rxx(theta_se)
+e_rel = round(e_rel, digits=3)
 ```
 
-lhalalala
+The `fscores()` function is used to compute the estimated $\theta$ value for each participant predicted by the `fit` model.
+The `full.scores.SE` is set to `TRUE` because the package uses the $\theta$ value and standard error of each participant (*SE*~$\theta$~) to compute the empirical reliability.
+We store the estimated $\theta$ and its *SE*~$\theta$~ in a new data frame, namely `theta_se`, and then run `empirical_rxx()` function to calculate empirical reliability.
+The output of these codes is `r e_rel`, which is very close to marginal reliability.
+However, it is very important to note that while marginal and empirical reliability aim to quantify the scale's overall reliability, they base the calculations on different assumptions.
+Marginal reliability assumes that $\theta$ is normally distributed, and empirical reliability uses $\theta$ distribution predicted by the model, which still contains measurement errors but more realistic.
+
+It is very important to note that our model has a poor fit, as we showed in step 4.
+In practice, we recommend that readers address the model fitting issues before interpreting reliability or drawing substantive conclusions based on these estimates.
+
+To paint a more comprehensive picture, we can compare IRT-based reliability calculations with unweighted sum-score based reliability, such as Cronbach's $\alpha$ and McDonald's $\omega$.
+To do this, we can use `omega()` function provided by *psych* package [@revellePsychProceduresPsychological2023], which can be done by running this command:
 
@@
 ```
+```{r}
+#| include: false
+
+om <- omega(rwa)
+alpha <- om$alpha
+alpha = round(alpha, digits = 3)
+oh <- om$omega_h
+oh = round(oh, digits = 3)
+```
+
+The output of `omega()` function includes many information but we only focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
+Both Cronbach's $\alpha$ ($\alpha$ = `r alpha`) and McDonald's $\omega$ ($\omega$~h~ = `r oh`) shows that the RWA scale is overall internally consistent.
 

### 2024-01-17 codes.R

@@ -289,7 +289,7 @@ empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical re
 # Reliability seems to be pretty good.
 
 # Now we need to calculate marginal reliability.
-marginal_rxx(fit) # Calculating marginal reliability.
+m_rel <- marginal_rxx(fit) # Calculating marginal reliability.
 # Marginal reliability is almost similar to empirical reliability.
 
 # ...and then plot the marginal reliability across the latent trait spectrum.

### 2024-01-17 draft_paper.qmd
minor language correction

@@
 
-Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023a], *ggmirt* [@masurGgmirt2023], *tidyverse* [@wickhamWelcomeTidyverse2019], *caret* [@kuhnCaretClassificationRegression2024], and *devtools* [@wickhamDevtoolsToolsMake2022], with these following commands:
+Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023], *ggmirt* [@masurGgmirt2023], *tidyverse* [@wickhamWelcomeTidyverse2019], *caret* [@kuhnCaretClassificationRegression2024], and *devtools* [@wickhamDevtoolsToolsMake2022], with these following commands:
 
@@
 We store the estimated $\theta$ and its *SE*~$\theta$~ in a new data frame, namely `theta_se`, and then run `empirical_rxx()` function to calculate empirical reliability.
-The output of these codes is `r e_rel`, which is very close to marginal reliability.
-However, it is very important to note that while marginal and empirical reliability aim to quantify the scale's overall reliability, they base the calculations on different assumptions.
-Marginal reliability assumes that $\theta$ is normally distributed, and empirical reliability uses $\theta$ distribution predicted by the model, which still contains measurement errors but more realistic.
-
-It is very important to note that our model has a poor fit, as we showed in step 4.
-In practice, we recommend that readers address the model fitting issues before interpreting reliability or drawing substantive conclusions based on these estimates.
+The output of these codes is `r e_rel`, which is very close to marginal reliability we estimated before.
+Notably, while marginal and empirical reliability aim to quantify the overall reliability of the scale, they base the calculations on different assumptions.
+Marginal reliability assumes that $\theta$ is normally distributed, and empirical reliability uses the $\theta$ distribution predicted by the model, which still contains measurement error but is more realistic.
+Note that our model has a poor fit, perhaps due to local dependence, as we showed in steps 4 and 5.
+In practice, we recommend that readers address model fitting issues before interpreting reliability or drawing substantive conclusions based on these estimates.
 
@@
 
-The output of `omega()` function includes many information but we only focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
+The output of `omega()` function includes many information but we only need to focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
 Both Cronbach's $\alpha$ ($\alpha$ = `r alpha`) and McDonald's $\omega$ ($\omega$~h~ = `r oh`) shows that the RWA scale is overall internally consistent.

### 2024-01-18 draft_paper.qmd
v1 manuscript draft is done!

@@
 GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous (Likert-style) items.
-The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, model fitting, interpretation of results, and dealing with common issues and anomalies that may typically arise in the process."
+The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, model fitting, interpretation of results, and dealing with some common issues that may typically arise in the process."
 keywords:
@@
 The foundation of scientific research is the measurement process, which involves defining the construct to be measured, determining measurement assumptions, and evaluating measurement validity and precision.
-For instance, a researcher studying the role of authoritarian personality in explaining prejudice must first clearly define these variables, and then, develop a measurement strategy to operationalize the variables.
-This is challenging in applied psychology, as most psychological constructs are not directly observable.
+To illustrate this process, consider a researcher studying the role of authoritarian personality in explaining prejudice must first clearly define these variables, and then, develop a measurement strategy to operationalize the variables.
+This is challenging for applied psychology researchers, as most psychological constructs are not directly observable.
 To ensure a precise measurement, researchers rely on statistical techniques, assuming that these non-observable traits are "out there," or later we name this concept a *latent trait* or a *manifest variable*.
-Researchers then create tools, like scales, stimuli, tasks, observation checklists, etc., which are assumed to represent these these latent traits.
+Researchers then create tools, like scales, stimuli, tasks, observation checklists, etc., which are assumed to represent these latent traits.
 
 In psychological research, where variables are often not directly observable, construct validity, which refers to a question on whether a scale measures what it is intended to measure [@cronbachConstructValidityPsychological1955], becomes crucial.
-Construct validity, as argued by @cronbachConstructValidityPsychological1955, can be scrutinized by linking test scores to other related constructs and observations.
+Construct validity can be scrutinized by linking test scores to other related constructs and observations [@cronbachConstructValidityPsychological1955].
 Test validity relies on whether the construct behaves as theory predicts within a "nomological network" [@cronbachConstructValidityPsychological1955].
@@
 
-Over time, validity theory has evolved and has been expanded.
-Validity is now seen not as a property of a specific test, but rather lies in the consequential aspects of the test use [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
+Validity theory has evolved and has been expanded from time to time and validity is now seen not as a property of a specific test, but rather lies in the consequential aspects of the test use [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
 In this sense, a test is deemed valid when researchers can demonstrate evidence for formulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016], such as causal inference [@rutkowskiCausalInferencesLarge2016], used to defend test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
@@
 Furthermore, applied psychological researchers seem to overlook the assumptions underlying their chosen method for evaluating reliability.
-For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] and exceptionally popular [@mcneishThanksCoefficientAlpha2018], it is unclear whether researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), and thus, limits its usefulness [@sijtsmaUseMisuseVery2008].
+For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] as the most popular reliability coefficient [@mcneishThanksCoefficientAlpha2018], it is unclear whether researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), which limits its usefulness [@sijtsmaUseMisuseVery2008].
 
-With this in mind, this oversight in measurement quality can raise reasonable concerns about the replicability of research findings because measurement contributes to the (in)validity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
-Measurement oversight can be identified in decisions that researchers make, which potentially compromise the validity of the measures used in their studies, a phenomenon known as "*questionable measurement practices*" [@flakeMeasurementSchmeasurementQuestionable2020].
-Further, the lack of evidence for measurement validity contributes to the difficulty in reaching a consensus about the best way to measure a construct.
-In the long run, it becomes a major obstacle to establishing cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
-Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to assist them in evaluating measurement validity so that they can improve their measurement practices, and thus, the credibility of their findings.
+In this sense, measurements oversights can raise legitimate concerns about the replicability of research findings because measurement directly contributes to the (in)validity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
+To better identify how these oversights manifest themselves in the research process, we should pay more attention to decisions that researchers make that potentially compromise the validity of the measures used in their studies, a phenomenon known as "*questionable measurement practices*" [@flakeMeasurementSchmeasurementQuestionable2020].
+Furthermore, the lack of evidence for measurement validity contributes to the difficulty of reaching a consensus on the best way to measure a construct.
+In the long run, this is a major obstacle to the establishment of cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to help them assess measurement validity so that they can improve their measurement practices, and thus, the credibility of their findings.
 
-In this article, we aim to gently introduce the graded response model (GRM), which is a family of item response models, specifically aimed to assess the measurement precision of a polytomous (Likert-style) scale.
-We start this paper by briefly explaining the basics of Item Response Theory (IRT), the theoretical foundation of GRM, as well as contrasting its differences with the widely known Classical True Score Theory (CTT).
-In this paper, we aim to keep our tutorial concise so we do not cover all IRT concepts in detail.
+The purpose of this article is to provide a brief introduction to the Graded Response Model (GRM), a family of item response models specifically designed to assess the measurement precision of a polytomous (Likert-style) scale.
+We begin this paper by briefly explaining the basics of Item Response Theory (IRT), the theoretical foundation of GRM, and contrasting its differences with the widely known Classical True Score Theory (CTT).
+In this paper, we aim to keep our tutorial concise, so we do not cover all IRT concepts in detail.
 Interested readers are referred to available didactic texts on IRT, such as @embretsonItemResponseTheory2000 for the introductory level, and @bakerBasicsItemResponse2017 and @deayalaTheoryPracticeItem2022 for a more technical and comprehensive overview.
@@
 We also introduce three key assumptions underlying a GRM and how to test these assumptions.
-Subsequently, we provide an illustrative example of testing measurement precision using GRM, and in this part, we show how to practically implement GRM analysis and interpret its results.
+We then provide an illustrative example of testing measurement precision using GRM, and in this part, we show how to practically implement GRM analysis and interpret its results.
 We complement the illustrative example with code in the open-source programming language R [@rcoreteamLanguageEnvironmentStatistical2023] so that the readers can implement and reproduce the example presented in this paper.
-Readers with some experience with R and RStudio can easily follow this tutorial, but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials developed by @navarroPsychologicalScience2018.
+Readers with some experience in R and RStudio can easily follow this tutorial, but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials developed by @navarroPsychologicalScience2018.
 At last, we present some concluding remarks to encourage researchers to implement a GRM analysis as a part of their routine.
@@
 To scrutinize their measurement quality, psychological researchers have relied upon two foundational principles underlying psychological testing, i.e., CTT and IRT, to decompose observed score into its *deterministic* and *random* or stochastic elements [@zumboValidityFoundationalIssues2006].
-On the one hand, CTT decomposes observed score into *true* score and its *error* components.
+On the one hand, CTT decomposes observed scores into *true* score and its *error* components.
 In practice, researchers implement this principle by conducting Structural Equation Modeling (SEM), Exploratory Factor Analysis (EFA), or Confirmatory Factor Analysis (CFA).
-Specifying the measurement part of SEM, or employing EFA and CFA models, allows for the decomposition of the covariance matrix of a given data into latent factors, which represent true score or actual ability or trait level, and error terms (i.e., residuals or unique variances).
-Consequently, the relationship between observed score and true score is *linear*, as true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
+Specifying the measurement part of SEM, or employing EFA and CFA models, allows for the decomposition of the covariance matrix of a given data into latent factors, which represent true score or trait level, and error terms (i.e., residuals or unique variances).
+Consequently, the relationship between observed score and true score is *linear*, since true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
 IRT, on the other hand, models this relationship in a *probabilistic* rather than a linear fashion.
-More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, if necessary, guessing [@bakerBasicsItemResponse2017].
+More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, when appropriate, guessing [@bakerBasicsItemResponse2017].
 
@@
 Since measurement error relies on *s*, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample regardless of their trait level.
-This shortcoming restricts the utility of CTT, especially since psychologists often need to interpret individual scores, not just evaluate the test as a whole.
-Additionally, since standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is presumed to be equal across different levels of a trait or ability.
-This is unrealistic since researchers frequently encounter situations where a test is excessively difficult for a group of low-performing participants, providing little information beyond indicating that their trait or ability level is significantly lower than what the test can measure.
+This shortcoming limits the utility of CTT, especially since psychologists often need to interpret individual scores, not just evaluate the test as a whole.
+Additionally, since standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is assumed to be the same across different levels of a trait or ability.
+This is unrealistic since researchers often encounter situations where a test is overly difficult for a group of low-performing participants, providing little information beyond an indication that their trait or ability level is significantly lower than what the test can measure.
 
@@
 This approach allows for the estimation of reliability at varying levels of trait or ability (i.e., test information function - TIF).
-By doing this, when a test is overly challenging for low-performing individuals or too easy for high-performing individuals, IRT analysis can help identify the levels of trait or ability where the test is most reliable.
-A concrete example of this is a study scrutinizing the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
-According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
-Therefore, IRT models offer a more informative and nuanced perspective, proving useful for researchers who wish to closely examine the performance of their measures.
+By doing this, when a test is overly challenging for low-performing individuals or too easy for high-performing individuals, IRT can help identify the levels of trait or ability at which the test is most reliable.
+A concrete example of this is a study that examined the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
+According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring individuals with low levels of sadism [@blotnerDarkTriadDead2022].
+Therefore, IRT models offer a more informative and nuanced perspective that proves useful for researchers who wish to closely examine the performance of their measures.
 
 Further, IRT allows researchers to examine the performance of a specific item (hence "item" response theory) by specifying the relationship between item score and $\theta$ given one-, two-, or three-parameter.
-One-parameter logistic (1PL) or Rasch model, the simplest variant of the IRT models, accounts only item difficulty (*b*) while presuming equal item discrimination (*a*) across items.
-Practically, this model slightly overlaps with CTT in the sense that they assume that all items carry equal informative value thus the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
-This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measurements remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
+The one-parameter logistic (1PL) or Rasch model, the simplest variant of the IRT models, accounts only item difficulty (*b*) while assuming equal item discrimination (*a*) across items.
+In practice, this model overlaps slightly with CTT in the sense that they assume that all items have equal informative value, so that the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
+This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measures remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
 Put simply, Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
-For example, the difference in depression levels between two individuals should be always the same regardless of the scale used to measure their depression levels.
-While this principle reasonably enforces objectivity in measurement practices, it demands a strong theory delineating the construct and strict requirements of data-model fit while both assumptions rarely hold in a real-world scenario, especially in psychological science.
+For example, the difference in depression levels between two individuals should always be the same regardless of the scale used to measure their depression levels.
+While this principle reasonably enforces objectivity in measurement practices, it requires a strong theory delineating the construct and strict requirements of data-model fit while both of these assumptions rarely hold in a real-world scenario, especially in psychological science.
 
-Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*) to differ.
-Additionally, in some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
-The field of IRT has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
-It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false response), and the focus of this article is nonetheless to show the utility of IRT for fitting the ordered (Likert-style) responses.
-We briefly summarize the features of the most frequently employed IRT models in {apatb-table1}.
+Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing for differences in item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*).
+Additionally, in some contexts, researchers may suspect that some parts of the probabilistic relationship between observed score and $\theta$ is explained by guessing, thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+The field of IRT has rapidly evolved to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
+It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false responses), and the focus of this article is nonetheless to demonstrate the utility of IRT for fitting the ordered (Likert-style) responses.
+We briefly summarize the features of the most commonly used IRT models in {apatb-table1}.
 
@@
 For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\theta$.
-Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold) in order to handle ordered polytomous data.
+Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold) to handle ordered polytomous data.
 
@@
 
-Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item of a scale with five response categories.
+Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item on a scale with five response categories.
 In general, IPF describes a relationship between $\theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\theta$).
@@
 
-Before running an analysis, researchers need to be aware of assumption underlying a GRM model.
+Before running an analysis, researchers need to be aware of the assumption underlying a GRM model.
 The first key assumption is that $\theta$ is monotonically correlated with the probability of endorsing a response category.
 In other words, individuals with higher levels of $\theta$ have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
-For instance, people with higher tendency of sadistic personality have a greater chance of answering "*moderately agree*" or "*strongly agree*" on a sadism scale compared to those with lower levels of sadism.
+For instance, people with a higher tendency of sadistic personality have a greater chance of answering "*moderately agree*" or "*strongly agree*" on a sadism scale compared to those with lower levels of sadism.
 
-The second key assumption pertains to unidimensionality of $\theta$.
+The second key assumption pertains to the unidimensionality of $\theta$.
 This implies that the item pool tested using a GRM analysis should represent only one latent trait ($\theta$).
-Although it is indeed possible to account for multiple $\theta$ in a IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
-An unidimensional IRT model can still be robustly applied to multidimensional data if multiple latent traits are moderately intercorrelated or when there is a strong general factor (*g*) underlying the data [@reiseEvaluatingImpactMultidimensionality2015].
+Although it is indeed possible to account for multiple $\theta$ in an IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
+A unidimensional IRT model can still be robustly applied to multidimensional data if multiple latent traits are moderately intercorrelated or when there is a strong general factor (*g*) underlying the data [@reiseEvaluatingImpactMultidimensionality2015].
 To test whether an item pool represents only one $\theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
 
-Relatedly, a GRM model assumes that the item pool are locally independent, as the third assumption.
+Relatedly, a GRM model assumes that the item pool is locally independent, as the third assumption.
 Local independence suggests that participants' responses to one item do not influence their response to another.
 It is important to note that evidence for unidimensionality does not always warrant local independence.
-As an eyeball example - consider a trust in science scale containing these two items: "*I trust scientists working in the natural science*" and "*most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in the natural science are very likely to also trust biologists.
+As an eyeball example - consider trust in science scale containing these two items: "*I trust scientists working in natural science*" and "*Most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in natural science are very likely to also trust biologists.
 To inspect whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\theta$ using residual correlation analysis [@chenLocalDependenceIndexes1997].
@@
 To illustrate the application of GRM for analyzing measurement precision of an ordered polytomous scale, we provide an example of a GRM analysis of the RWA scale data [@altemeyerRightwingAuthoritarianism1981; @altemeyerAuthoritarians2006].
-@altemeyerRightwingAuthoritarianism1981 defines RWA as a personality propensity to blindly abide established authorities (i.e., authoritarian submission), to act aggressively toward individuals who are perceived to be punished by these established authorities (i.e., authoritarian aggression), and to uphold traditional values promoted by the authorities (i.e., conventionalism).
+@altemeyerRightwingAuthoritarianism1981 defines RWA as a personality propensity to blindly abide by established authorities (i.e., authoritarian submission), to act aggressively toward individuals who are perceived to be punished by these established authorities (i.e., authoritarian aggression), and to uphold traditional values promoted by the authorities (i.e., conventionalism).
 Individuals with higher levels of RWA tend to view the world as a dangerous place [@duckittDualProcessMotivational2017], and thus, to ensure stability and safety, they are motivated to preserve social order by deferring to those whom they perceive as legal, social, or moral authorities; for instance, the government, religious institutions, or political or religious or military leaders [@saundersRightWingAuthoritarianismScale2017].
-The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains as one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors [@akramiRightWingAuthoritarianismSocial2006; @osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
+The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors [@akramiRightWingAuthoritarianismSocial2006; @osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
 
-In this paper, we use the latest version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items that participants are asked to respond their agreement to those items on a nine-point scale, ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
+In this paper, we use the latest version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items that participants are asked to respond with their agreement to those items on a nine-point scale, ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
 While the RWA scale consists of three sub-dimensions, i.e., submissiveness, aggression, and conventionalism, the RWA scale is (theoretically) unidimensional because [@altemeyerAuthoritarians2006] shows that the sub-dimensions are strongly intercorrelated.
@@
 The dataset (`data.csv`) and codebook (`codebook.txt`) are available in `data` folder in our repository.
-Readers can download them from our repository and then simply import the dataset with this following command:
+Readers can download them from our repository and then simply import the dataset with the following command:
 
@@
 
-According the information provided in the codebook, the responses to the RWA scale are denoted in `Q1` to `Q22`, each represents score of each item of the RWA scale.
+According to the information provided in the codebook, the responses to the RWA scale are denoted in `Q1` to `Q22`, each representing the score of each item of the RWA scale.
 Readers can also see the information of `Q1` to `Q22` variables in their R console: these variables are integer and have values ranging from 1 to 9.
@@
 This command summarizes key descriptive statistics of a data frame, and the summary is provided in {apatb-table2}.
-As we see in {apatb-table2}, all variables have minimum value of `0`, while the minimum score should be `1`.
+As we see in {apatb-table2}, all variables have a minimum value of `0`, while the minimum score should be `1`.
 Again, there is no information provided in the codebook regarding what `0` actually represents.
@@
 After executing these commands, readers can view the percentage of `0` in each items in their R console, which overall are very small, ranging from 0.09% to 0.32% of the total cases.
-Since the percentages are very small, it is very likely that `0` is a code for a missing value.
+Since the percentages are very small, `0` is likely a code for a missing value.
 It is important to note that *mirt* package uses the Expected-Maximization (EM) algorithm to estimate model parameters, and the EM algorithm can handle missing values [@chalmersMirtMultidimensionalItem2012].
@@
 
-Interestingly, if we look {apatb-table2} again, mean score of the items seem to differ drastically.
+Interestingly, if we look at {apatb-table2} again, the mean scores of the items seem to differ drastically.
 Some items have high mean scores, ranging from 6 to 7, but some of those are comparatively low.
@@
 This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
-We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items do not drastically vary and have `1` as its minimum value.
+We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items does not drastically vary and has `1` as its minimum value.
 
@@
 Next, we show the readers the ways of testing unidimensionality.
-To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggests three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
-In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this is by calling this command:
+To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggest three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
+In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this by calling this command:
 
@@
 The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data [@harmanFactorAnalysisMinimizing1966].
-Alternatively, readers can also run a parallel analysis with a polychoric correlation matrix by calling this following command:
+Alternatively, readers can also run a parallel analysis with a polychoric correlation matrix by calling the following command:
 
@@
 
-A parallel analysis compares the eigenvalues from the data with those yielded from a randomly generated dataset with the same sample size in order to determine the number of factors one should retain in EFA [@guoAssessingDimensionalityIRT2023].
+A parallel analysis compares the eigenvalues from the data with those yielded from a randomly generated dataset with the same sample size to determine the number of factors one should retain in EFA [@guoAssessingDimensionalityIRT2023].
 The codes indicate that we tell R to run a parallel analysis on the data frame `rwa`, with one factor.
-The option `fa="fa"` implies that we want to show the eigenvalues for a EFA, while `cor = "poly"` means that we use a polychoric correlation matrix as an input.
+The option `fa="fa"` implies that we want to show the eigenvalues for an EFA, while `cor = "poly"` means that we use a polychoric correlation matrix as an input.
 
-The call to both commands above produces this following error: `Error in polychoric(x): You have more than8 categories for your items, polychoric is probably not needed`.
-Since we have more than eight response categories, we should instead run an EFA with a Pearson's correlation matrix as an input.
-Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run a EFA by calling these following commands:
+The call to both commands above produces the following error: `Error in polychoric(x): You have more than8 categories for your items, polychoric is probably not needed`.
+Since we have more than eight response categories, we should instead run an EFA with Pearson's correlation matrix as an input.
+Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run an EFA by calling these following commands:
 
@@
 After calling the commands, readers can find `Proportion Var` in the output, which reflects the amount of variance explained by a latent factor.
-The variance proportion of our EFA model is 0.56, which means that 56% of total variance is explained by a latent factor.
-Since the latent factor can account for more than 50% of variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
-To better visualize the Eigenvalues of the EFA, we can draw a scree plot using these following commands:
+The variance proportion of our EFA model is 0.56, which means that 56% of the total variance is explained by a latent factor.
+Since the latent factor can account for more than 50% of the variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
+To better visualize the Eigenvalues of the EFA, we can draw a scree plot using the following commands:
 
@@
 
-To scrutinize unidimensionality assumption, we can also run a parallel analysis by running this following command:
+To scrutinize the unidimensionality assumption, we can also run a parallel analysis by running the following command:
 
@@
 However, according to {apafg-fig3}, we can see clearly that the Eigenvalues from our actual data fall steeply after the first factor.
-To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running this following command:
+To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running the following command:
 
@@
 
-The output shows that the Eigenvalues for the first factor is much larger than the its adjacent factor (`12.225/0.843`), further supporting for the evidence for unidimensionality.
+The output shows that the Eigenvalue for the first factor is much larger than the the adjacent factor (`12.225/0.843`), further supporting the evidence for unidimensionality.
 
@@
 
-This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are column 1 to 22 of the data frame that we are going to use in the analysis.
-Then, we can continue to model fitting by typing this following command:
+This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are columns 1 to 22 of the data frame that we are going to use in the analysis.
+Then, we can continue to model fitting by typing the following command:
 
@@
 In the E step, the algorithm estimates the expected value of the $\theta$, and in the M step, it improves model parameters to maximize the likelihood of the observed data given the expected value of $\theta$.
-The process continues until model parameters are converged in stable values that fit to the data.
+The process continues until model parameters are converged in stable values that fit the data.
 If the error message (a) appears, it means that the package cannot estimate a stable solution for model parameters after 500 iterations.
@@
 
-The solution to error message (b) is less straightforward than (a) because it indicates that the model cannot be identified at all, which can have several causes.
+The solution to the error message (b) is less straightforward than (a) because it indicates that the model cannot be identified at all, which can have several causes.
 It could be due to an error in specifying assumptions about the number of latent traits or item properties, or it could be due to insufficient sample size.
@@
 
-The error message (c) and (d) are easier to solve because both indicate the error are related to the data structure.
+The error message (c) and (d) are easier to solve because both are related to the data structure.
 The former means that certain items have no variance, consisting only one response category.
@@
 The output from this procedure is presented in {apatb-table4}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
-To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorize item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
-As we seen in {apatb-table4}, item discrimination parameters of the RWA scale are ranging from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
-All threshold parameters  show a consistent increase, implying that those with higher RWA levels tend towards higher response categories.
-However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
-This might suggest that the RWA scale is less sensitive to measure individuals with a low or very low RWA level.
+To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorizes item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
+As we see in {apatb-table4}, item discrimination parameters of the RWA scale range from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
+All threshold parameters  show a consistent increase, implying that those with higher RWA levels tend towards a higher response categories.
+However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with the RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
+This might suggest that the RWA scale is less sensitive to individuals with a low or very low RWA level.
 
-The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which both are also provided in {apatb-table4}.
+The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which are also provided in {apatb-table4}.
 Before estimating a graded response model, *mirt* ran an EFA, and now as we can see in the console, we are looking at the EFA results.
-The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
+The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi-polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
 However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.
@@
 m2_stat <- m2_results$M2
-m2_stat = round(m2_stat, digits = 3)
 df <- m2_results$df
-p_value <- m2_results$p.value
 rmsea <- m2_results$RMSEA
@@
 Here, we set the `type` option to `"C2"` because it is suitable for computing *M*~2~ statistics in polytomous models.
-The interpretation of GOF statistics are similar to a general guide of interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003].
+The interpretation of GOF statistics is similar to a general guide for interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003].
 
-According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* = `r p_value`, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), and this may be caused by local dependency between the items.
+According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* < .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), and this may be caused by local dependency between the items.
 We will explore this issue further in the next part.
 
-Next, we calculate item-level fit statistics, i.e., the scaled $\chi$^2^ statistics, by running this following function:
+Next, we calculate item-level fit statistics, i.e., the scaled $\chi$^2^ statistics, by running the following function:
 
@@
 
-To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of model residuals.
+To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of residuals.
 First, we demonstrate how to run Local Dependency (LD) $\chi$^2^ statistics [@chenLocalDependenceIndexes1997], which looks at the covariance between item pairs after accounting for $\theta$.
@@
 We are only interested in large correlations between a pair of items because they indicate that responses to one item depend on responses to another item beyond what is explained by $\theta$.
-It is important to note that there is no consensus on a rule of thumb for the cutoff value of residual correlations because LD statistics are contingent to the parameters of a specific dataset [@christensenCriticalValuesYen2017].
-For the purpose of this tutorial, we set |0.2| as an paired correlation value that we want to look closely.
+It is important to note that there is no consensus on a rule of thumb for the cutoff value of residual correlations because LD statistics are contingent on the parameters of a specific dataset [@christensenCriticalValuesYen2017].
+For the purpose of this tutorial, we set |0.2| as a paired correlation value that we want to look closely at.
 To do so, we create a vector to define the value of residual correlations that we are interested in:
@@
 
-We can then use the new vector `lar` to ask R to tell us the item pairs with residuals correlations above |0.2| by running this function:
+We can then use the new vector `lar` to ask R to tell us the item pairs with residual correlations above |0.2| by running this function:
 
@@
 
-To evaluate the performance of each item in measuring RWA trait, we can visualize the amount of information explained by each item with this simple line of code:
+To evaluate the performance of each item in measuring the RWA trait, we can visualize the amount of information explained by each item with this simple line of code:
 
@@
 Peaks that are higher and narrower indicate items that are very informative for specific levels of $\theta$.
-In our case, most items provide the highest amount of information near the center to the right side of the $\theta$ distribution, indicating they are most useful for individuals with an average to high level of RWA.
+In our case, most items provide the highest amount of information near the center to the right side of the $\theta$ distribution, indicating they are most useful for individuals with average to high levels of RWA.
 
-It is also possible to evaluate the overall performance of the RWA scale by plotting a TIF, which can be done by running this following code:
+It is also possible to evaluate the overall performance of the RWA scale by plotting a TIF, which can be done by running the following code:
 
@@
 The heart of an IRT analysis is to estimate the precision of the measure, which can vary given different levels of $\theta$.
-*mirt* provides two strategies to compute reliability that differs in their assumption regarding the distribution of $\theta$.
+*mirt* provides two strategies to compute reliability that differ in their assumption regarding the distribution of $\theta$.
 First, readers may calculate marginal reliability by running this simple command:
@@
 
-The output of the above code is `r m_rel`, which indicates that the RWA scale as a whole is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
+The output of the above code is `r m_rel`, which indicates that the overall RWA scale is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
 Since reliability can vary across different levels of $\theta$, readers can also visualize the scale's reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
@@
 Second, *mirt* can also calculate the RWA scale overall reliability using $\theta$ predicted by the model.
-To compute empirical reliability, one needs to calculate estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
+To compute empirical reliability, one needs to calculate the estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
 To do this, readers can run these two lines of codes:
@@
 Note that our model has a poor fit, perhaps due to local dependence, as we showed in steps 4 and 5.
-In practice, we recommend that readers address model fitting issues before interpreting reliability or drawing substantive conclusions based on these estimates.
+In practice, we recommend that readers address model-fitting issues first before interpreting reliability or drawing substantive conclusions based on these estimates.
 
-To paint a more comprehensive picture, we can compare IRT-based reliability calculations with unweighted sum-score based reliability, such as Cronbach's $\alpha$ and McDonald's $\omega$.
+To paint a more comprehensive picture, we can compare IRT-based reliability calculations with unweighted sum-score-based reliability, such as Cronbach's $\alpha$ and McDonald's $\omega$.
 To do this, we can use `omega()` function provided by *psych* package [@revellePsychProceduresPsychological2023], which can be done by running this command:
@@
 
-The output of `omega()` function includes many information but we only need to focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
+The output of `omega()` function includes several information but for the purpose of this tutorial, we only need to focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
 Both Cronbach's $\alpha$ ($\alpha$ = `r alpha`) and McDonald's $\omega$ ($\omega$~h~ = `r oh`) shows that the RWA scale is overall internally consistent.
 
-# Conclusions
+# Discussion
 
-Since construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], applied researchers can contribute to the cumulative science by reporting evidence for measurement validity [@floraPurposePracticeExploratory2017], and this can be done by implementing and reporting a GRM analysis.
+Construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], so reporting evidence of validity should always be an important part of the routine.
+In practice, however, researchers are less interested in examining the performance of the measures they use in their study, making it difficult to assess the integrity of their research findings [@flakeConstructValidationSocial2017; @husseyHiddenInvalidity152020].
+In this tutorial, we demonstrate the applicability of GRM analysis as part of the IRT family to help applied psychology researchers assess their measurement quality.
+We provide a non-technical guide to implementing a GRM analysis through a simple 7-step process using a real, openly available dataset.
+To maximize the effectiveness of this tutorial, we show how to perform a GRM analysis using R [@rcoreteamLanguageEnvironmentStatistical2023], an open source statistical software, and make all materials publicly available.
+We also supplement our tutorial with some tips for troubleshooting common problems when running the GRM analysis.
+
+We begin the tutorial with a theoretical overview of IRT, which underlies GRM, so that readers can relate the practical steps to the theory behind the analysis.
+Since IRT is less popular than CTT, we also briefly explain how IRT differs from CTT in its assumptions.
+However, we want to emphasize that our goal here is not to argue for the superiority of CTT over IRT, since the choice of analytic tool depends largely on the specific research question at hand.
+It is important to highlight that researchers should be aware of the merits and limitations of their chosen methods.
+Therefore, we argue that researchers should always justify why they choose a particular method over many available alternatives.
+
+We agree with the call for psychological researchers to shift their focus from improving their methodological practices to advancing the process of theory building [@eronenTheoryCrisisPsychology2021; @grahekAnatomyPsychologicalTheory2021; @proulxStatisticalRitualTheory2021].
+Therefore, theory building should precede the creation of a psychological measure.
+It is important to note, however, that construct validation is a critical step in the iterative process of theorizing a psychological phenomenon [@grahekAnatomyPsychologicalTheory2021].
+Therefore, we encourage applied psychology researchers to report evidence of measurement quality to ensure the validity of their findings and contribute to cumulative psychological science [@floraPurposePracticeExploratory2017].
+One way to do this is to conduct and report a GRM analysis of their measures.
+We hope that this tutorial can be seen as a small step towards the larger goal of building robust psychological science.
+
+# Conclusion
+
+Applied psychology researchers strive to advance psychological science by producing robust and replicable findings.
+To do so, they should begin by carefully defining the construct, developing an appropriate research design, and, most importantly, creating a measure that accurately captures the phenomenon of interest.
+In this tutorial, we provide a non-technical guide that we hope will help applied psychology researchers critically evaluate and improve the quality of their measurement tools.
+By using a real, openly available dataset, we provide a realistic scenario for evaluating the performance of a psychological scale.
+By making the materials publicly available, this tutorial paper facilitates applied psychology researchers to easily implement the GRM in their own research project.
 

### 2024-01-18 codes.R

@@ -289,7 +289,7 @@ empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical re
 # Reliability seems to be pretty good.
 
 # Now we need to calculate marginal reliability.
-m_rel <- marginal_rxx(fit) # Calculating marginal reliability.
+marginal_rxx(fit) # Calculating marginal reliability.
 # Marginal reliability is almost similar to empirical reliability.
 
 # ...and then plot the marginal reliability across the latent trait spectrum.
@@ -301,6 +301,8 @@ conRelPlot(fit, title="Reliability of the RWA Scale Given to the θ Level")
 
 omega(rwa) # This script computes several reliability coefficients
 # As we see here, the RWA scale is internally consistent.
+
+om <- omega(rwa)
 
 # Session Info ------
 sessionInfo()

### 2024-01-22 manuscript.qmd
creating blind annotated R script and revising manuscript

--- 2024-01-18 draft_paper.qmd
@@
 title: "Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R"
-shorttitle: "A Graded Response Model Tutorial"
+shorttitle: "The Graded Response Model Tutorial"
 author:
@@
         region: Jawa Timur, Indonesia
-abstract: "This tutorial paper introduces the Graded Response Model (GRM), a tool for testing measurement precision under the Item Response Theory (IRT) paradigm.
+abstract: "This tutorial introduces the Graded Response Model (GRM), a tool for testing measurement precision within the Item Response Theory (IRT) paradigm.
 Addressing common problems of measurement imprecision and lack of construct validity, the tutorial guides researchers through a unidimensional GRM analysis in the R environment, using psych, mirt, and ggmirt packages.
 GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous (Likert-style) items.
-The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, model fitting, interpretation of results, and dealing with some common issues that may typically arise in the process."
+The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, testing model assumptions, model fitting, and interpretation of results."
 keywords:
@@
 
-The foundation of scientific research is the measurement process, which involves defining the construct to be measured, determining measurement assumptions, and evaluating measurement validity and precision.
-To illustrate this process, consider a researcher studying the role of authoritarian personality in explaining prejudice must first clearly define these variables, and then, develop a measurement strategy to operationalize the variables.
-This is challenging for applied psychology researchers, as most psychological constructs are not directly observable.
-To ensure a precise measurement, researchers rely on statistical techniques, assuming that these non-observable traits are "out there," or later we name this concept a *latent trait* or a *manifest variable*.
-Researchers then create tools, like scales, stimuli, tasks, observation checklists, etc., which are assumed to represent these latent traits.
-
-In psychological research, where variables are often not directly observable, construct validity, which refers to a question on whether a scale measures what it is intended to measure [@cronbachConstructValidityPsychological1955], becomes crucial.
-Construct validity can be scrutinized by linking test scores to other related constructs and observations [@cronbachConstructValidityPsychological1955].
-Test validity relies on whether the construct behaves as theory predicts within a "nomological network" [@cronbachConstructValidityPsychological1955].
-In practice, researchers establish validity by correlating the test score with external criterion i.e., other theoretically related traits or behavior [@zumboSettingStageValidity2014].
-
-Validity theory has evolved and has been expanded from time to time and validity is now seen not as a property of a specific test, but rather lies in the consequential aspects of the test use [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016; @messickValidityPsychologicalAssessment1995].
-In this sense, a test is deemed valid when researchers can demonstrate evidence for formulating a logical argument [@kaneValidatingInterpretationsUses2013; @kaneValidityEvaluationClaims2016], such as causal inference [@rutkowskiCausalInferencesLarge2016], used to defend test interpretations and its practical use [@messickValidityPsychologicalAssessment1995].
-This makes construct validity an ongoing process where researchers are advised to continuously gather and report evidence for validity of the measures they use in their research [@flakeConstructValidationSocial2017; @messickValidityPsychologicalAssessment1995; @zumboSettingStageValidity2014].
-
-Yet in practice, researchers tend to overlook to the quality of their measures.
-A study reviewing articles published in a social and personality psychology journal found that only a little more than half (53%) of sample articles cited validity evidence from previous validation studies.
-Nineteen percent of those articles, nonetheless, had adapted or modified the measures in many different ways so that the evidence for validity may not extend to these modified versions [@flakeConstructValidationSocial2017].
-Additionally, a larger study examining fifteen commonly used measures in social and personality psychology (e.g., Big Five Inventory, belief in just world scale, need for cognitive closure scale, etc.) even paints a grimmer picture [@husseyHiddenInvalidity152020].
-While the majority of the tested scales (88%) purportedly had good validity, a more exhaustive examination through internal consistency, test-retest reliability, factor structure, and invariance tests revealed that only 4% of these scales possess good measurement validity [@husseyHiddenInvalidity152020].
-Furthermore, applied psychological researchers seem to overlook the assumptions underlying their chosen method for evaluating reliability.
-For example, while Cronbach's $\alpha$ is always almost reported [@flakeStrengtheningFoundationEducational2021] as the most popular reliability coefficient [@mcneishThanksCoefficientAlpha2018], it is unclear whether researchers are aware of its underlying assumptions (that true scores and item variances should be equal and that item residuals should be uncorrelated, i.e., $\tau$ equivalence), which limits its usefulness [@sijtsmaUseMisuseVery2008].
-
-In this sense, measurements oversights can raise legitimate concerns about the replicability of research findings because measurement directly contributes to the (in)validity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
-To better identify how these oversights manifest themselves in the research process, we should pay more attention to decisions that researchers make that potentially compromise the validity of the measures used in their studies, a phenomenon known as "*questionable measurement practices*" [@flakeMeasurementSchmeasurementQuestionable2020].
-Furthermore, the lack of evidence for measurement validity contributes to the difficulty of reaching a consensus on the best way to measure a construct.
-In the long run, this is a major obstacle to the establishment of cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
-Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to help them assess measurement validity so that they can improve their measurement practices, and thus, the credibility of their findings.
+Only half of published findings include evidence of measurement validity [@flakeConstructValidationSocial2017] and a large proportion of published studies suffer from hidden invalidity [@husseyHiddenInvalidity152020].
+Lack of evidence for measurement validity can raise serious concerns about the replicability of research findings, as it directly contributes to the invalidity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
+Furthermore, the lack of evidence for measurement validity can hamper consensus on the best way to measure a construct, which becomes a major obstacle to the establishment of cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
+Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to help them assess measurement validity so that they can ensure the credibility of their findings.
 
 The purpose of this article is to provide a brief introduction to the Graded Response Model (GRM), a family of item response models specifically designed to assess the measurement precision of a polytomous (Likert-style) scale.
-We begin this paper by briefly explaining the basics of Item Response Theory (IRT), the theoretical foundation of GRM, and contrasting its differences with the widely known Classical True Score Theory (CTT).
+We begin this paper by briefly explaining the basics of Item Response Theory (IRT) and contrasting its differences with the widely known Classical True Score Theory (CTT).
 In this paper, we aim to keep our tutorial concise, so we do not cover all IRT concepts in detail.
@@
 
-Further, we briefly explain what GRM is and how a GRM model is specified.
-In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations (i.e., plots) derived from a GRM analysis.
+Further, we briefly explain what GRM is and how it is specified.
+In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations derived from a GRM analysis.
 We also introduce three key assumptions underlying a GRM and how to test these assumptions.
-We then provide an illustrative example of testing measurement precision using GRM, and in this part, we show how to practically implement GRM analysis and interpret its results.
+We then provide an illustrative example of testing measurement precision using a GRM analysis, and in this part, we show how to practically implement a GRM analysis and interpret its results.
 We complement the illustrative example with code in the open-source programming language R [@rcoreteamLanguageEnvironmentStatistical2023] so that the readers can implement and reproduce the example presented in this paper.
 Readers with some experience in R and RStudio can easily follow this tutorial, but for those who are not yet familiar with R, we refer them to excellent, easy-to-follow materials developed by @navarroPsychologicalScience2018.
-At last, we present some concluding remarks to encourage researchers to implement a GRM analysis as a part of their routine.
+Finally, we present some concluding remarks to encourage researchers to implement a GRM analysis as a part of their routine.
 
@@
 
-To scrutinize their measurement quality, psychological researchers have relied upon two foundational principles underlying psychological testing, i.e., CTT and IRT, to decompose observed score into its *deterministic* and *random* or stochastic elements [@zumboValidityFoundationalIssues2006].
-On the one hand, CTT decomposes observed scores into *true* score and its *error* components.
-In practice, researchers implement this principle by conducting Structural Equation Modeling (SEM), Exploratory Factor Analysis (EFA), or Confirmatory Factor Analysis (CFA).
-Specifying the measurement part of SEM, or employing EFA and CFA models, allows for the decomposition of the covariance matrix of a given data into latent factors, which represent true score or trait level, and error terms (i.e., residuals or unique variances).
+To scrutinize their measurement quality, psychological researchers have relied on two basic principles underlying psychological testing, i.e., CTT and IRT, to decompose observed scores into their *deterministic* and *random* or stochastic components [@zumboValidityFoundationalIssues2006].
+CTT, on the one hand, decomposes observed outcomes into *true* scores and *error* components.
+In practice, researchers implement this principle by performing structural equation modeling (SEM), exploratory factor analysis (EFA), or confirmatory factor analysis (CFA).
+Specifying the measurement part of a SEM model, or estimating EFA and CFA models, allows the covariance matrix of a given set of data to be decomposed into latent factors, which represent the true score or trait level, and error terms (i.e., residuals or unique variances).
 Consequently, the relationship between observed score and true score is *linear*, since true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
 IRT, on the other hand, models this relationship in a *probabilistic* rather than a linear fashion.
-More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account the properties of the items, such as item discrimination, difficulty, and, when appropriate, guessing [@bakerBasicsItemResponse2017].
+More specifically, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account item properties such as item discrimination, difficulty, and, when appropriate, guessing [@bakerBasicsItemResponse2017].
 
@@
 In CTT, standard deviation of the observed score (*s*) is used to calculate standard error of measurement.
-Since measurement error relies on *s*, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample regardless of their trait level.
-This shortcoming limits the utility of CTT, especially since psychologists often need to interpret individual scores, not just evaluate the test as a whole.
-Additionally, since standard error of measurement is also a function of reliability, which is typically denoted as a correlation between two parallel tests, reliability is assumed to be the same across different levels of a trait or ability.
-This is unrealistic since researchers often encounter situations where a test is overly difficult for a group of low-performing participants, providing little information beyond an indication that their trait or ability level is significantly lower than what the test can measure.
+Therefore, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample regardless of their trait level.
+This shortcoming limits the utility of CTT, especially since psychologists often need to interpret individual scores, rather than just evaluate the test as a whole.
+Additionally, since standard error of measurement is also a function of reliability, reliability is assumed to be the same across different levels of a trait or ability.
+This assumption is unrealistic since researchers often encounter situations where a test is overly difficult for a group of low-performing participants, providing little information beyond an indication that their trait or ability level is significantly lower than what the test can measure.
 
-IRT offers an elegant solution to this issue by enabling the calculation of standard errors for each individual (*SE*~$\theta$~), and test reliability can be inferred from the average of *SE*~$\theta$~ across a sample of participants [@embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
+IRT offers an elegant solution to this issue by allowing the calculation of standard errors for each individual (*SE*$\theta$), and thus, test reliability can be inferred from the average of *SE*$\theta$ across a sample of participants [@embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
 This approach allows for the estimation of reliability at varying levels of trait or ability (i.e., test information function - TIF).
@@
 A concrete example of this is a study that examined the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
-According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring individuals with low levels of sadism [@blotnerDarkTriadDead2022].
-Therefore, IRT models offer a more informative and nuanced perspective that proves useful for researchers who wish to closely examine the performance of their measures.
+According to this study, the sadism sub-scale of the SD4 is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring individuals with lower levels of sadism [@blotnerDarkTriadDead2022].
+In this sense, IRT models offer a more informative and nuanced perspective that proves useful for researchers who wish to closely examine the performance of their measures.
 
-Further, IRT allows researchers to examine the performance of a specific item (hence "item" response theory) by specifying the relationship between item score and $\theta$ given one-, two-, or three-parameter.
-The one-parameter logistic (1PL) or Rasch model, the simplest variant of the IRT models, accounts only item difficulty (*b*) while assuming equal item discrimination (*a*) across items.
+Further, IRT allows researchers to examine the performance of a specific item by specifying the relationship between item score and $\theta$ given one-, two-, or three-parameter.
+The one-parameter logistic (1PL) or a Rasch model, the simplest variant of the IRT models, accounts for only item difficulty (*b*) while assuming equal item discrimination (*a*) across items.
 In practice, this model overlaps slightly with CTT in the sense that they assume that all items have equal informative value, so that the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
 This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measures remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
-Put simply, Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
-For example, the difference in depression levels between two individuals should always be the same regardless of the scale used to measure their depression levels.
-While this principle reasonably enforces objectivity in measurement practices, it requires a strong theory delineating the construct and strict requirements of data-model fit while both of these assumptions rarely hold in a real-world scenario, especially in psychological science.
+Put simply, a Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
+More concretely, the difference in depression levels between two individuals should always be the same regardless of the scale used to measure their depression levels.
+While this principle reasonably enforces objectivity in measurement practices, it requires a strong theory underlying the construct and strict requirements of data-model fit, and both of these assumptions rarely hold in a real-world scenario, especially in psychological science.
 
 Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing for differences in item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*).
-Additionally, in some contexts, researchers may suspect that some parts of the probabilistic relationship between observed score and $\theta$ is explained by guessing, thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
+In addition, in some contexts, researchers may suspect that some parts of the probabilistic relationship between observed score and $\theta$ is explained by guessing, thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
 The field of IRT has rapidly evolved to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
@@
 We briefly summarize the features of the most commonly used IRT models in {apatb-table1}.
+
+{{< pagebreak >}}
+
+```{r}
+#| label: apatb-table1
+#| apa-cap: Comparison Between The Commonly Used IRT Models
+#| apa-note: NULL
+#| echo: false
+```
+
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| Model                                   | Key Characteristics                                                                                                                                         | Data Type   | Response Options        |
++=========================================+=============================================================================================================================================================+=============+=========================+
+| 1-PL Model (Rasch Model)                | 1\.
+Estimates only item difficulties (*b*).
+| Dichotomous | Correct/Incorrect (0/1) |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Assumes that all items have equal discrimination parameters (*a*).
+|             |                         |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 3\.
+Item and person parameters are independent.
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| 2-PL Model                              | 1\.
+Estimates item difficulties (*b*) and item discrimination (*a*).
+| Dichotomous | Correct/Incorrect (0/1) |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| 3-PL Model                              | 1\.
+Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*).
+| Dichotomous | Correct/Incorrect (0/1) |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses.
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| Graded Response Model (GRM)             | 1\.
+Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style).
+| Polytomous  | Ordered Categories      |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| Partial Credit Model (PCM)              | 1\.
+An extension of the 1-PL (Rasch) model for polytomous items.
+| Polytomous  | Ordered Categories      |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Estimates thresholds between adjacent categories but assumes equal discrimination across items.
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| Generalized Partial Credit Model (GPCM) | Extending PCM to allow differential discrimination parameters across items.
+| Polytomous  | Ordered Categories      |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+| Nominal Response Model (NRM)            | 1\.
+Appropriate for modeling categorical responses with no order.
+| Categorical | Unordered Categories    |
+|                                         |                                                                                                                                                             |             |                         |
+|                                         | 2\.
+Estimates discrimination parameters (*a*) and multiple category-specific parameters (*b*).
+|             |                         |
++-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
+
+{{< pagebreak >}}
 
@@
 The fundamental idea of GRM is to extend the logic of simpler dichotomous IRT models to polytomous scales by applying a probabilistic function to each response category.
-In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\theta$, item difficulty, and item discrimination.
-GRM extends this idea by modeling the probability of picking a certain response category or higher on an item (i.e., *step function*) given to item difficulty and discrimination.
+In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\theta$, item difficulty (*b*), and item discrimination (*a*).
+GRM extends this idea by modeling the probability of selecting certain response category or higher on an item (i.e., *step function*) given to item difficulty (*b*) and discrimination (*a*).
 For each response category (e.g., answering "agree" on a five-point Likert scale), GRM calculates the cumulative probability of a participant answering "agree" or above, given to their $\theta$.
-Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold) to handle ordered polytomous data.
+Therefore, the notion of item difficulty in dichotomous IRT models is extended to the step function (i.e., item threshold - *b*) to handle ordered polytomous data.
 
@@
 
-Let's take a closer look at {apafg-fig1}, which shows an example of an item probability function (IPF) from an item on a scale with five response categories.
+{apafg-fig1} shows an example of an item probability function (IPF) from an item on a scale with five response categories.
 In general, IPF describes a relationship between $\theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\theta$).
@@
 
+{{< pagebreak >}}
+
+```{r}
+#| label: apafg-fig1
+#| apa-cap: An Item Probability Function from a GRM Model
+#| apa-note: NULL
+#| output: true
+#| echo: false
+
+knitr::include_graphics("CPF example.png")
+```
+
+{{< pagebreak >}}
+
 ## Assumptions
 
-Before running an analysis, researchers need to be aware of the assumption underlying a GRM model.
-The first key assumption is that $\theta$ is monotonically correlated with the probability of endorsing a response category.
-In other words, individuals with higher levels of $\theta$ have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
+The first key assumption of a GRM is that $\theta$ is monotonically correlated with the probability of endorsing a response category.
+More sharply, individuals with higher levels of $\theta$ should have a higher probability of endorsing response category that represents greater intensity of the traits [@hambletonIRTModelsAnalysis2010].
 For instance, people with a higher tendency of sadistic personality have a greater chance of answering "*moderately agree*" or "*strongly agree*" on a sadism scale compared to those with lower levels of sadism.
@@
 It is important to note that evidence for unidimensionality does not always warrant local independence.
-As an eyeball example - consider trust in science scale containing these two items: "*I trust scientists working in natural science*" and "*Most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in natural science are very likely to also trust biologists.
-To inspect whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\theta$ using residual correlation analysis [@chenLocalDependenceIndexes1997].
+As an eyeball example - consider a scale measuring trust in science, which contains: "*I trust scientists working in natural science*" and "*Most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in natural science are very likely to also trust biologists.
+To test whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\theta$ by performing residual correlation analysis [@chenLocalDependenceIndexes1997].
 
@@
 
-In this paper, we use the latest version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items that participants are asked to respond with their agreement to those items on a nine-point scale, ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
-While the RWA scale consists of three sub-dimensions, i.e., submissiveness, aggression, and conventionalism, the RWA scale is (theoretically) unidimensional because [@altemeyerAuthoritarians2006] shows that the sub-dimensions are strongly intercorrelated.
-While some evidence shows otherwise [@duckittMultidimensionalityRightWingAuthoritarian2013], for the purpose of this article, we assume that the RWA scale is unidimensional.
+In this paper, we use the most recent version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items in which participants are asked to indicate their agreement with the items on a nine-point scale ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
+While the RWA scale consists of three sub-dimensions, i.e., Submissiveness, Aggression, and Conventionalism, the RWA scale is theoretically assumed to be unidimensional because [@altemeyerAuthoritarians2006] shows that these sub-dimensions are strongly intercorrelated.
+While there is some evidence to the contrary [@duckittMultidimensionalityRightWingAuthoritarian2013], for the purposes of this article we will assume that the RWA scale is unidimensional.
 
@@
 To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
-We also include the annotated R script file (.R) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
-The Quarto file (and its corresponding .docx and .pdf output) and R script file are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
-The dataset we used in this tutorial paper was obtained from [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/), which is publicly accessible.
+We also include a longer, annotated R script file (.R) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
+The Quarto file (and its corresponding .docx and .pdf output) and R script file are publicly available on [a Github repository]().
+The dataset we used in this tutorial paper was obtained from a publicly accessible [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/).
 
@@
 As we see in {apatb-table2}, all variables have a minimum value of `0`, while the minimum score should be `1`.
-Again, there is no information provided in the codebook regarding what `0` actually represents.
-Therefore, before deciding what we should do next, it is better to find out how many `0` we have in the data frame.
-To this end, we can calculate the percentage of `0` in each item by running these commands:
-
-```{r}
-zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
-print(zero) # Showing the percentage of "0" for each item.
-```
-
-After executing these commands, readers can view the percentage of `0` in each items in their R console, which overall are very small, ranging from 0.09% to 0.32% of the total cases.
-Since the percentages are very small, `0` is likely a code for a missing value.
-It is important to note that *mirt* package uses the Expected-Maximization (EM) algorithm to estimate model parameters, and the EM algorithm can handle missing values [@chalmersMirtMultidimensionalItem2012].
-If we decide to eliminate cases with missing values, we still have a sizable number of cases, nonetheless.
-Therefore, to simplify our analysis, we only keep cases with complete responses by executing these commands:
-
-```{r}
-rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Recoding "0" with "NA" in all columns.
-  drop_na()  # Removing cases with any "NA" values.
-```
-
-If readers prefer to keep cases with missing values, especially when the sample size is low, readers can exclude `drop_na()` command.
-
-Interestingly, if we look at {apatb-table2} again, the mean scores of the items seem to differ drastically.
-Some items have high mean scores, ranging from 6 to 7, but some of those are comparatively low.
-The RWA scale indeed has some unfavorable items but, again, there is no information in the codebook whether these unfavorable items have been reversely coded.
-However, if we look closely at ten items with high mean ($\bar{x}$ > 6), these are the items that are supposed to be unfavorable.
-Therefore, we can reasonably assume that unfavorable items have not been reversed in the original dataset, and we should do so by running these commands:
-
-```{r}
-unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
-rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 to reverse code the unfavorable items.
-```
-
-First, we define a vector namely `unfav` to identify which items should be reversed, and then we use `mutate()` function to reverse the score.
-This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
-We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items does not drastically vary and has `1` as its minimum value.
-
-## Step 3: Examining Dimensionality
-
-Next, we show the readers the ways of testing unidimensionality.
-To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggest three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
-In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this by calling this command:
-
-```{r}
-#| eval: false
-
-irt.fa(rwa, nfactors = 1, fm = "minres")
-```
-
-`irt.fa` function is to run an EFA with a polychoric correlation matrix as an input, not a Pearson's correlation matrix, because our data is ordinal.
-The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data [@harmanFactorAnalysisMinimizing1966].
-Alternatively, readers can also run a parallel analysis with a polychoric correlation matrix by calling the following command:
-
-```{r}
-#| eval: false
-
-fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa", cor = "poly")
-```
-
-A parallel analysis compares the eigenvalues from the data with those yielded from a randomly generated dataset with the same sample size to determine the number of factors one should retain in EFA [@guoAssessingDimensionalityIRT2023].
-The codes indicate that we tell R to run a parallel analysis on the data frame `rwa`, with one factor.
-The option `fa="fa"` implies that we want to show the eigenvalues for an EFA, while `cor = "poly"` means that we use a polychoric correlation matrix as an input.
-
-The call to both commands above produces the following error: `Error in polychoric(x): You have more than8 categories for your items, polychoric is probably not needed`.
-Since we have more than eight response categories, we should instead run an EFA with Pearson's correlation matrix as an input.
-Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run an EFA by calling these following commands:
-
-```{r}
-cor <- cor(rwa, method = "pearson") # First, creating a Pearson's correlation matrix.
-efa <- fa(rwa, nfactors = 1, fm = "minres") # Now, running EFA.
-print(efa) # Print the results.
-```
-
-After calling the commands, readers can find `Proportion Var` in the output, which reflects the amount of variance explained by a latent factor.
-The variance proportion of our EFA model is 0.56, which means that 56% of the total variance is explained by a latent factor.
-Since the latent factor can account for more than 50% of the variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
-To better visualize the Eigenvalues of the EFA, we can draw a scree plot using the following commands:
-
-```{r}
-#| eval: false
-
-plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
-abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
-```
-
-The first line of code is a function to plot the Eigenvalues (`efa$values`, x-axis) given the number of latent factors (y-axis).
-The option `type = "b"` implies that we ask R to display the Eigenvalues exact points and a line connecting these points along the number of factors.
-The second line of code aims to display a horizontal red line (i.e., a reference line) to see which factors have eigenvalues greater than one, which is a common criterion for factor retention.
-{apafg-fig2} shows that there is a clear break or an "elbow" that displays the location where the Eigenvalues start to level off.
-This implies that factors beyond the first may not be meaningful and could be only noise.
-Therefore, the scree plot strengthens our assumption that the item pool is, indeed, unidimensional.
-
-To scrutinize the unidimensionality assumption, we can also run a parallel analysis by running the following command:
-
-```{r}
-pa <- fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa")
-```
-
-Readers should find a plot similar to {apafg-fig3} appear right after executing this code as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
-This means that the parallel analysis suggests that there are six factors underlying our item pool, not one.
-However, according to {apafg-fig3}, we can see clearly that the Eigenvalues from our actual data fall steeply after the first factor.
-To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running the following command:
-
-```{r}
-pa$fa.values
-```
-
-The output shows that the Eigenvalue for the first factor is much larger than the the adjacent factor (`12.225/0.843`), further supporting the evidence for unidimensionality.
-
-## Step 4: Model Estimation, Parameters, and Fit Statistics
-
-In this step, we start to specify a vector representing our model specification, such as:
-
-```{r}
-model <- 'rwa = 1-22'
-```
-
-This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are columns 1 to 22 of the data frame that we are going to use in the analysis.
-Then, we can continue to model fitting by typing the following command:
-
-```{r}
-fit <- mirt(data = rwa, 1, model = model, itemtype = "graded", SE = TRUE, verbose = FALSE)
-```
-
-The code above implies that we are fitting an IRT model using data from a data frame namely `rwa` (`data = rwa`).
-The number `1` indicates that we presume that the model contains only one $\theta$, i.e., unidimensional.
-We also set the model specification to `model = model`, which we have previously determined.
-We set `itemtype` to `"graded"` because we want to run a GRM model.
-The `SE` option is set to `TRUE` because we ask R to also estimate the standard error.
-At last, we set the `verbose` option to `FALSE` to avoid R displaying unnecessary information during the model fitting process, so the `mirt()` function can run quietly.
-
-Apart from this tutorial, readers might encounter four common error messages after running `mirt()` function: (a) `EM cycles terminated after 500 iterations`, (b) `Could not invert information matrix; model may not be empirically identified`, (c) `The following items have only one response category and cannot be estimated`, and (d) `Error in [<-(*tmp*, i, nms[[i]], value = items.old[[i]]) : subscript out of bounds`.
-Error messages (a) and (b) correspond to the convergence issue, while (c) and (d) are issues related to the data structure.
-
-*mirt* uses the EM algorithm as a default option.
-In short, the EM algorithm estimates model parameters in two steps: the expectation (E) and the maximization (M) steps.
-In the E step, the algorithm estimates the expected value of the $\theta$, and in the M step, it improves model parameters to maximize the likelihood of the observed data given the expected value of $\theta$.
-The process continues until model parameters are converged in stable values that fit the data.
-If the error message (a) appears, it means that the package cannot estimate a stable solution for model parameters after 500 iterations.
-As a solution, readers can simply increase the maximum number of iterations to, for instance, 1000 cycles by adding this option `technical = list(NCYCLES = 10000)` to the `mirt()` function.
-
-The solution to the error message (b) is less straightforward than (a) because it indicates that the model cannot be identified at all, which can have several causes.
-It could be due to an error in specifying assumptions about the number of latent traits or item properties, or it could be due to insufficient sample size.
-Therefore, when error message (b) appears, it is important to take a step back and think twice about the model assumptions, the fit between the model and the underlying theory, and whether the sample size is large enough to estimate the model properly.
-
-The error message (c) and (d) are easier to solve because both are related to the data structure.
-The former means that certain items have no variance, consisting only one response category.
-The solution for this issue is to exclude these items from model estimations.
-The latter indicates a mismatch between the vector of model specification and the data frame, for instance, specifying a vector with ten variables, while in fact, the data frame has only nine columns.
-To solve this issue, readers are suggested to check again whether the specified vector representing the model specification matches the structure of the data frame.
-
-Next, we can ask the package to calculate item discrimination and thresholds by calling these functions below:
-
-```{r}
-coefs <- coef(fit, IRTpars = TRUE, simplify = TRUE) # Saving model parameters (item discrimination (a) and threshold (b)) in a data frame.
-print(coefs) # Calling the data frame.
-summary(fit) # Displaying factor loadings and commonality.
-```
-
-The first line of code indicates that we are calling a `coef()` function to calculate item parameters from `fit` model, and then, store them in a new data frame called `coefs`.
-The `IRTpars` and `simplify` option is set to `TRUE` because we want to display the traditional IRT parameters (*a* and *b*) in a simple, readable format without showing the standard errors.
-
-The output from this procedure is presented in {apatb-table4}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
-To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorizes item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
-As we see in {apatb-table4}, item discrimination parameters of the RWA scale range from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
-All threshold parameters  show a consistent increase, implying that those with higher RWA levels tend towards a higher response categories.
-However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with the RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
-This might suggest that the RWA scale is less sensitive to individuals with a low or very low RWA level.
-
-The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which are also provided in {apatb-table4}.
-Before estimating a graded response model, *mirt* ran an EFA, and now as we can see in the console, we are looking at the EFA results.
-The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi-polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
-However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.
-
-Next, we can estimate the model goodness-of-fit (GOF) statistics (*M*~2~) by calling this command below:
-
-```{r}
-M2(fit, type = "C2")
-```
-```{r}
-#| include: false
-
-m2_results <- M2(fit, type="C2")
-m2_results[] <- lapply(m2_results, as.numeric)
-m2_stat <- m2_results$M2
-df <- m2_results$df
-rmsea <- m2_results$RMSEA
-rmsea = round(rmsea, digits=3)
-srmsr <- m2_results$SRMSR
-srmsr = round(srmsr, digits=3)
-tli <- m2_results$TLI
-tli = round(tli, digits=3)
-cfi <- m2_results$CFI
-cfi = round(cfi, digits=3)
-```
-
-We ask the package to calculate the scaled *M*~2~ statistics [@maydeu-olivaresLimitedInformationGoodnessoffit2006] and other GOF indices, such as Root Mean Square Error of Approximation (RMSEA), Comparative Fit Index (CFI), Tucker-Lewis Index (TLI), and Standardized Root-Mean-Square Residual (SRMSR) by running this code above.
-Here, we set the `type` option to `"C2"` because it is suitable for computing *M*~2~ statistics in polytomous models.
-The interpretation of GOF statistics is similar to a general guide for interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003].
-
-According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* < .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), and this may be caused by local dependency between the items.
-We will explore this issue further in the next part.
-
-Next, we calculate item-level fit statistics, i.e., the scaled $\chi$^2^ statistics, by running the following function:
-
-```{r}
-item.fit <- itemfit(fit) # Estimating item fit statistics and saving them in a data frame.
-print(item.fit) # Calling the data frame.
-```
-
-The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
-All items have very good (low) *RMSEA* values but normally, we want the *p* values of the scaled $\chi$^2^ to be nonsignificant, implying that there is no discrepancy between the observed response pattern with what the model predicts.
-In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
-
-## Step 5: Model Residuals
-
-To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of residuals.
-First, we demonstrate how to run Local Dependency (LD) $\chi$^2^ statistics [@chenLocalDependenceIndexes1997], which looks at the covariance between item pairs after accounting for $\theta$.
-To that end, readers can run two lines of codes as follows:
-
-```{r}
-ld <- residuals(fit, type = "LD") # Running local dependency (LD) statistics.
-up <- which(upper.tri(ld), arr.ind = TRUE) # Creating a new matrix containing values only on the upper side of the diagonal (correlations).
-```
-
-The first line of code aims to extract residuals of `fit` model and store them as a matrix, namely `ld`.
-The `type` option is set to `"LD"` because we ask the package to calculate LD statistics of the `fit` model.
-After running the first line, readers may view a matrix containing residual covariance (in the lower diagonal) and correlations (in the upper diagonal).
-Correlations are more interpretable, so we focus on the upper side of the diagonal.
-Therefore, the second line of code is to create a new matrix containing only correlation values in the upper diagonal.
-
-We are only interested in large correlations between a pair of items because they indicate that responses to one item depend on responses to another item beyond what is explained by $\theta$.
-It is important to note that there is no consensus on a rule of thumb for the cutoff value of residual correlations because LD statistics are contingent on the parameters of a specific dataset [@christensenCriticalValuesYen2017].
-For the purpose of this tutorial, we set |0.2| as a paired correlation value that we want to look closely at.
-To do so, we create a vector to define the value of residual correlations that we are interested in:
-
-```{r}
-#| eval: false
-lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # A vector defining unusually large residuals ( > |0.2|).
-```
-
-We can then use the new vector `lar` to ask R to tell us the item pairs with residual correlations above |0.2| by running this function:
-
-```{r}
-#| eval: false
-for (i in 1:nrow(lar)) {
-  row <- lar[i, 1]
-  col <- lar[i, 2]
-  value <- ld[row, col]
-  cat(sprintf("A large residual correlation is found between item %d and item %d: %f\n", row, col, value))
-} # Now we detect the problematic pairs.
-```
-
-After running the function above, readers may encounter an error message: `Error in lar[i, 1] : subscript out of bounds`.
-This message indicates that R does not detect any residual correlation above |0.2|.
-To paint a clearer picture, we may need to use another way to examine model residuals.
-In the next part, we demonstrate the use of Yen's *Q*~3~ statistics [@yenEffectsLocalItem1984], which is considered more powerful for detecting underlying local dependency [@chenLocalDependenceIndexes1997].
-To run Yen's *Q*~3~, readers can type and run this command:
-
-```{r}
-q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics.
-```
-
-This code asks R to run `residuals()` function using `"Q3"` as the `type`, and then, keep the value as a new matrix, namely `q3`.
-Again, we are only interested in item pairwise correlations above |0.2|, and to help us flag problematic pairs, we can make use of `findCorrelation()` function from *caret* package [@kuhnCaretClassificationRegression2024] as follows:
-
-```{r}
-findCorrelation(q3, cutoff = 0.2, verbose = T) # Flagging problematic item pairwise correlations.
-```
-
-After running the code, readers may see in their R console that residual correlations between item Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are above |0.2|.
-Interestingly, all of those items, except for Q4, have nonsignificant *S*-$\chi$^2^ statistics (see {apatb-table5}) as well, which tells us that we have to look at these items closely and then decide whether these items have shared characteristics beyond what is explained by the model.
-
-## Step 6: IRT Plots
-
-*mirt* offers features to visualize model parameters but the options for customizing these plots are rather limited.
-*ggmirt* package [@masurGgmirt2023] fills this gap by combining *mirt* and *ggplot2* functions.
-In this tutorial, we demonstrate the use of *ggmirt* to visualize Item Probability Function (IPF), Item Information Function (IIF), Test Information Function (TIF), and conditional probability plot.
-
-To visualize IPF, readers can type and run this function:
-
-```{r}
-tracePlot(fit, title = "Item Probability Functions of RWA Scale") + labs(color="Response Categories")
-```
-
-The `labs(color)` function is to assign different colors to each curve representing a response category.
-The output of this function is {apafg-fig4}.
-In {apafg-fig4}, we see that as $\theta$ increases, respondents are more likely to choose higher response categories.
-The gradual transition from one response option to the next across the spectrum of $\theta$ values indicates that the items are capturing incremental increases in the RWA level.
-However, all IPFs of RWA items seem to be significantly overlapping and tend to peak on a $\theta$ value close to or higher than the mean.
-This implies that RWA items are more sensitive to differentiate participants with high levels of RWA.
-
-To evaluate the performance of each item in measuring the RWA trait, we can visualize the amount of information explained by each item with this simple line of code:
-
-```{r}
-itemInfoPlot(fit, facet = TRUE, title = "Item Information Functions of the RWA Scale")
-```
-
-The `facet` option is set to `TRUE` so that R displays IIF for each item.
-The output for this function is {apafg-fig5}, where the x-axis represents the range of $\theta$, and the y-axis indicates the amount of information provided by each item.
-Peaks that are higher and narrower indicate items that are very informative for specific levels of $\theta$.
-In our case, most items provide the highest amount of information near the center to the right side of the $\theta$ distribution, indicating they are most useful for individuals with average to high levels of RWA.
-
-It is also possible to evaluate the overall performance of the RWA scale by plotting a TIF, which can be done by running the following code:
-
-```{r}
-testInfoPlot(fit, title = "Test Information Function of the RWA Scale")
-```
-
-The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring a group of individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
-However, the RWA scale is not optimal for measuring individuals with RWA levels below or beyond this range.
-
-## Step 7: Computing Reliability
-
-The heart of an IRT analysis is to estimate the precision of the measure, which can vary given different levels of $\theta$.
-*mirt* provides two strategies to compute reliability that differ in their assumption regarding the distribution of $\theta$.
-First, readers may calculate marginal reliability by running this simple command:
-
-```{r}
-marginal_rxx(fit)
-```
-```{r}
-#| include: false
-
-m_rel <- marginal_rxx(fit)
-m_rel = round(m_rel, digits=3)
-```
-
-The output of the above code is `r m_rel`, which indicates that the overall RWA scale is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
-Since reliability can vary across different levels of $\theta$, readers can also visualize the scale's reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
-
-```{r}
-conRelPlot(fit, title = "Reliability of the RWA Scale Given to the θ Level")
-```
-
-The output of this code is {apafg-fig7}, which shows that the RWA scale can measure individuals with $\theta$ levels between -2*SD* and +4*SD* with sufficient reliability, i.e., *r*~xx~ $\geq$ 0.75.
-
-Second, *mirt* can also calculate the RWA scale overall reliability using $\theta$ predicted by the model.
-To compute empirical reliability, one needs to calculate the estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
-To do this, readers can run these two lines of codes:
-
-```{r}
-theta_se <- fscores(fit, full.scores.SE = TRUE) # Extracting the estimated theta score of each participant.
-empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
-```
-```{r}
-#| include: false
-
-e_rel <- empirical_rxx(theta_se)
-e_rel = round(e_rel, digits=3)
-```
-
-The `fscores()` function is used to compute the estimated $\theta$ value for each participant predicted by the `fit` model.
-The `full.scores.SE` is set to `TRUE` because the package uses the $\theta$ value and standard error of each participant (*SE*~$\theta$~) to compute the empirical reliability.
-We store the estimated $\theta$ and its *SE*~$\theta$~ in a new data frame, namely `theta_se`, and then run `empirical_rxx()` function to calculate empirical reliability.
-The output of these codes is `r e_rel`, which is very close to marginal reliability we estimated before.
-Notably, while marginal and empirical reliability aim to quantify the overall reliability of the scale, they base the calculations on different assumptions.
-Marginal reliability assumes that $\theta$ is normally distributed, and empirical reliability uses the $\theta$ distribution predicted by the model, which still contains measurement error but is more realistic.
-Note that our model has a poor fit, perhaps due to local dependence, as we showed in steps 4 and 5.
-In practice, we recommend that readers address model-fitting issues first before interpreting reliability or drawing substantive conclusions based on these estimates.
-
-To paint a more comprehensive picture, we can compare IRT-based reliability calculations with unweighted sum-score-based reliability, such as Cronbach's $\alpha$ and McDonald's $\omega$.
-To do this, we can use `omega()` function provided by *psych* package [@revellePsychProceduresPsychological2023], which can be done by running this command:
-
-```{r}
-omega(rwa)
-```
-```{r}
-#| include: false
-
-om <- omega(rwa)
-alpha <- om$alpha
-alpha = round(alpha, digits = 3)
-oh <- om$omega_h
-oh = round(oh, digits = 3)
-```
-
-The output of `omega()` function includes several information but for the purpose of this tutorial, we only need to focus on Cronbach's $\alpha$ and McDonald's $\omega$~h~.
-Both Cronbach's $\alpha$ ($\alpha$ = `r alpha`) and McDonald's $\omega$ ($\omega$~h~ = `r oh`) shows that the RWA scale is overall internally consistent.
-
-# Discussion
-
-Construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], so reporting evidence of validity should always be an important part of the routine.
-In practice, however, researchers are less interested in examining the performance of the measures they use in their study, making it difficult to assess the integrity of their research findings [@flakeConstructValidationSocial2017; @husseyHiddenInvalidity152020].
-In this tutorial, we demonstrate the applicability of GRM analysis as part of the IRT family to help applied psychology researchers assess their measurement quality.
-We provide a non-technical guide to implementing a GRM analysis through a simple 7-step process using a real, openly available dataset.
-To maximize the effectiveness of this tutorial, we show how to perform a GRM analysis using R [@rcoreteamLanguageEnvironmentStatistical2023], an open source statistical software, and make all materials publicly available.
-We also supplement our tutorial with some tips for troubleshooting common problems when running the GRM analysis.
-
-We begin the tutorial with a theoretical overview of IRT, which underlies GRM, so that readers can relate the practical steps to the theory behind the analysis.
-Since IRT is less popular than CTT, we also briefly explain how IRT differs from CTT in its assumptions.
-However, we want to emphasize that our goal here is not to argue for the superiority of CTT over IRT, since the choice of analytic tool depends largely on the specific research question at hand.
-It is important to highlight that researchers should be aware of the merits and limitations of their chosen methods.
-Therefore, we argue that researchers should always justify why they choose a particular method over many available alternatives.
-
-We agree with the call for psychological researchers to shift their focus from improving their methodological practices to advancing the process of theory building [@eronenTheoryCrisisPsychology2021; @grahekAnatomyPsychologicalTheory2021; @proulxStatisticalRitualTheory2021].
-Therefore, theory building should precede the creation of a psychological measure.
-It is important to note, however, that construct validation is a critical step in the iterative process of theorizing a psychological phenomenon [@grahekAnatomyPsychologicalTheory2021].
-Therefore, we encourage applied psychology researchers to report evidence of measurement quality to ensure the validity of their findings and contribute to cumulative psychological science [@floraPurposePracticeExploratory2017].
-One way to do this is to conduct and report a GRM analysis of their measures.
-We hope that this tutorial can be seen as a small step towards the larger goal of building robust psychological science.
-
-# Conclusion
-
-Applied psychology researchers strive to advance psychological science by producing robust and replicable findings.
-To do so, they should begin by carefully defining the construct, developing an appropriate research design, and, most importantly, creating a measure that accurately captures the phenomenon of interest.
-In this tutorial, we provide a non-technical guide that we hope will help applied psychology researchers critically evaluate and improve the quality of their measurement tools.
-By using a real, openly available dataset, we provide a realistic scenario for evaluating the performance of a psychological scale.
-By making the materials publicly available, this tutorial paper facilitates applied psychology researchers to easily implement the GRM in their own research project.
-
-{{< pagebreak >}}
-
-# References
-
-::: {#refs}
-:::
-
-{{< pagebreak >}}
-
-```{r}
-#| label: apatb-table1
-#| apa-cap: Comparison Between Common IRT Models
-#| apa-note: NULL
-#| echo: false
-```
-
-| Model                                   | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-|----------|--------------------------------------------|----------|----------|
-| 1-PL Model (Rasch Model)                | 1\.
-Estimates only item difficulties (*b*).
-2.
-Assumes that all items have equal discrimination parameters (*a*).
-3.
-Item and person parameters are independent.
-| Dichotomous | Correct/Incorrect (0/1) |
-| 2-PL Model                              | 1\.
-Estimates item difficulties (*b*) and item discrimination (*a*).
-2.
-Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.
-| Dichotomous | Correct/Incorrect (0/1) |
-| 3-PL Model                              | 1\.
-Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*).
-2.
-Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses.
-| Dichotomous | Correct/Incorrect (0/1) |
-| Graded Response Model (GRM)             | 1\.
-Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style).
-2.
-Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.
-| Polytomous  | Ordered Categories      |
-| Partial Credit Model (PCM)              | 1\.
-An extension of the 1-PL (Rasch) model for polytomous items.
-2.
-Estimates thresholds between adjacent categories but assumes equal discrimination across items.
-| Polytomous  | Ordered Categories      |
-| Generalized Partial Credit Model (GPCM) | Extending PCM to allow differential discrimination parameters across items.
-| Polytomous  | Ordered Categories      |
-| Nominal Response Model (NRM)            | 1\.
-Appropriate for modeling categorical responses with no order.
-2.
-Estimates discrimination parameters (*a*) and multiple category-specific parameters (*b*).
-| Categorical | Unordered Categories    |
-
-{{< pagebreak >}}
-
-```{r}
-#| label: apafg-fig1
-#| apa-cap: An Item Probability Function from a GRM Model
-#| apa-note: NULL
-#| output: true
-#| echo: false
-
-knitr::include_graphics("CPF example.png")
-```
 
@@
 ```
+
+{{< pagebreak >}}
+
+Again, there is no information provided in the codebook regarding what `0` actually represents.
+Therefore, before deciding what we should do next, it is better to find out how many `0` we have in the data frame.
+To this end, we can calculate the percentage of `0` in each item by running these commands:
+
+```{r}
+zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
+print(zero) # Showing the percentage of "0" for each item.
+```
+
+After executing these commands, readers can see the percentage of `0` in each items in their R console, which overall are very small, ranging from 0.09% to 0.32% of the total cases.
+Since the percentages are very small, `0` is likely a code for a missing value.
+It is important to note that *mirt* package uses the Expected-Maximization (EM) algorithm to estimate model parameters, and the EM algorithm can handle missing values [@chalmersMirtMultidimensionalItem2012].
+If we decide to eliminate cases with missing values, we still have a sizable number of cases, nonetheless.
+Therefore, to simplify our analysis, we only keep cases with complete responses by executing these commands:
+
+```{r}
+rwa <- rwa %>%
+  mutate_all(~na_if(., 0)) %>%  # Recoding "0" with "NA" in all columns.
+  drop_na()  # Removing cases with any "NA" values.
+```
+
+If readers prefer to keep cases with missing values, especially when the sample size is low, readers can exclude `drop_na()` command.
+
+Interestingly, if we look at {apatb-table2} again, the mean scores of the items seem to differ drastically.
+Some items have high mean scores, ranging from 6 to 7, but some of those are comparatively low.
+The RWA scale indeed has some unfavorable items but, again, there is no information in the codebook whether these unfavorable items have been reversely coded.
+However, if we look closely at ten items with high mean ($\bar{x}$ \> 6), these are the items that are supposed to be unfavorable.
+Therefore, we can reasonably assume that unfavorable items have not been reversed in the original dataset, and we should do so by running these commands:
+
+```{r}
+unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
+rwa <- rwa %>% 
+  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 to reverse code the unfavorable items.
+```
+
+First, we define a vector namely `unfav` to identify which items should be reversed, and then we use `mutate()` function to reverse the score.
+This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
+We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items does not drastically vary and has `1` as its minimum value.
 
@@
 
+## Step 3: Examining Dimensionality
+
+Next, we show the readers the ways of testing unidimensionality.
+To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggest three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
+In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this by calling this command:
+
+```{r}
+#| eval: false
+
+irt.fa(rwa, nfactors = 1, fm = "minres")
+```
+
+`irt.fa` function is to run an EFA with a polychoric correlation matrix as an input, not a Pearson's correlation matrix, because our data is ordinal.
+The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data [@harmanFactorAnalysisMinimizing1966].
+Since we have more than eight response categories, we should instead run an EFA with Pearson's correlation matrix as an input.
+Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run an EFA by calling these following commands:
+
+```{r}
+cor <- cor(rwa, method = "pearson") # First, creating a Pearson's correlation matrix.
+efa <- fa(rwa, nfactors = 1, fm = "minres") # Now, running EFA.
+print(efa) # Print the results.
+```
+
+After calling the commands, readers can find `Proportion Var` in the output, which reflects the amount of variance explained by a latent factor.
+The variance proportion of our EFA model is 0.56, which means that 56% of the total variance is explained by a latent factor.
+Since the latent factor can account for more than 50% of the variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
+To better visualize the Eigenvalues of the EFA, we can draw a scree plot using the following commands:
+
+```{r}
+#| eval: false
+
+plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
+abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
+```
+
+The first line of code is a function to plot the Eigenvalues (`efa$values`, x-axis) given the number of latent factors (y-axis).
+The option `type = "b"` implies that we ask R to display the Eigenvalues exact points and a line connecting these points along the number of factors.
+The second line of code aims to display a horizontal red line (i.e., a reference line) to see which factors have eigenvalues greater than one, which is a common criterion for factor retention.
+{apafg-fig2} shows that there is a clear break or an "elbow" that displays the location where the Eigenvalues start to level off.
+This implies that factors beyond the first may not be meaningful and could be only noise.
+Therefore, the scree plot strengthens our assumption that the item pool is, indeed, unidimensional.
+
+{{< pagebreak >}}
+
 ```{r fig2}
@@
 
+To scrutinize the unidimensionality assumption, we can also run a parallel analysis by running the following command:
+
+```{r}
+pa <- fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa")
+```
+
+Readers should find a plot similar to {apafg-fig3} appear right after executing this code as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
+This means that the parallel analysis suggests that there are six factors underlying our item pool, not one.
+However, according to {apafg-fig3}, we can see clearly that the Eigenvalues from our actual data fall steeply after the first factor.
+To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running the following command:
+
+```{r}
+pa$fa.values
+```
+
+The output shows that the Eigenvalue for the first factor is much larger than the the adjacent factor (`12.225/0.843`), further supporting the evidence for unidimensionality.
+
+{{< pagebreak >}}
+
 ```{r fig3}
@@
 ```
+
+{{< pagebreak >}}
+
+## Step 4: Model Estimation, Parameters, and Fit Statistics
+
+In this step, we start to specify a vector representing our model, such as:
+
+```{r}
+model <- 'rwa = 1-22'
+```
+
+This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are columns 1 to 22 of the data frame that we are going to use in the analysis.
+Then, we can continue to model fitting by typing the following command:
+
+```{r}
+fit <- mirt(data = rwa, 1, model = model, itemtype = "graded", SE = TRUE, verbose = FALSE)
+```
+
+The code above implies that we are fitting an IRT model using data from a data frame namely `rwa` (`data = rwa`).
+The number `1` indicates that we assume that the model contains only one $\theta$, i.e., unidimensional.
+We also set the model specification to `model = model`, which we have previously determined.
+We set `itemtype` to `"graded"` because we want to run a GRM model.
+The `SE` option is set to `TRUE` because we ask R to also estimate the standard error.
+At last, we set the `verbose` option to `FALSE` to avoid R displaying unnecessary information during the model fitting process, so the `mirt()` function can run quietly.
+
+Next, we can ask the package to calculate item discrimination and thresholds by calling these functions below:
+
+```{r}
+coefs <- coef(fit, IRTpars = TRUE, simplify = TRUE) # Saving model parameters (item discrimination (a) and threshold (b)) in a data frame.
+print(coefs) # Calling the data frame.
+summary(fit) # Displaying factor loadings and commonality.
+```
+
+The first line of code indicates that we are calling a `coef()` function to calculate item parameters from `fit` model, and then, store them in a new data frame called `coefs`.
+The `IRTpars` and `simplify` option is set to `TRUE` because we want to display the traditional IRT parameters (*a* and *b*) in a simple, readable format without showing the standard errors.
+
+The output from this procedure is presented in {apatb-table4}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
+To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorizes item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
+As we see in {apatb-table4}, item discrimination parameters of the RWA scale range from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
+All threshold parameters show a consistent increase, implying that those with higher RWA levels tend towards a higher response categories.
+However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with the RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
+This might suggest that the RWA scale is less sensitive to individuals with a low or very low RWA level.
+
+The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which are also provided in {apatb-table4}.
+Before estimating a graded response model, *mirt* ran an EFA, and now as we can see in the console, we are looking at the EFA results.
+The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi-polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
+However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.
 
@@
 
+Next, we can estimate the model goodness-of-fit (GOF) statistics (*M*~2~) by calling this command below:
+
+```{r}
+M2(fit, type = "C2")
+```
+
+```{r}
+#| include: false
+
+m2_results <- M2(fit, type="C2")
+m2_results[] <- lapply(m2_results, as.numeric)
+m2_stat <- m2_results$M2
+df <- m2_results$df
+rmsea <- m2_results$RMSEA
+rmsea = round(rmsea, digits=3)
+srmsr <- m2_results$SRMSR
+srmsr = round(srmsr, digits=3)
+tli <- m2_results$TLI
+tli = round(tli, digits=3)
+cfi <- m2_results$CFI
+cfi = round(cfi, digits=3)
+```
+
+*mirt* calculates the *M*~2~ statistics [@maydeu-olivaresLimitedInformationGoodnessoffit2006] and other GOF indices, such as Root Mean Square Error of Approximation (RMSEA), Comparative Fit Index (CFI), Tucker-Lewis Index (TLI), and Standardized Root-Mean-Square Residual (SRMSR) after running the code above.
+Here, we set the `type` option to `"C2"` because it is suitable for computing *M*~2~ statistics in polytomous models.
+The interpretation of GOF statistics is similar to a general guide for interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003], which are *RMSEA* $\leq$ 0.05, *SRMSR* \< 0.05, *TLI* and *CFI* $\geq$ 0.97.
+
+According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics.
+All GOF statistics, except for CFI, do not indicate a good fit.
+Model misfit, in this case, may be caused by local dependency between the items.
+We will explore this issue further in the next part.
+
+Next, we calculate item-level fit statistics, i.e., the signed \$\\chi\$^2^ statistics, by running the following function:
+
+```{r}
+item.fit <- itemfit(fit) # Estimating item fit statistics and saving them in a data frame.
+print(item.fit) # Calling the data frame.
+```
+
+The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
+All items have very good (low) *RMSEA* values but normally, we want the *p* values of the signed \$\\chi\$^2^ to be nonsignificant (*p* \> .05), implying that there is no discrepancy between the observed response pattern with what the model predicts.
+In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
+
+{{< pagebreak >}}
+
 ```{r apatb-table5}
@@
 #| apa-cap: Item Fit Statistics
-#| apa-note: Scaled χ2 Statistics. RMSEA = Root Mean Square Error of Approximation, CFI = Comparative Fit Index, TLI = Tucker-Lewis Index, SRMR = Standardized Root Mean Square Residual.
+#| apa-note: Signed χ2 Statistics. RMSEA = Root Mean Square Error of Approximation, CFI = Comparative Fit Index, TLI = Tucker-Lewis Index, SRMR = Standardized Root Mean Square Residual.
 #| ft.align: left
@@
 
+## Step 5: Model Residuals
+
+To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of residuals.
+First, we demonstrate how to run Local Dependency (LD) \$\\chi\$^2^ statistics [@chenLocalDependenceIndexes1997], which looks at the covariance between item pairs after accounting for $\theta$.
+In this tutorial, we demonstrate the use of Yen's *Q*~3~ statistics [@yenEffectsLocalItem1984], which is considered more powerful for detecting underlying local dependency than LD \$\\chi\$^2^ statistics [@chenLocalDependenceIndexes1997].
+To run Yen's *Q*~3~, readers can type and run this command:
+
+```{r}
+q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics.
+```
+
+This code asks R to run `residuals()` function using `"Q3"` as the `type`, and then, keep the value as a new matrix, namely `q3`.
+Again, we are only interested in item pairwise correlations above \|0.2\|, and to help us flag problematic pairs, we can make use of `findCorrelation()` function from *caret* package [@kuhnCaretClassificationRegression2024] as follows:
+
+```{r}
+findCorrelation(q3, cutoff = 0.2, verbose = T) # Flagging problematic item pairwise correlations.
+```
+
+After running the code, readers may see in their R console that residual correlations between item Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are above \|0.2\|.
+Interestingly, all of those items, except for Q4, have significant *S*-\$\\chi\$^2^ statistics (see {apatb-table5}) as well, which tells us that we have to look at these items closely and then decide whether these items have shared characteristics beyond what is explained by the model.
+
+## Step 6: IRT Plots
+
+*mirt* offers features to visualize model parameters but the options for customizing these plots are rather limited.
+*ggmirt* package [@masurGgmirt2023] fills this gap by combining *mirt* and *ggplot2* functions.
+In this tutorial, we demonstrate the use of *ggmirt* to visualize Item Probability Function (IPF), Item Information Function (IIF), Test Information Function (TIF), and conditional probability plot.
+
+To visualize IPF, readers can type and run this function:
+
+```{r}
+tracePlot(fit, title = "Item Probability Functions of RWA Scale") + labs(color="Response Categories")
+```
+
+The `labs(color)` function is to assign different colors to each curve representing a response category.
+The output of this function is {apafg-fig4}.
+In {apafg-fig4}, we see that as $\theta$ increases, respondents are more likely to choose higher response categories.
+The gradual transition from one response option to the next across the spectrum of $\theta$ values indicates that the items are capturing incremental increases in the RWA level.
+However, all IPFs of RWA items seem to be significantly overlapping and tend to peak on a $\theta$ value close to or higher than the mean.
+This implies that RWA items are more sensitive to differentiate participants with high levels of RWA.
+
+{{< pagebreak >}}
+
 ```{r fig4}
@@
 ```
+
+{{< pagebreak >}}
+
+To evaluate the performance of each item in measuring the RWA trait, we can visualize the amount of information explained by each item with this simple line of code:
+
+```{r}
+itemInfoPlot(fit, facet = TRUE, title = "Item Information Functions of the RWA Scale")
+```
+
+The `facet` option is set to `TRUE` so that R displays IIF for each item.
+The output for this function is {apafg-fig5}, where the x-axis represents the range of $\theta$, and the y-axis indicates the amount of information provided by each item.
+Peaks that are higher and narrower indicate items that are very informative for specific levels of $\theta$.
+In our case, most items provide the highest amount of information near the center to the right side of the $\theta$ distribution, indicating they are most useful for individuals with average to high levels of RWA.
 
@@
 
+It is also possible to evaluate the overall performance of the RWA scale by plotting a TIF, which can be done by running the following code:
+
+```{r}
+testInfoPlot(fit, title = "Test Information Function of the RWA Scale")
+```
+
+The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring a group of individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
+However, the RWA scale is not optimal for measuring individuals with RWA levels below or beyond this range.
+
+{{< pagebreak >}}
+
 ```{r fig6}
@@
 
+## Step 7: Computing Reliability
+
+The heart of an IRT analysis is to estimate the precision of the measure, which can vary given different levels of $\theta$.
+*mirt* provides two strategies to compute reliability that differ in their assumption regarding the distribution of $\theta$.
+First, readers may calculate marginal reliability by running this simple command:
+
+```{r}
+marginal_rxx(fit)
+```
+
+```{r}
+#| include: false
+
+m_rel <- marginal_rxx(fit)
+m_rel = round(m_rel, digits=3)
+```
+
+The output of the above code is `r m_rel`, which indicates that the overall RWA scale is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
+Since reliability can vary across different levels of $\theta$, readers can also visualize the scale's reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
+
+```{r}
+conRelPlot(fit, title = "Reliability of the RWA Scale Given to the θ Level")
+```
+
+The output of this code is {apafg-fig7}, which shows that the RWA scale can measure individuals with $\theta$ levels between -2*SD* and +4*SD* with sufficient reliability, i.e., *r*~xx~ $\geq$ 0.75.
+
+{{< pagebreak >}}
+
 ```{r fig7}
@@
 ```
+
+{{< pagebreak >}}
+
+*mirt* can also calculate the RWA scale overall reliability using $\theta$ predicted by the model.
+To compute empirical reliability, one needs to calculate the estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
+To do this, readers can run these two lines of codes:
+
+```{r}
+theta_se <- fscores(fit, full.scores.SE = TRUE) # Extracting the estimated theta score of each participant.
+empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
+```
+
+```{r}
+#| include: false
+
+e_rel <- empirical_rxx(theta_se)
+e_rel = round(e_rel, digits=3)
+```
+
+The `fscores()` function is used to compute the estimated $\theta$ value for each participant predicted by the `fit` model.
+The `full.scores.SE` is set to `TRUE` because the package uses the $\theta$ value and standard error of each participant (*SE*$\theta$) to compute the empirical reliability.
+We store the estimated $\theta$ and its *SE*$\theta$ in a new data frame, namely `theta_se`, and then run `empirical_rxx()` function to calculate empirical reliability.
+The output of these codes is `r e_rel`, which is very close to marginal reliability we estimated before.
+Notably, while marginal and empirical reliability aim to quantify the overall reliability of the scale, they base the calculations on different assumptions.
+To summarize, marginal reliability assumes that $\theta$ is normally distributed while empirical reliability uses the $\theta$ distribution predicted by the model, which still contains measurement error yet more realistic.
+
+# Discussion
+
+Construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], so reporting evidence of validity should always be an important part of the routine.
+In practice, however, researchers are less interested in examining the performance of the measures they use in their study, making it difficult to assess the credibility of their research findings [@flakeConstructValidationSocial2017; @husseyHiddenInvalidity152020].
+In this tutorial, we demonstrate the applicability of GRM analysis as part of the IRT family to help applied psychology researchers assess their measurement quality.
+We provide a non-technical guide to implementing a GRM analysis through a simple 7-step process using a real, openly available dataset.
+To maximize the effectiveness of this tutorial, we show how to perform a GRM analysis using R [@rcoreteamLanguageEnvironmentStatistical2023], an open source statistical software, and make all materials publicly available.
+
+We begin the tutorial with a theoretical overview of IRT, which underlies GRM, so that readers can relate the practical steps to the theory behind the analysis.
+Since IRT is less popular than CTT, we also briefly explain how IRT differs from CTT in its assumptions.
+However, we want to emphasize that our goal here is not to argue for the superiority of CTT over IRT, since the choice of analytic tool depends largely on the specific research question at hand.
+It is important to highlight that researchers should be aware of the merits and limitations of their chosen methods.
+Therefore, researchers should always justify why they choose a particular method over many available alternatives.
+
+Note that the model we estimated has a poor fit, perhaps due to local dependency, as we showed in steps 4 and 5.
+In practice, we recommend addressing model fitting issues before interpreting measurement precision or drawing substantive conclusions based on these estimates.
+One solution is to rephrase or to combine the content of the problematic items that indicate local dependency.
+Alternatively, readers may need to reconsider the $\theta$ structure.
+If the data is unidimensional but some of the items are locally dependent, this may indicate the existence of multiple $\theta$ within the data structure.
+In this sense, modeling the test data as a correlated multidimensional model or a bifactor model (i.e., multidimensional models with a *g* factor) may be a solution, given that a previous study shows that the RWA scale is multidimensional [@duckittMultidimensionalityRightWingAuthoritarian2013].
+Removing locally dependent items should be a last resort, as it may improve model fit but may also compromise measurement precision.
+
+Finally, we support the call for psychological researchers to shift their focus from improving their methodological practices to advancing the process of theory building [@eronenTheoryCrisisPsychology2021; @grahekAnatomyPsychologicalTheory2021; @proulxStatisticalRitualTheory2021], because formulating a sound theory always precedes the creation of a high-quality psychological measure.
+It is important to note, however, that construct validation is a critical step in the iterative process of theorizing a psychological phenomenon [@grahekAnatomyPsychologicalTheory2021].
+Therefore, we encourage applied psychology researchers to report evidence of measurement quality to ensure the validity of their findings and contribute to cumulative psychological science [@floraPurposePracticeExploratory2017].
+One way to do this is to conduct and report a GRM analysis of their measures.
+We hope that this tutorial can be seen as a small step towards the larger goal of building robust psychological science.
+
+{{< pagebreak >}}
+
+# References
+
+::: {#refs}
+:::

### 2024-01-22 annotated_codes_for_review.R

@@ -1,0 +1,307 @@
+# Tutorial on running a Graded Response Model, initiated on 09.11.2023
+
+# Welcome to the tutorial!  ------
+# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
+# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
+# examining the performance of a scale with polytomous responses (Likert-type scale).
+
+# To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
+# the right-wing authoritarianism (RWA) scale (Altemeyer). 
+
+## Step 1a: Preparation - Install and activate the packages ##  ------
+
+# First of all, we should install the packages we need for the analysis. If you already have these packages  
+# already installed in your device, you can safely skip this step.
+
+# install.packages("tidyverse", # for data wrangling
+# "psych", # for descriptive statistics and unidimensionality test
+# "devtools", # for installing R package that is not available on CRAN
+# "mirt", # for conducting the main GRM analysis
+# "caret", # for helping us detecting large residuals correlation (local independence test)
+# dependencies=TRUE)
+
+## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
+
+devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
+
+# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
+
+devtools::install_github("masurp/ggmirt")
+
+# Now, we activate the package:
+
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+
+## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
+
+# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
+# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
+
+url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
+
+# If you look closely at the .zip folder, there are two files in there; one is a .csv file (this is the dataset),
+# and two, a .txt file (a codebook). Since we need them both, we will extract them and make them readable in R environment.
+
+zip <- tempfile(fileext = ".zip") # Defining the path to temporarily save the downloaded zip file
[…]

### 2024-01-22 manuscript.qmd
manuscript submitted

@@
 rwa <- subset(ds, select = Q1:Q22)
-table1 <- psych::describe(rwa); table1 <- as.data.frame(table1)
-table1 <- table1 %>% 
+table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
+table2 <- table2 %>% 
   rownames_to_column(var="Item") %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table1 <- colformat_double(x=table1, j="Minimum", digits = 0)
-table1 <- colformat_double(x=table1, j="Maximum", digits = 0)
-table1 <- colformat_double(x=table1, j="Range", digits = 0)
-table1 <- colformat_double(x=table1, j="n", digits = 0)
-table1
+table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
+table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
+table2 <- colformat_double(x=table2, j="Range", digits = 0)
+table2 <- colformat_double(x=table2, j="n", digits = 0)
+table2
 ```
@@
 # Transforming describe() output into a APA-formatted table
-table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
-table2 <- table2 %>% 
+table3 <- psych::describe(rwa); table3 <- as.data.frame(table3)
+table3 <- table3 %>% 
   rownames_to_column(var="Item") %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
-table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
-table2 <- colformat_double(x=table2, j="Range", digits = 0)
-table2 <- colformat_double(x=table2, j="n", digits = 0)
-table2
+table3 <- colformat_double(x=table3, j="Minimum", digits = 0)
+table3 <- colformat_double(x=table3, j="Maximum", digits = 0)
+table3 <- colformat_double(x=table3, j="Range", digits = 0)
+table3 <- colformat_double(x=table3, j="n", digits = 0)
+table3
 ```
@@
 
-table3 <- as.data.frame(coefs$items)
+table4 <- as.data.frame(coefs$items)
 load <- as.data.frame(sum$rotF)
 h2 <- as.data.frame(sum$h2)
-table3 <- cbind(table3, load, h2)
-table3 <- table3 %>% 
+table4 <- cbind(table4, load, h2)
+table4 <- table4 %>% 
   rownames_to_column(var="Item") %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table3 <- colformat_double(x=table3, j="a", digits = 2)
-table3 <- colformat_double(x=table3, j="b1", digits = 2)
-table3 <- colformat_double(x=table3, j="b2", digits = 2)
-table3 <- colformat_double(x=table3, j="b3", digits = 2)
-table3 <- colformat_double(x=table3, j="b4", digits = 2)
-table3 <- colformat_double(x=table3, j="b5", digits = 2)
-table3 <- colformat_double(x=table3, j="b6", digits = 2)
-table3 <- colformat_double(x=table3, j="b7", digits = 2)
-table3 <- colformat_double(x=table3, j="b8", digits = 2)
-table3
+table4 <- colformat_double(x=table4, j="a", digits = 2)
+table4 <- colformat_double(x=table4, j="b1", digits = 2)
+table4 <- colformat_double(x=table4, j="b2", digits = 2)
+table4 <- colformat_double(x=table4, j="b3", digits = 2)
+table4 <- colformat_double(x=table4, j="b4", digits = 2)
+table4 <- colformat_double(x=table4, j="b5", digits = 2)
+table4 <- colformat_double(x=table4, j="b6", digits = 2)
+table4 <- colformat_double(x=table4, j="b7", digits = 2)
+table4 <- colformat_double(x=table4, j="b8", digits = 2)
+table4
 
@@
 
-According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics.
+According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .05, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics.
 All GOF statistics, except for CFI, do not indicate a good fit.
@@
 
-table4 <- as.data.frame(item.fit)
-table4 <- table4 %>%
+table5 <- as.data.frame(itemfit(fit))
+table5 <- table5 %>%
   select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
-  rename(Item=item, χ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
+  rename(Item=item, Sχ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table4 <- colformat_double(x=table4, j="χ2", digits = 2)
-table4 <- colformat_double(x=table4, j="df", digits = 2)
-table4 <- colformat_double(x=table4, j="RMSEA", digits = 2)
-table4 <- colformat_double(x=table4, j="p", digits = 2)
-table4
+table5 <- colformat_double(x=table5, j="Sχ2", digits = 2)
+table5 <- colformat_double(x=table5, j="df", digits = 0)
+table5 <- colformat_double(x=table5, j="RMSEA", digits = 3)
+table5 <- colformat_double(x=table5, j="p", digits = 3)
+table5
 

### 2024-08-19 manuscript.qmd
Revision round 1

--- 2024-01-22 manuscript.qmd
@@
 ---
-title: "Getting Started with the Graded Response Model (GRM): A gentle introduction and tutorial in R"
+title: "Getting Started with the Graded Response Model (GRM): An introduction and tutorial in R"
 shorttitle: "The Graded Response Model Tutorial"
@@
     affiliations:
-      - name: Universitas Airlangga
-        department: Department of Psychology
-        address: Jalan Airlangga 4-6
-        city: Surabaya
-        region: Jawa Timur, Indonesia
-        postal-code: "60286"
       - name: Ludwig-Maximilians-Universität
@@
         city: Munich
+        region: Germany
         postal-code: "80802"
+      - name: Universitas Airlangga
+        department: Department of Psychology
+        address: Jalan Airlangga 4-6
+        city: Surabaya, Indonesia
+        postal-code: "60286"
   - name: Hanif Akhtar
@@
         region: Jawa Timur, Indonesia
-abstract: "This tutorial introduces the Graded Response Model (GRM), a tool for testing measurement precision within the Item Response Theory (IRT) paradigm.
-Addressing common problems of measurement imprecision and lack of construct validity, the tutorial guides researchers through a unidimensional GRM analysis in the R environment, using psych, mirt, and ggmirt packages.
+abstract: "This tutorial introduces the Graded Response Model (GRM), a tool for testing measurement precision within the Item Response Theory (IRT) paradigm, which is useful for informing researchers about the item and person properties of their measurement.
+The tutorial aims to guide applied researchers through a unidimensional GRM analysis in the R environment, using the psych, mirt, and ggmirt packages.
 GRM is specifically designed to examine the psychometric properties of psychological scales with polytomous (Likert-style) items.
-The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM, and steps for data preparation, testing model assumptions, model fitting, and interpretation of results."
+The tutorial illustrates the procedure using data from the Open Psychometrics Database on the Right-Wing Authoritarianism (RWA) scale, outlining the theoretical underpinnings of GRM and steps for data preparation, testing model assumptions, model fitting, plotting item parameters, and interpretation of results."
 keywords:
@@
     conflict-of-interest: "We declare we have no competing interests."
-    financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD)."
+    financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD), award number 91803023."
 lang: en
@@
 
-install.packages("flextable", dependencies=TRUE) 
 library(flextable)
+data <- read.csv("data/data.csv")
+rename.items <- sprintf("%03d", 1:22)
+colnames(data) <- rename.items
+rm(rename.items)
 ```
 
-Only half of published findings include evidence of measurement validity [@flakeConstructValidationSocial2017] and a large proportion of published studies suffer from hidden invalidity [@husseyHiddenInvalidity152020].
-Lack of evidence for measurement validity can raise serious concerns about the replicability of research findings, as it directly contributes to the invalidity of the findings [@flakeMeasurementSchmeasurementQuestionable2020; @lilienfeldPsychologicalMeasurementReplication2020].
-Furthermore, the lack of evidence for measurement validity can hamper consensus on the best way to measure a construct, which becomes a major obstacle to the establishment of cumulative psychological science [@elsonPsychologicalMeasuresAren2023].
-Given these circumstances, it is critical to provide applied psychological researchers with a set of tools and practical steps to help them assess measurement validity so that they can ensure the credibility of their findings.
+To examine the quality of psychological measures, applied researchers implement statistical or formal mathematical models, which always require specific testable assumptions.
+Classical test theory (CTT) is one of the model-based measurement theories widely used to examine measurement precision, i.e., how accurate a measure is at capturing underlying psychological constructs and minimizing measurement error.
+While CTT is useful for informing researchers about measurement precision at the sample level, some want to look closely at specific individuals in their sample or items in their scale.
+In this sense, item response theory (IRT) fills this need by allowing researchers to inspect their measurement quality at the person and item level.
+IRT models are nonetheless known to be computationally intensive and less practical than CTT-based analysis, so a tutorial with didactic value can potentially help applied researchers to consider IRT analysis as a tool for their research.
 
-The purpose of this article is to provide a brief introduction to the Graded Response Model (GRM), a family of item response models specifically designed to assess the measurement precision of a polytomous (Likert-style) scale.
-We begin this paper by briefly explaining the basics of Item Response Theory (IRT) and contrasting its differences with the widely known Classical True Score Theory (CTT).
-In this paper, we aim to keep our tutorial concise, so we do not cover all IRT concepts in detail.
+The purpose of this tutorial is to provide a brief introduction to the graded response model (GRM), a family of IRT models specifically designed to assess the measurement precision of a polytomous (Likert-style) scale.
+In this paper, we aim to keep our tutorial concise, so we only briefly introduce the basics of IRT concepts.
 Interested readers are referred to available didactic texts on IRT, such as @embretsonItemResponseTheory2000 for the introductory level, and @bakerBasicsItemResponse2017 and @deayalaTheoryPracticeItem2022 for a more technical and comprehensive overview.
 
-Further, we briefly explain what GRM is and how it is specified.
+First, we briefly introduce readers to IRT and explain what GRM is and how the model is specified.
 In this part, we highlight how model and item parameters are specified and interpreted as well as visualizations derived from a GRM analysis.
-We also introduce three key assumptions underlying a GRM and how to test these assumptions.
+We also introduce three assumptions underlying a GRM and how to test these assumptions.
 We then provide an illustrative example of testing measurement precision using a GRM analysis, and in this part, we show how to practically implement a GRM analysis and interpret its results.
@@
 
-To scrutinize their measurement quality, psychological researchers have relied on two basic principles underlying psychological testing, i.e., CTT and IRT, to decompose observed scores into their *deterministic* and *random* or stochastic components [@zumboValidityFoundationalIssues2006].
-CTT, on the one hand, decomposes observed outcomes into *true* scores and *error* components.
-In practice, researchers implement this principle by performing structural equation modeling (SEM), exploratory factor analysis (EFA), or confirmatory factor analysis (CFA).
-Specifying the measurement part of a SEM model, or estimating EFA and CFA models, allows the covariance matrix of a given set of data to be decomposed into latent factors, which represent the true score or trait level, and error terms (i.e., residuals or unique variances).
-Consequently, the relationship between observed score and true score is *linear*, since true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
-IRT, on the other hand, models this relationship in a *probabilistic* rather than a linear fashion.
-More specifically, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$), and in particular, this probability takes into account item properties such as item discrimination, difficulty, and, when appropriate, guessing [@bakerBasicsItemResponse2017].
+To scrutinize their measurement quality, psychological researchers have relied on two theoretical frameworks underlying psychological testing, CTT and IRT, to decompose observed or raw scores into their *deterministic* (i.e., "true" score) and *random* (i.e., measurement error) components [@zumboValidityFoundationalIssues2006].
+In practice, researchers implementing CTT principles apply structural equation modeling (SEM), exploratory factor analysis (EFA), or confirmatory factor analysis (CFA).
+Specifying the measurement model of an SEM model, or fitting EFA and CFA models, allows the covariance matrix of a given dataset to be decomposed into latent constructs ($\theta$) representing true scores or actual skill or trait levels, with measurement error (i.e., residuals or unique variances).
 
-The most critical distinction between CTT and IRT is how they conceptualize measurement error.
-In CTT, standard deviation of the observed score (*s*) is used to calculate standard error of measurement.
-Therefore, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample regardless of their trait level.
-This shortcoming limits the utility of CTT, especially since psychologists often need to interpret individual scores, rather than just evaluate the test as a whole.
-Additionally, since standard error of measurement is also a function of reliability, reliability is assumed to be the same across different levels of a trait or ability.
-This assumption is unrealistic since researchers often encounter situations where a test is overly difficult for a group of low-performing participants, providing little information beyond an indication that their trait or ability level is significantly lower than what the test can measure.
+In this sense, CTT generally assumes that the relationship between observed score and true score is *linear*, as true score is essentially a linear transformation of observed score [@embretsonItemResponseTheory2000].
+However, IRT models this relationship differently in a *probabilistic* rather than a linear fashion.
+More sharply, an IRT model assumes a probabilistic relationship between the observed score and the latent trait being measured ($\theta$).
+The probabilistic relationship in an IRT model accounts for the statistical properties of the items, such as item discrimination, difficulty, and, if necessary, pseudo-guessing parameter [@bakerBasicsItemResponse2017].
+IRT methods were originally developed to evaluate traditional aptitude and achievement tests that measure knowledge and skill levels, but the application of IRT has been extended to personality, attitude, and other psychological scales of various formats.
 
-IRT offers an elegant solution to this issue by allowing the calculation of standard errors for each individual (*SE*$\theta$), and thus, test reliability can be inferred from the average of *SE*$\theta$ across a sample of participants [@embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
-This approach allows for the estimation of reliability at varying levels of trait or ability (i.e., test information function - TIF).
-By doing this, when a test is overly challenging for low-performing individuals or too easy for high-performing individuals, IRT can help identify the levels of trait or ability at which the test is most reliable.
-A concrete example of this is a study that examined the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
-According to this study, the sadism sub-scale of the SD4 is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring individuals with lower levels of sadism [@blotnerDarkTriadDead2022].
-In this sense, IRT models offer a more informative and nuanced perspective that proves useful for researchers who wish to closely examine the performance of their measures.
+The most critical difference between CTT and IRT is the way each framework conceptualizes measurement error.
+CTT uses standard deviation of the observed score (*s*) to calculate standard error of measurement.
+Because measurement error is based on the observed score, CTT assumes that measurement error is sample-dependent and constant for all individuals in the sample, regardless of their $\theta$ level.
+This shortcoming limits the utility of CTT, especially since psychologists often need to interpret individual scores, not just the test or the sample as a whole.
+In addition, because the standard error of measurement is also a function of reliability, it is assumed that scale reliability will always be the same across different levels of $\theta$.
+This is unrealistic because researchers often encounter situations in which a scale is "too hard" to endorse for a group of "low-performing" (i.e., low $\theta$) participants, providing little information beyond an indication that their $\theta$ level is much lower than what the scale can measure.
+
+IRT offers a solution to this issue by enabling the calculation of standard error for each individual (*SE*$\theta$), and test reliability can be inferred from the average of *SE*$\theta$ across a sample of participants [@embretsonItemResponseTheory2000; @langSciencePracticeItem2021].
+This approach allows for the estimation of reliability at varying levels of $\theta$ (i.e., test information function - TIF).
+By doing this, when a test is overly challenging for low-performing individuals or too easy for high-performing individuals, IRT analysis can help identify the levels of $\theta$ where the test is most reliable.
+A concrete example of this is a study scrutinizing the reliability of the Short Dark Tetrad (SD4) scale from an IRT perspective [@blotnerDarkTriadDead2022].
+According to this study, the sadism subscale of the SD4 scale is the most reliable for measuring individuals with average to high levels ($\bar{x}$ \< $\theta$ \< 2.5 *SD*) of sadism but suboptimal for measuring those with low levels of sadism [@blotnerDarkTriadDead2022].
+Therefore, IRT models offer a more informative approach, thus are useful for researchers who wish to closely examine the performance of their measures at the person level.
 
 Further, IRT allows researchers to examine the performance of a specific item by specifying the relationship between item score and $\theta$ given one-, two-, or three-parameter.
-The one-parameter logistic (1PL) or a Rasch model, the simplest variant of the IRT models, accounts for only item difficulty (*b*) while assuming equal item discrimination (*a*) across items.
-In practice, this model overlaps slightly with CTT in the sense that they assume that all items have equal informative value, so that the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
-This notion actually stems from a philosophical principle of *specific objectivity*, which requires that comparisons between measures remain independent of both the item and individual characteristics [@raschSpecificObjectivityAttempt1977].
-Put simply, a Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
-More concretely, the difference in depression levels between two individuals should always be the same regardless of the scale used to measure their depression levels.
-While this principle reasonably enforces objectivity in measurement practices, it requires a strong theory underlying the construct and strict requirements of data-model fit, and both of these assumptions rarely hold in a real-world scenario, especially in psychological science.
+One-parameter logistic (1PL) or Rasch model accounts only varying item difficulty (*b*) while presuming equal item discrimination (*a*) across items.
+Practically, this model slightly overlaps with CTT in the sense that they assume that all items carry equal informative value thus the estimated $\theta$ of a 1PL/Rasch model is identical to the sum score of CTT [@langSciencePracticeItem2021; @stemlerRaschMeasurementItem2021].
+In this sense, Rasch model assumes that the latent trait ($\theta$) should remain unaffected by specific items used in the test.
+For example, the difference in depression levels between two individuals should be always the same regardless of the scale used to measure their depression levels, be it Beck Depression Inventory (BDI) or Patient Health Questionnaire-9 (PHQ-9).
+While this principle reasonably enforces objectivity in measurement practices, it demands a strong theory delineating the construct and strict requirements of data-model fit, while both assumptions rarely hold in reality.
 
-Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing for differences in item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*).
-In addition, in some contexts, researchers may suspect that some parts of the probabilistic relationship between observed score and $\theta$ is explained by guessing, thus three-parameter logistic (3PL) model incorporates guessing parameter (*c*).
-The field of IRT has rapidly evolved to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
-It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false responses), and the focus of this article is nonetheless to demonstrate the utility of IRT for fitting the ordered (Likert-style) responses.
-We briefly summarize the features of the most commonly used IRT models in {apatb-table1}.
+Furthermore, the two-parameter logistic (2PL) model fills this gap by allowing item ability to differentiate individuals with varying levels of $\theta$ (i.e., item discrimination parameter - *a*) to differ.
+Additionally, in some contexts, researchers may suspect that a part of the probabilistic relationship between observed score and $\theta$ is explained by guessing thus three-parameter logistic (3PL) model incorporates pseudo-guessing parameter (*c*).
+
+Further, IRT paradigm has rapidly developed to include various models suited to specific contexts, such as handling ordinal responses [@murakiGeneralizedPartialCredit1992; @samejimaGradedResponseModel1997], categorical responses [@thissenNominalCategoriesItem2013], or assessing multidimensional traits simultaneously [@bockMarginalMaximumLikelihood1981; @chalmersMirtMultidimensionalItem2012].
+It is important to note that 1PL, 2PL, and 3PL models are only applicable to binary or dichotomous data (e.g., true/false response), and the focus of this article is nonetheless to show the utility of IRT for fitting the ordered (Likert-style) responses.
+We briefly summarize the distinctions between 1PL, 2PL, 3PL, and GRM model in {apatb-table1}.
 
@@
 #| label: apatb-table1
-#| apa-cap: Comparison Between The Commonly Used IRT Models
+#| apa-cap: Comparison Between Common IRT Models
 #| apa-note: NULL
@@
 
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
 | Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-+=========================================+=============================================================================================================================================================+=============+=========================+
+|-----------------|--------------------|-----------------|-----------------|
 | 1-PL Model (Rasch Model)    | 1\.
 Estimates only item difficulties (*b*).
+2.
+Assumes that all items have equal discrimination parameters (*a*).
+3.
+Item and person parameters are independent.
 | Dichotomous | Correct/Incorrect (0/1) |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Assumes that all items have equal discrimination parameters (*a*).
-|             |                         |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 3\.
-Item and person parameters are independent.
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
 | 2-PL Model                  | 1\.
 Estimates item difficulties (*b*) and item discrimination (*a*).
+2.
+Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.
 | Dichotomous | Correct/Incorrect (0/1) |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Less stringent than 1-PL model since it allows item discrimination parameters (*a*) to vary.
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
 | 3-PL Model                  | 1\.
 Estimates item difficulties (*b*), discrimination (*a*), and pseudo-guessing parameter (*c*).
+2.
+Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses.
 | Dichotomous | Correct/Incorrect (0/1) |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Appropriate for modeling a test data with multiple responses (e.g., multiple-choice tests), and thus, guessing might influence participants' responses.
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
 | Graded Response Model (GRM) | 1\.
 Appropriate for modeling ordinal data with more than two response categories (i.e., Likert-style).
+2.
+Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.
 | Polytomous  | Ordered Categories      |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Estimates a discrimination parameter (*a*) and multiple threshold parameters (*b*) per item.
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
-| Partial Credit Model (PCM)              | 1\.
-An extension of the 1-PL (Rasch) model for polytomous items.
-| Polytomous  | Ordered Categories      |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Estimates thresholds between adjacent categories but assumes equal discrimination across items.
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
-| Generalized Partial Credit Model (GPCM) | Extending PCM to allow differential discrimination parameters across items.
-| Polytomous  | Ordered Categories      |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
-| Nominal Response Model (NRM)            | 1\.
-Appropriate for modeling categorical responses with no order.
-| Categorical | Unordered Categories    |
-|                                         |                                                                                                                                                             |             |                         |
-|                                         | 2\.
-Estimates discrimination parameters (*a*) and multiple category-specific parameters (*b*).
-|             |                         |
-+-----------------------------------------+-------------------------------------------------------------------------------------------------------------------------------------------------------------+-------------+-------------------------+
 
@@
 
-The GRM is a family of IRT models specifically designed to analyze ordered polytomous (Likert-style) data [@samejimaGradedResponseModel1997; @samejimaGeneralGradedResponse2010; @samejimaGradedResponseModels2016].
+GRM is a family of IRT models specifically designed to analyze ordered polytomous (e.g., Likert-style) data [@samejimaGradedResponseModel1997; @samejimaGeneralGradedResponse2010; @samejimaGradedResponseModels2016].
+GRM generally can be applied to a different types of test formats, such as scales measuring behavioral outcomes [@ariasHierarchyPsychometricProperties2016], personality and attitude scales [@rauthmannInvestigatingMACHIV2013], or patient-reported outcome measures [@normandGradedResponseModelbased2006].
+Situational judgment tests (SJTs), which measure non-cognitive abilities, decision-making, and problem solving in context-specific situations [@corstjensSituationalJudgementTests2017], may also be suitable for GRM analysis when the response categories are ordered.
+
 The fundamental idea of GRM is to extend the logic of simpler dichotomous IRT models to polytomous scales by applying a probabilistic function to each response category.
-In dichotomous 2PL IRT models, the probability of answering a correct response is modeled as a function of $\theta$, item difficulty (*b*), and item discrimination (*a*).
+In dichotomous two-parameter logistic (2PL) IRT models, the probability of answering a correct response is modeled as a function of $\theta$, item difficulty (*b*), and item discrimination (*a*).
 GRM extends this idea by modeling the probability of selecting certain response category or higher on an item (i.e., *step function*) given to item difficulty (*b*) and discrimination (*a*).
@@
 
-To illustrate the step function, consider a scale measuring sadistic personality (e.g., "*watching a fist-fight excites me*," etc.) with response categories ranging from 1 (*strongly disagree*) to 4 (*strongly agree*).
+To illustrate the step function, consider a scale measuring sadistic personality (e.g., "*watching a fist-fight excites me*," etc.) with response categories ranging from 1 (*strongly disagree*) to 5 (*strongly agree*).
 Imagine these categories are hierarchically ordered from the lowest category (*strongly disagree*) to the highest (*strongly agree*), like a staircase.
@@
 Therefore, a GRM model of a five-point Likert scale calculates four item threshold parameters (*b*): the location of $\theta$ level where individuals are equally likely to respond 1 or 2 (*b*~1~), 2 or 3 (*b*~2~), 3 or 4 (*b*~3~), and 4 or 5 (*b*~4~).
-Each threshold is exactly the point where a participant is equally likely to respond to either of the adjacent response categories.
-For example, if *b*~1~ = -1.23 for the item "*watching a fist-fight excites me*", it implies that participants with sadism level 1.23 below the mean are equally likely to either answer *strongly disagree* or *moderately disagree*.
+Each threshold is exactly the point at which a participant is equally likely to respond to either of the adjacent response categories.
+Note that the level of the latent trait ($\theta$) that a person has is typically centered around a mean of zero.
+The mean represents the average level of the trait across all participants in the sample.
+When we interpret item threshold parameters, such as b1, we are considering how far an individual's $\theta$ level deviates from this mean.
+For example, if *b*~1~ = -1.23 for the item "*watching a fist-fight excites me*", this means that participants with a sadism level 1.23 below the mean might change their response from *strongly disagree* to *moderately disagree*.
 
-{apafg-fig1} shows an example of an item probability function (IPF) from an item on a scale with five response categories.
+{apafg-fig1} shows an example of an item probability function (IPF) from an item on a scale with five response categories along with the staircase illustration.
 In general, IPF describes a relationship between $\theta$ (x-axis) and the probability of endorsing a response category (y-axis - *P*$\theta$).
@@
 Item threshold is exactly the location of $\theta$ where two adjacent category probability curves cross each other.
+The "Strongly Disagree" and "Strongly Agree" curves are boundary categories in a GRM model, which results in their peaks being at the extreme ends of the $\theta$.
+These curves look different than the other because they represent the cumulative probability of selecting the most extreme responses, while intermediate categories peak in the middle and have more defined, bell-shaped curves.
+The probability curves of boundary categories simply mean that individuals at extreme $\theta$ levels are very likely to select extreme responses.
 
@@
 #| label: apafg-fig1
-#| apa-cap: An Item Probability Function from a GRM Model
+#| apa-cap: Staircase Illustration and Item Probability Functions of an Item in a GRM Model
 #| apa-note: NULL
@@
 This implies that the item pool tested using a GRM analysis should represent only one latent trait ($\theta$).
-Although it is indeed possible to account for multiple $\theta$ in an IRT model (multidimensional IRT, see @bockFullInformationItemFactor1988, we limit the scope of our tutorial to the unidimensional GRM.
+Although it is indeed possible to account for multiple $\theta$ in an IRT model (multidimensional IRT) we limit the scope of our tutorial to the unidimensional GRM.
 A unidimensional IRT model can still be robustly applied to multidimensional data if multiple latent traits are moderately intercorrelated or when there is a strong general factor (*g*) underlying the data [@reiseEvaluatingImpactMultidimensionality2015].
-To test whether an item pool represents only one $\theta$, researchers can apply a parallel analysis [@guoAssessingDimensionalityIRT2023] or a factor analysis [@hambletonAssessingDimensionalitySet1986], before specifying their GRM models.
+To test whether an item pool represents one $\theta$, researchers can apply a parallel analysis, a factor analysis, or a multidimensional scaling (MDS) [@deayalaAssessmentDimensionalityUse1991; @guoAssessingDimensionalityIRT2023], before specifying their GRM models.
 
 Relatedly, a GRM model assumes that the item pool is locally independent, as the third assumption.
-Local independence suggests that participants' responses to one item do not influence their response to another.
-It is important to note that evidence for unidimensionality does not always warrant local independence.
-As an eyeball example - consider a scale measuring trust in science, which contains: "*I trust scientists working in natural science*" and "*Most biologists are trustworthy*." While both items might measure the same latent trait (i.e., trust in science), those who trust scientists working in natural science are very likely to also trust biologists.
+Local independence suggests that participants' responses to one item do not affect their responses to another.
 To test whether items are locally independent, researchers can examine the relationships between item responses after accounting for $\theta$ by performing residual correlation analysis [@chenLocalDependenceIndexes1997].
+In practice, it is quite difficult to fully satisfy the local dependency assumptions when researchers measure a construct with multi-item measures, so we should always expect some degree of local dependency to be present in the model.
+That said, some local dependency problems may be insignificant, and there are several strategies to avoid severe model misfit due to local dependency, which we will discuss later.
+
+Note that evidence of unidimensionality does not always warrant local independence.
+As an eyeball example - consider a scale measuring trust in science that includes: "*I trust scientists working in natural science*" and "*Most biologists are trustworthy*." While both items may measure the same latent trait (i.e., trust in science), as indicated by moderate or large loading factors, those who trust scientists in the natural sciences are very likely to trust biologists as well.
+Therefore, in practice, it is likely that these items will still be moderately correlated even after taking into account their loading factors on $\theta$.
 
@@
 
-To illustrate the application of GRM for analyzing measurement precision of an ordered polytomous scale, we provide an example of a GRM analysis of the RWA scale data [@altemeyerRightwingAuthoritarianism1981; @altemeyerAuthoritarians2006].
-@altemeyerRightwingAuthoritarianism1981 defines RWA as a personality propensity to blindly abide by established authorities (i.e., authoritarian submission), to act aggressively toward individuals who are perceived to be punished by these established authorities (i.e., authoritarian aggression), and to uphold traditional values promoted by the authorities (i.e., conventionalism).
-Individuals with higher levels of RWA tend to view the world as a dangerous place [@duckittDualProcessMotivational2017], and thus, to ensure stability and safety, they are motivated to preserve social order by deferring to those whom they perceive as legal, social, or moral authorities; for instance, the government, religious institutions, or political or religious or military leaders [@saundersRightWingAuthoritarianismScale2017].
-The RWA scale developed by @altemeyerRightwingAuthoritarianism1981 remains one of the most important measures in the field of social and political psychology [@saundersRightWingAuthoritarianismScale2017], and has helped researchers to conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors [@akramiRightWingAuthoritarianismSocial2006; @osbornePsychologicalCausesSocietal2023; @sibleyPersonalityPoliticalOrientation2012].
+To illustrate the application of GRM for analyzing measurement precision of an ordered polytomous scale, we provide an example of a GRM analysis of the RWA scale data [@altemeyerAuthoritarians2006].
+@altemeyerAuthoritarians2006 defines RWA as a personality tendency to blindly obey established authorities (i.e., authoritarian submission), to act aggressively toward individuals who are perceived to be punished by these established authorities (i.e., authoritarian aggression), and to uphold traditional values promoted by authorities (i.e., conventionalism).
+Individuals with higher levels of RWA tend to view the world as a dangerous place, and thus, to ensure stability and security, they are motivated to maintain social order by deferring to those they perceive as legal, social, or moral authorities, such as the government, religious institutions, or political, religious, or military leaders [@saundersRightWingAuthoritarianismScale2017].
+The RWA scale remains one of the most important measures in the field of social and political psychology and has helped researchers conceptualize the role of RWA in shaping various social psychological outcomes, such as prejudice, political behavior, and various antisocial behaviors.
 
-In this paper, we use the most recent version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items in which participants are asked to indicate their agreement with the items on a nine-point scale ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4).
-While the RWA scale consists of three sub-dimensions, i.e., Submissiveness, Aggression, and Conventionalism, the RWA scale is theoretically assumed to be unidimensional because [@altemeyerAuthoritarians2006] shows that these sub-dimensions are strongly intercorrelated.
-While there is some evidence to the contrary [@duckittMultidimensionalityRightWingAuthoritarian2013], for the purposes of this article we will assume that the RWA scale is unidimensional.
+In this paper, we use the most recent version of the RWA scale [@altemeyerAuthoritarians2006], which consists of 22 items in which participants are asked to indicate their agreement with the items on a nine-point scale ranging from "*strongly disagree*" (-4) to "*strongly agree*" (+4), with `0` as the midpoint.
+While the RWA scale consists of three sub-dimensions, i.e., Submissiveness, Aggression, and Conventionalism, the RWA scale is theoretically assumed to be unidimensional because @altemeyerAuthoritarians2006 shows that these sub-dimensions are strongly intercorrelated.
+While there is some evidence to the contrary [@duckittMultidimensionalityRightWingAuthoritarian2013] and despite the theoretical debates existing in the literature pertaining to the dimensionality of RWA, for the purposes of this article we will assume that the RWA construct is theoretically unidimensional.
 
@@
 To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
-We also include a longer, annotated R script file (.R) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
-The Quarto file (and its corresponding .docx and .pdf output) and R script file are publicly available on [a Github repository]().
+We also include a longer, annotated R Markdown file (.Rmd) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
+In the same file, we also include a part where we demonstrate the application of GRM using a simulated dataset, which we do not include in the article, so that readers can compare the example we present here against an ideal scenario.
+The Quarto file (and its corresponding .docx and .pdf output) and an annotated R Markdown file are publicly available on [a Github repository]() (*unlinked for blind review*).
 The dataset we used in this tutorial paper was obtained from a publicly accessible [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/).
@@
 
-Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023], *ggmirt* [@masurGgmirt2023], *tidyverse* [@wickhamWelcomeTidyverse2019], *caret* [@kuhnCaretClassificationRegression2024], and *devtools* [@wickhamDevtoolsToolsMake2022], with these following commands:
+Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023], *ggmirt* [@masurGgmirt2023], and *caret* [@kuhnCaretClassificationRegression2024], and *skimr* [@waringSkimrCompactFlexible2024] with these following commands:
 
 ```{r}
+#| eval: false
+
 install.packages("tidyverse", # for data wrangling
@@
                  "caret", # for helping us detecting large residuals correlation (local independence test)
+                 "skimr", # for visualizing data distribution in a data frame at glance
                  dependencies=TRUE)
@@
 ```{r}
-library(mirt); library(ggmirt); library(psych); library(tidyverse); library(caret)
+library(mirt); library(ggmirt); library(psych); library(tidyverse); library(caret); library(skimr)
 ```
@@
 Now after the packages are activated, we need to import the dataset to our R environment.
-The dataset (`data.csv`) and codebook (`codebook.txt`) are available in `data` folder in our repository.
+The cleaned dataset (`data.csv`) and code book (`codebook.txt`) are available in `data` folder in our repository.
 Readers can download them from our repository and then simply import the dataset with the following command:
@@
 ```{r}
-ds <- read.csv("data/data.csv")
+#| eval: false
+
+data <- read.csv("path_to_data/data.csv") # Replace "path_to_data" with the actual path to your data file
 ```
 
-However, since the dataset is openly accessible in the Open Psychometrics webpage, readers can also directly import the dataset from the Open Psychometrics webpage to their R environment.
-For interested readers, we show how to do this in detail in our annotated R script file.
+The dataset provided in our repository has been cleaned, with all unfavorable items reversed scored, and is ready for analysis.
+Since the dataset is openly available on the Open Psychometrics website, readers can also import the dataset directly from the website into their R environment.
+For interested readers, we show in detail how to perform the import and data cleaning process in our annotated R Markdown file, which is available as supplementary material.
 
-Next, it is important to examine the structure of the data frame (`ds`) to get a glimpse of its structure.
-By typing `str()` command, readers can examine the variables' name, number of cases, types of variables (integer or character), and the values of each variable.
-Then readers can match the information provided in their R console to the codebook.
-
-```{r}
-str(ds)
-```
-
-According to the information provided in the codebook, the responses to the RWA scale are denoted in `Q1` to `Q22`, each representing the score of each item of the RWA scale.
-Readers can also see the information of `Q1` to `Q22` variables in their R console: these variables are integer and have values ranging from 1 to 9.
-In the codebook, there is no information regarding what these values (i.e., 1-9) mean.
-However, we could reasonably assume that participants who chose "*strongly disagree*" (-4) were scored `1`, and those who opted for "*strongly agree*" (+4) were scored `9`.
-
-Please note that we are only interested in the responses of the RWA scale, so we should subset the dataset to contain only the variables we are interested in, and then, examine the structure again.
-To this end, readers can type these commands:
-
-```{r}
-rwa <- subset(ds, select = Q1:Q22)
-str(rwa)
-```
-
-Here, we have a new data frame namely `rwa`, which contains only the responses to the RWA scale (`Q1:Q22`).
-In the data frame `rwa`, we have 22 variables with 9,881 participants.
-Before proceeding to the analysis stage, we recommend readers to inspect descriptive statistics, which we explain the procedure in the next sub-section.
-
-## Step 2: Inspecting Key Descriptive Statistics
-
-To efficiently examine descriptive statistics, readers can make use of `describe()` function from *psych* package [@revellePsychProceduresPsychological2023] by typing a simple command:
-
-```{r}
-describe(rwa)
-```
-
-This command summarizes key descriptive statistics of a data frame, and the summary is provided in {apatb-table2}.
-As we see in {apatb-table2}, all variables have a minimum value of `0`, while the minimum score should be `1`.
-
-{{< pagebreak >}}
-
-```{r apatb-table2}
-#| output: true
-#| echo: false
-#| apa-cap: Descriptive Statistics of RWA Scale
-#| apa-note: SD = Standard Deviation
-#| ft.align: left
-
-# Transforming describe() output into a APA-formatted table
-rwa <- subset(ds, select = Q1:Q22)
-table1 <- psych::describe(rwa); table1 <- as.data.frame(table1)
-table1 <- table1 %>% 
-  rownames_to_column(var="Item") %>% 
-  select(Item, mean, sd, min, max, range, n) %>% 
-  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
-  flextable() %>%
-  theme_apa() %>% 
-  line_spacing(part = "all") %>% 
-  padding(padding.top = 5, padding.bottom = 5)
-table1 <- colformat_double(x=table1, j="Minimum", digits = 0)
-table1 <- colformat_double(x=table1, j="Maximum", digits = 0)
-table1 <- colformat_double(x=table1, j="Range", digits = 0)
-table1 <- colformat_double(x=table1, j="n", digits = 0)
-table1
-```
-
-{{< pagebreak >}}
-
-Again, there is no information provided in the codebook regarding what `0` actually represents.
-Therefore, before deciding what we should do next, it is better to find out how many `0` we have in the data frame.
-To this end, we can calculate the percentage of `0` in each item by running these commands:
-
-```{r}
-zero <- colSums(rwa == 0) / nrow(rwa) * 100 # Computing the percentage of "0" in each column.
-print(zero) # Showing the percentage of "0" for each item.
-```
-
-After executing these commands, readers can see the percentage of `0` in each items in their R console, which overall are very small, ranging from 0.09% to 0.32% of the total cases.
-Since the percentages are very small, `0` is likely a code for a missing value.
-It is important to note that *mirt* package uses the Expected-Maximization (EM) algorithm to estimate model parameters, and the EM algorithm can handle missing values [@chalmersMirtMultidimensionalItem2012].
-If we decide to eliminate cases with missing values, we still have a sizable number of cases, nonetheless.
-Therefore, to simplify our analysis, we only keep cases with complete responses by executing these commands:
-
-```{r}
-rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Recoding "0" with "NA" in all columns.
-  drop_na()  # Removing cases with any "NA" values.
-```
-
-If readers prefer to keep cases with missing values, especially when the sample size is low, readers can exclude `drop_na()` command.
-
-Interestingly, if we look at {apatb-table2} again, the mean scores of the items seem to differ drastically.
-Some items have high mean scores, ranging from 6 to 7, but some of those are comparatively low.
-The RWA scale indeed has some unfavorable items but, again, there is no information in the codebook whether these unfavorable items have been reversely coded.
-However, if we look closely at ten items with high mean ($\bar{x}$ \> 6), these are the items that are supposed to be unfavorable.
-Therefore, we can reasonably assume that unfavorable items have not been reversed in the original dataset, and we should do so by running these commands:
-
-```{r}
-unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
-rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 to reverse code the unfavorable items.
-```
-
-First, we define a vector namely `unfav` to identify which items should be reversed, and then we use `mutate()` function to reverse the score.
-This is simply done by subtracting the values of the unfavorable items from the maximum score plus one.
-We can examine descriptive statistics of our modified data frame by running `describe()` function again, and as readers can see in {apatb-table3}, now mean score across items does not drastically vary and has `1` as its minimum value.
-
-{{< pagebreak >}}
-
-```{r apatb-table3}
-#| output: true
-#| echo: false
-#| apa-cap: Descriptive Statistics of RWA Scale
-#| apa-note: Descriptive Statistics After Reversing Unfavorable Items and removing cases with NA. SD = Standard Deviation.
-#| ft.align: left
-
-rwa <- rwa %>%
-  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
-  drop_na()  # Removing cases with any NA values.
-unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
-rwa <- rwa %>% 
-  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) to reverse code the unfavorable items.
-# Transforming describe() output into a APA-formatted table
-table2 <- psych::describe(rwa); table2 <- as.data.frame(table2)
-table2 <- table2 %>% 
-  rownames_to_column(var="Item") %>% 
-  select(Item, mean, sd, min, max, range, n) %>% 
-  rename(Mean=mean, SD=sd, Minimum=min, Maximum=max, Range=range) %>% 
-  flextable() %>% 
-  theme_apa() %>% 
-  line_spacing(part = "all") %>% 
-  padding(padding.top = 5, padding.bottom = 5)
-table2 <- colformat_double(x=table2, j="Minimum", digits = 0)
-table2 <- colformat_double(x=table2, j="Maximum", digits = 0)
-table2 <- colformat_double(x=table2, j="Range", digits = 0)
-table2 <- colformat_double(x=table2, j="n", digits = 0)
-table2
-```
-
-{{< pagebreak >}}
-
-## Step 3: Examining Dimensionality
+## Step 2: Examining Dimensionality
 
 Next, we show the readers the ways of testing unidimensionality.
-To test the number of latent factors of an item pool, @deayalaAssessmentDimensionalityUse1991 suggest three alternatives, which are multidimensional scaling (MDS), EFA, and CFA.
+This step is important so that researchers can decide whether applying unidimensional GRM analysis is the right choice.
+In doing so, there are three available alternatives, which are multidimensional scaling (MDS), EFA, or CFA [@deayalaAssessmentDimensionalityUse1991].
 In this tutorial, we demonstrate the use of EFA, and *psych* package provides a very efficient way to do this by calling this command:
@@
 
-irt.fa(rwa, nfactors = 1, fm = "minres")
+irt.fa(data, nfactors = 1, fm = "minres")
 ```
 
-`irt.fa` function is to run an EFA with a polychoric correlation matrix as an input, not a Pearson's correlation matrix, because our data is ordinal.
-The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data [@harmanFactorAnalysisMinimizing1966].
-Since we have more than eight response categories, we should instead run an EFA with Pearson's correlation matrix as an input.
-Therefore, we first need to create a Pearson's correlation matrix from our data frame, and then, run an EFA by calling these following commands:
+`irt.fa()` function is to run an EFA with a polychoric correlation matrix as an input when the data are ordinal, which is often the case in practice, especially when researchers are working with a five-option Likert scale.
+Since we have more than eight response categories in our current dataset, after running `irt.fa()` function, an error message, "*polychoric is probably not needed*", should appear in the console.
+Therefore, another option would be running an EFA manually with a correlation matrix as an input.
+To determine which correlation method should be used when constructing the correlation matrix, we need to check whether items are normally distributed by calling this command:
 
 ```{r}
-cor <- cor(rwa, method = "pearson") # First, creating a Pearson's correlation matrix.
-efa <- fa(rwa, nfactors = 1, fm = "minres") # Now, running EFA.
+#| eval: false
+skim(data)
+```
+
+After running this command, readers can see in the console a table summarizing the data frame, including histograms of each item in `hist` column.
+Here, readers would find that all items are heavily skewed, so that we should use a Spearman correlation matrix as an input for EFA.
+In doing so, we need to create a Spearman correlation matrix from our data frame, and then, run an EFA by calling these following commands:
+
+```{r}
+cor <- cor(data, method = "spearman") # First, creating a Spearman correlation matrix.
+efa <- fa(cor, nfactors = 1, fm = "minres") # Now, running EFA.
 print(efa) # Print the results.
@@
 After calling the commands, readers can find `Proportion Var` in the output, which reflects the amount of variance explained by a latent factor.
-The variance proportion of our EFA model is 0.56, which means that 56% of the total variance is explained by a latent factor.
+The variance proportion of our EFA model is `0.53`, which means that 53% of the total variance is explained by a latent factor.
 Since the latent factor can account for more than 50% of the variance, we can reasonably assume that the latent factor underlying our data is unidimensional.
-To better visualize the Eigenvalues of the EFA, we can draw a scree plot using the following commands:
+To better visualize the eigenvalues of the EFA, we can draw a scree plot using the following commands:
 
@@
 
-The first line of code is a function to plot the Eigenvalues (`efa$values`, x-axis) given the number of latent factors (y-axis).
-The option `type = "b"` implies that we ask R to display the Eigenvalues exact points and a line connecting these points along the number of factors.
-The second line of code aims to display a horizontal red line (i.e., a reference line) to see which factors have eigenvalues greater than one, which is a common criterion for factor retention.
-{apafg-fig2} shows that there is a clear break or an "elbow" that displays the location where the Eigenvalues start to level off.
-This implies that factors beyond the first may not be meaningful and could be only noise.
-Therefore, the scree plot strengthens our assumption that the item pool is, indeed, unidimensional.
+{apafg-fig2} shows that there is a distinct break or "elbow" that indicates where the eigenvalues begin to level off below `1`.
+This implies that factors beyond the first may not be meaningful and could be just noise.
+Therefore, the scree plot supports our assumption that the variance of the item pool is mainly explained by one latent factor.
 
@@
 
-To scrutinize the unidimensionality assumption, we can also run a parallel analysis by running the following command:
+In a case where there is no or unclear theoretical assumption or empirical evidence of dimensionality, such that researchers are unsure of the $\theta$ structure of their item pool, it is suggested that a parallel analysis be performed before proceeding with EFA [@liuInitialInvestigationModified2007].
+The purpose of running a parallel analysis is to identify the optimal number of factors underlying the item pool by comparing the eigenvalues of the data with a set of simulated data sets.
+Parallel analysis can be easily applied by running the following command:
 
 ```{r}
-pa <- fa.parallel(rwa, nfactors = 1, fm = "minres", fa = "fa")
+fa.parallel(data, fm="minres", fa="pc")
 ```
 
-Readers should find a plot similar to {apafg-fig3} appear right after executing this code as well as a message, which says: `Parallel analysis suggests that the number of factors =  6  and the number of components =  NA`.
-This means that the parallel analysis suggests that there are six factors underlying our item pool, not one.
-However, according to {apafg-fig3}, we can see clearly that the Eigenvalues from our actual data fall steeply after the first factor.
-To paint a clearer picture, we can examine the Eigenvalues of each latent factor estimated by the parallel analysis by running the following command:
+As suggested by @guoAssessingDimensionalityIRT2023, here we use principal component analysis (PCA - `fa="pc"`) to estimate the eigenvalues.
+When researchers have a Likert scale with five or more but less than 8 response categories, it is recommended to perform a parallel analysis with a polychoric correlation matrix [@guoAssessingDimensionalityIRT2023], which can be done by adding `cor = "poly"` to the above command.
+
+After running the code, readers will see in the console that parallel analysis suggests two components underlying the item pool but this is not a clear cut since the eigenvalue of the second component is only slightly above `1` (i.e., `1.303`).
+In this situation, we can run another EFA to be sure by assuming that there are two factors underlying the data, and then compare the results with the single-factor EFA we ran earlier.
 
 ```{r}
-pa$fa.values
+efa2 <- fa(cor, nfactors = 2, fm = "minres") # Running EFA assuming that there are two factors.
+print(efa2) # Print the results.
 ```
 
-The output shows that the Eigenvalue for the first factor is much larger than the the adjacent factor (`12.225/0.843`), further supporting the evidence for unidimensionality.
+EFA with two factors has slightly more variance explained and lower root mean square residuals (`Cumulative Var` = 0.57, RMSR = 0.03) than the EFA we ran earlier (`Proportion Var` = 0.53, RMSR = 0.05), indicating a better model fit.
+However, the correlation between the first and second factors is large (*r* = 0.79).
+In this case, it is difficult to definitively conclude that our data show a single factor (i.e., unidimensional), but we will proceed with the unidimensional GRM analysis because the RWA theory underlying the item pool argues for unidimensionality, the one-factor EFA shows acceptable evidence of unidimensionality, and, in general, a one-factor model is easier to interpret.
+It should be noted, however, that we can expect some local dependency problems with our one-dimensional GRM model later, since the two-factor model is a slightly more accurate representation of our data, according to our EFA results.
 
-{{< pagebreak >}}
+When stronger evidence of unidimensionality is needed, especially when testing the precision of a newly developed scale, researchers can also cross-validate the $\theta$ structure of their scale on another sample by running a CFA [@floraPurposePracticeExploratory2017], and then decide to run a uni- or multidimensional GRM analysis after obtaining stronger evidence of the number of $\theta$ underlying the item pool.
+Note that parallel analyses, EFA, and CFA are used to uncover the $\theta$ structure of the item pool and to focus on the snippet of the performance of the measure at the sample level.
+If researchers are interested in item-level and person-level parameters, then GRM should still be conducted.
+EFA and GRM can be performed on the same dataset, since the purpose of each analysis is different, but EFA and CFA should be performed on a different sample, with EFA performed at the early phase and CFA performed at a later stage, after obtaining preliminary evidence of the underlying $\theta$ structure [@floraPurposePracticeExploratory2017].
 
-```{r fig3}
-#| output: true
-#| echo: false
-#| label: apafg-fig3
-#| apa-cap: Parallel Analysis
-#| apa-note: NULL
-
-plot(pa)
-```
-
-{{< pagebreak >}}
-
-## Step 4: Model Estimation, Parameters, and Fit Statistics
+## Step 3: Model Estimation, Parameters, and Fit Statistics
 
@@
 ```{r}
-model <- 'rwa = 1-22'
+model <- 'theta = 1-22'
 ```
 
-This code implies that we want to estimate a model with $\theta$ namely `rwa`, and the items representing the $\theta$ are columns 1 to 22 of the data frame that we are going to use in the analysis.
+This code implies that we want to estimate a model with one $\theta$ namely `theta`, which is supported by EFA results we ran earlier.
+The items representing the $\theta$ are columns 1 to 22 of the data frame that we are going to use in the analysis.
 Then, we can continue to model fitting by typing the following command:
@@
 ```{r}
-fit <- mirt(data = rwa, 1, model = model, itemtype = "graded", SE = TRUE, verbose = FALSE)
+fit <- mirt(data = data, 1, model = model, itemtype = "graded", SE = TRUE, verbose = FALSE)
 ```
-
-The code above implies that we are fitting an IRT model using data from a data frame namely `rwa` (`data = rwa`).
-The number `1` indicates that we assume that the model contains only one $\theta$, i.e., unidimensional.
-We also set the model specification to `model = model`, which we have previously determined.
-We set `itemtype` to `"graded"` because we want to run a GRM model.
-The `SE` option is set to `TRUE` because we ask R to also estimate the standard error.
-At last, we set the `verbose` option to `FALSE` to avoid R displaying unnecessary information during the model fitting process, so the `mirt()` function can run quietly.
 
@@
 
-The first line of code indicates that we are calling a `coef()` function to calculate item parameters from `fit` model, and then, store them in a new data frame called `coefs`.
-The `IRTpars` and `simplify` option is set to `TRUE` because we want to display the traditional IRT parameters (*a* and *b*) in a simple, readable format without showing the standard errors.
+The output from this procedure is presented in {apatb-table2}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
+To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorizes item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
 
-The output from this procedure is presented in {apatb-table4}, which shows item discrimination (*a*) of each item and item thresholds (*b1-b8*) of each response category within an item.
-To interpret *a*, readers can use a rule of thumb suggested by @bakerBasicsItemResponse2017, which categorizes item discrimination exceeding 0.00, 0.35, 0.65, 1.35, and 1.70, as very low, low, moderate, high, and very high.
-As we see in {apatb-table4}, item discrimination parameters of the RWA scale range from high to very high (1.57 (Q1) to 3.32 (Q7)), suggesting efficient differentiation among individuals at different RWA levels.
-All threshold parameters show a consistent increase, implying that those with higher RWA levels tend towards a higher response categories.
-However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with the RWA level around the mean are likely to opt for "*strongly disagree*" or stepping to its adjacent response category.
-This might suggest that the RWA scale is less sensitive to individuals with a low or very low RWA level.
+As we see in {apatb-table2}, item discrimination parameters of the RWA scale range from high to very high (1.57 - item #1 to 3.32 - item #7), indicating a strong ability of RWA items to differentiate between individuals with different RWA levels.
+The threshold parameters consistently increase, suggesting that individuals with higher RWA levels are more likely to choose higher response categories.
+However, *b1* and *b2* for all items are very close to zero, which indicates that individuals with the RWA level around the mean are likely to opt for the lowest extreme category (i.e., "*strongly disagree*" or -4) or stepping to its adjacent response category.
+This might suggest that the RWA scale is less sensitive to individuals with a low and very low RWA level.
 
-The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which are also provided in {apatb-table4}.
+The third line of code is a function to calculate a factor loading ($\lambda$) and commonality (h^2^) of each item, which are also provided in {apatb-table2}.
 Before estimating a graded response model, *mirt* ran an EFA, and now as we can see in the console, we are looking at the EFA results.
-The results are slightly different from our previous EFA analysis, because *mirt* runs EFA using a quasi-polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Pearson's correlation matrix as an input.
+The results are slightly different from an EFA analysis we ran earlier, because *mirt* runs EFA using a quasi-polychoric correlation matrix, while the one we ran earlier to test unidimensionality used a Spearman correlation matrix as an input.
 However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.
@@
 
-```{r apatb-table4}
+```{r apatb-table2}
 #| output: true
@@
 #| apa-note: a = Discrimination, b1-b8 = Response specific threshold parameters, λ = Standardized Factor Loadings, h2 = Commonality.
+There are 8 threshold parameters because each threshold represents the point of transition between adjacent categories, not the number of categories themselves.
 #| ft.align: left
@@
 
-table3 <- as.data.frame(coefs$items)
+table2 <- as.data.frame(coefs$items)
 load <- as.data.frame(sum$rotF)
 h2 <- as.data.frame(sum$h2)
-table3 <- cbind(table3, load, h2)
-table3 <- table3 %>% 
+table2 <- cbind(table2, load, h2)
+table2 <- table2 %>% 
   rownames_to_column(var="Item") %>% 
-  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, rwa, h2) %>% 
-  rename(λ=rwa) %>% 
+  select(Item, a, b1, b2, b3, b4, b5, b6, b7, b8, theta, h2) %>% 
+  rename(λ=theta) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table3 <- colformat_double(x=table3, j="a", digits = 2)
-table3 <- colformat_double(x=table3, j="b1", digits = 2)
-table3 <- colformat_double(x=table3, j="b2", digits = 2)
-table3 <- colformat_double(x=table3, j="b3", digits = 2)
-table3 <- colformat_double(x=table3, j="b4", digits = 2)
-table3 <- colformat_double(x=table3, j="b5", digits = 2)
-table3 <- colformat_double(x=table3, j="b6", digits = 2)
-table3 <- colformat_double(x=table3, j="b7", digits = 2)
-table3 <- colformat_double(x=table3, j="b8", digits = 2)
-table3
+table2 <- colformat_double(x=table2, j="a", digits = 2)
+table2 <- colformat_double(x=table2, j="b1", digits = 2)
+table2 <- colformat_double(x=table2, j="b2", digits = 2)
+table2 <- colformat_double(x=table2, j="b3", digits = 2)
+table2 <- colformat_double(x=table2, j="b4", digits = 2)
+table2 <- colformat_double(x=table2, j="b5", digits = 2)
+table2 <- colformat_double(x=table2, j="b6", digits = 2)
+table2 <- colformat_double(x=table2, j="b7", digits = 2)
+table2 <- colformat_double(x=table2, j="b8", digits = 2)
+table2
 
@@
 
-Next, we can estimate the model goodness-of-fit (GOF) statistics (*M*~2~) by calling this command below:
+Next, we can estimate the model goodness-of-fit statistics (*M*~2~) by calling this command below:
 
@@
 m2_stat <- m2_results$M2
+m2_stat = round(m2_stat, digits=2)
 df <- m2_results$df
@@
 
-*mirt* calculates the *M*~2~ statistics [@maydeu-olivaresLimitedInformationGoodnessoffit2006] and other GOF indices, such as Root Mean Square Error of Approximation (RMSEA), Comparative Fit Index (CFI), Tucker-Lewis Index (TLI), and Standardized Root-Mean-Square Residual (SRMSR) after running the code above.
-Here, we set the `type` option to `"C2"` because it is suitable for computing *M*~2~ statistics in polytomous models.
-The interpretation of GOF statistics is similar to a general guide for interpreting GOF in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003], which are *RMSEA* $\leq$ 0.05, *SRMSR* \< 0.05, *TLI* and *CFI* $\geq$ 0.97.
+*mirt* calculates the *M*~2~ statistics for model fit [@maydeu-olivaresLimitedInformationGoodnessoffit2006] and other goodness-of-fit indices, such as Root Mean Square Error of Approximation (RMSEA), Comparative Fit Index (CFI), Tucker-Lewis Index (TLI), and Standardized Root-Mean-Square Residual (SRMSR) after running the code above.
+Here, we set the `type` option to `C2` because it is suitable for computing *M*~2~ statistics in polytomous models.
+*M*~2~ statistic is conceptually similar to the $\chi$ ^2^ test of overall model fit in SEM [@maydeu-olivaresLimitedInformationGoodnessoffit2006], so the interpretation is similar.
+The rule of thumb for other goodness of fit statistics is also similar to a general guide for interpreting goodness of fit in CFA or SEM models [@schermelleh-engelEvaluatingFitStructural2003], which is *RMSEA* $\leq$ 0.05, *SRMSR* \< 0.05, *TLI* and *CFI* $\geq$ 0.97, for a good fit.
+While 0.05 \< *RMSEA* $\leq$ 0.08, 0.05 \< *SRMSR* $\leq$ 0.10, 0.97 \< *TLI* and *CFI* $\leq$ 0.95, for an acceptable fit.
 
-According to our analysis, the model overall does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .005, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics.
-All GOF statistics, except for CFI, do not indicate a good fit.
-Model misfit, in this case, may be caused by local dependency between the items.
-We will explore this issue further in the next part.
+According to our analysis, the model does not fit the data well (*M*~2~(`r df`) = `r m2_stat`, *p* \< .001, *RMSEA* = `r rmsea`, *SRMSR* = `r srmsr`, TLI = `r tli`, CFI = `r cfi`), because there is a significant discrepancy between response patterns predicted by the model with the data, as shown by significant *M*~2~ statistics.
+When faced with this situation, readers are advised to tentatively reject the model and then identify the sources and magnitude of the misfit [@klinePrinciplesPracticeStructural2023; @liuIdentifyingSourceMisfit2014].
+It is likely that a model fails the $\chi$ ^2^ test, but the residuals show an insignificant discrepancy between the observed and expected values when we have a very large sample [@klinePrinciplesPracticeStructural2023; @maydeu-olivaresEvaluatingFitIRT2015], which may well be the case since we have more than 9,000 cases in our dataset.
 
-Next, we calculate item-level fit statistics, i.e., the signed \$\\chi\$^2^ statistics, by running the following function:
+Overall, our model is neither a poorly fit nor a good fit.
+RMSEA shows a poor fit, while CFI and TLI indicate a good fit.
+However, the most important goodness-of-fit statistics we should pay attention to is SRMSR, since it provides the average effect size of model misfit [@maydeu-olivaresEvaluatingFitIRT2015].
+SRMSR is only slightly above the `0.05` cutoff, suggesting that some areas of our model may be misfitting, but the misfit is not so severe.
+With this in mind, it is noteworthy to identify the source of the misfit, and local dependency between items is the main suspect.
+
+Next, we calculate item-level fit statistics, i.e., the signed $\chi$ ^2^ statistics, by running the following function:
 
@@
 
-The output of this function is provided in {apatb-table5}, which shows fit statistics for an individual item.
-All items have very good (low) *RMSEA* values but normally, we want the *p* values of the signed \$\\chi\$^2^ to be nonsignificant (*p* \> .05), implying that there is no discrepancy between the observed response pattern with what the model predicts.
-In {apatb-table5}, only three items here are nonsignificant (Q2, Q4, and Q12), which strengthens our suspicion that the RWA items might not be locally independent.
+The output of this function is provided in {apatb-table3}, which shows that the signed $\chi$ ^2^ for item fit [@orlandoLikelihoodBasedItemFitIndices2000] for each item.
+All items have very good *RMSEA* values ($\leq$ 0.05), indicating that each individual item fits the underlying IRT model.
+Normally, we also want the *p* values of the signed $\chi$ ^2^ to be insignificant (*p* \> .05), suggesting that there is no discrepancy between the observed response pattern and what the model predicts.
+In {apatb-table3}, however, only three items here are not significant (#2, #4, and #12), which is expected when we have a very large sample [@klinePrinciplesPracticeStructural2023].
+Nonetheless, it may also be the case that some of these items are not locally independent.
+We will explore this issue further in the next part.
 
@@
 
-```{r apatb-table5}
+```{r apatb-table3}
 #| output: true
@@
 
-table4 <- as.data.frame(item.fit)
-table4 <- table4 %>%
-  select(item, S_X2, df.S_X2, RMSEA.S_X2, p.S_X2) %>% 
-  rename(Item=item, χ2=S_X2, df=df.S_X2, RMSEA=RMSEA.S_X2, p=p.S_X2) %>% 
+table3 <- as.data.frame(itemfit(fit))
+table3 <- table3 %>%
+  select(item, S_X2, df.S_X2, p.S_X2, RMSEA.S_X2) %>% 
+  rename(Item=item, Sχ2=S_X2, df=df.S_X2, p=p.S_X2, RMSEA=RMSEA.S_X2) %>% 
   flextable() %>% 
@@
   padding(padding.top = 5, padding.bottom = 5)
-table4 <- colformat_double(x=table4, j="χ2", digits = 2)
-table4 <- colformat_double(x=table4, j="df", digits = 2)
-table4 <- colformat_double(x=table4, j="RMSEA", digits = 2)
-table4 <- colformat_double(x=table4, j="p", digits = 2)
-table4
+table3 <- colformat_double(x=table3, j="Sχ2", digits = 2)
+table3 <- colformat_double(x=table3, j="df", digits = 0)
+table3 <- colformat_double(x=table3, j="p", digits = 4)
+table3 <- colformat_double(x=table3, j="RMSEA", digits = 3)
+table3
 
@@
 
-## Step 5: Model Residuals
+## Step 4: Model Residuals
 
-To ensure that the items are locally independent, *mirt* offers several alternatives to examine the behavior of residuals.
-First, we demonstrate how to run Local Dependency (LD) \$\\chi\$^2^ statistics [@chenLocalDependenceIndexes1997], which looks at the covariance between item pairs after accounting for $\theta$.
-In this tutorial, we demonstrate the use of Yen's *Q*~3~ statistics [@yenEffectsLocalItem1984], which is considered more powerful for detecting underlying local dependency than LD \$\\chi\$^2^ statistics [@chenLocalDependenceIndexes1997].
+To test whether the item pool is locally independent, *mirt* provides several alternatives for examining the behavior of the residuals.
+The first option is to run the Local Dependency (LD) $\chi$ ^2^ statistic [@chenLocalDependenceIndexes1997], which looks at the covariance between pairs of items after accounting for $\theta$.
+In this tutorial, we demonstrate the use of Yen's *Q*~3~ statistic [@yenEffectsLocalItem1984], which is deemed more powerful for detecting underlying local dependency in unidimensional models, especially when dealing with polytomous data, than the LD $\chi$ ^2^ statistic [@chenLocalDependenceIndexes1997].
+For comparison, we also demonstrate the use of LD $\chi$ ^2^ statistics in the annotated R Markdown file.
 To run Yen's *Q*~3~, readers can type and run this command:
@@
 
-This code asks R to run `residuals()` function using `"Q3"` as the `type`, and then, keep the value as a new matrix, namely `q3`.
-Again, we are only interested in item pairwise correlations above \|0.2\|, and to help us flag problematic pairs, we can make use of `findCorrelation()` function from *caret* package [@kuhnCaretClassificationRegression2024] as follows:
+As a practical guideline, @chenLocalDependenceIndexes1997 suggests that a critical value for the *Q*~3~ statistic is around \|0.2\|, so we are interested in item pairwise correlations above \|0.2\|.
+To help us flag problematic, locally dependent pairs, we can use the `findCorrelation()` function from the *caret* package as follows:
 
@@
 
-After running the code, readers may see in their R console that residual correlations between item Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are above \|0.2\|.
-Interestingly, all of those items, except for Q4, have significant *S*-\$\\chi\$^2^ statistics (see {apatb-table5}) as well, which tells us that we have to look at these items closely and then decide whether these items have shared characteristics beyond what is explained by the model.
+After running the code, readers may see in their R console that the residual correlations between items #3, #4, #5, #7, #11, #13, #14, #18, #19, and #21 are above \|0.2\|.
+As suspected, all of these items, except #4, also have significant *S*-$\chi$ \$^2^ statistics (see {apatb-table3}), which tells us that we need to look at these items closely and then decide whether these items have common characteristics beyond what is explained by the model.
+While it is worth looking at all of these item pairs, we recommend that readers prioritize the investigation of severe local dependencies, as indicated by item pair correlations above \|0.3\| (i.e., #14 and #3, #11 and #20, #5 and #1, #18 and #2), before addressing the rest of problematic pairs.
 
-## Step 6: IRT Plots
+## Step 5: IRT Plots
 
 *mirt* offers features to visualize model parameters but the options for customizing these plots are rather limited.
-*ggmirt* package [@masurGgmirt2023] fills this gap by combining *mirt* and *ggplot2* functions.
+*ggmirt* package fills this gap by combining *mirt* and *ggplot2* functions.
 In this tutorial, we demonstrate the use of *ggmirt* to visualize Item Probability Function (IPF), Item Information Function (IIF), Test Information Function (TIF), and conditional probability plot.
@@
 
-The `labs(color)` function is to assign different colors to each curve representing a response category.
-The output of this function is {apafg-fig4}.
-In {apafg-fig4}, we see that as $\theta$ increases, respondents are more likely to choose higher response categories.
-The gradual transition from one response option to the next across the spectrum of $\theta$ values indicates that the items are capturing incremental increases in the RWA level.
+The output of this function is {apafg-fig3}, which we can see that as $\theta$ increases, participants are more likely to choose higher response categories.
+The gradual transition from one response option to the next across the spectrum of $\theta$ values indicates that the items are capturing incremental increases in the RWA level, which is consistent with the gradual increase in threshold parameters we saw in the previous step.
 However, all IPFs of RWA items seem to be significantly overlapping and tend to peak on a $\theta$ value close to or higher than the mean.
@@
 
-```{r fig4}
+```{r fig3}
 #| output: true
 #| echo: false
-#| label: apafg-fig4
+#| label: apafg-fig3
 #| apa-cap: Item Probability Functions of RWA Scale
@@
 
-tracePlot(fit, facet=T, title = "Item Probability Functions of RWA Scale") + labs(color="Response Options")
+tracePlot(fit, facet=T, title = "Item Probability Functions of RWA Scale") + labs(color="Response Options" +
+  facet_wrap(~item, ncol = 5))
 ```
@@
 
-The `facet` option is set to `TRUE` so that R displays IIF for each item.
-The output for this function is {apafg-fig5}, where the x-axis represents the range of $\theta$, and the y-axis indicates the amount of information provided by each item.
+The output for this function is {apafg-fig4} where the x-axis represents the range of $\theta$, and the y-axis indicates the amount of information provided by each item.
 Peaks that are higher and narrower indicate items that are very informative for specific levels of $\theta$.
@@
 
-```{r fig5}
+```{r fig4}
 #| output: true
 #| echo: false
-#| label: apafg-fig5
+#| label: apafg-fig4
 #| apa-cap: Item Information Curves of the RWA Scale
@@
 
-itemInfoPlot(fit, facet=T, title = "Item Information Curves of the RWA Scale")
+itemInfoPlot <- function(model,
+                         items = NULL,
+                         facet = FALSE,
+                         title = "Item Information Curves",
+                         theta_range = c(-4,4),
+                         legend = FALSE) {
+
+  data <- model@Data$data %>% as.data.frame
+
+  theta_range = seq(theta_range[1], theta_range[2], by = .01)
+
+  test <- NULL
+  for(i in 1:length(data)){
+    theta <- matrix(theta_range)
+    test[[i]] <- testinfo(model, Theta = theta, which.items = i)
+  }
+
+  if (!is.null(items)) {
+    test <- test[items]
+  }
+
+  # Assign proper item names
+  names(test) <- sprintf('item.%03d', 1:length(test))  # Produces names like item.001, item.002, etc.
+
+  test <- as.data.frame(test, theta) %>%
+    tibble::rownames_to_column("theta") %>%
+    gather(key, value, -theta) %>%
+    mutate(theta = as.numeric(theta),
+           key = factor(key, levels = sprintf('item.%03d', 1:length(test))))  # Set factor levels for proper ordering
+
+  # final plot
+  if(isFALSE(facet)) {
+    p <- ggplot(test, aes(theta, value, colour = key)) + 
+      geom_line() + 
+      labs(x = expression(theta), 
+           y = expression(I(theta)), 
+           title = title,
+           color = "Item") +
+      theme_minimal() +
+      scale_color_brewer(palette = 7)
+
+    if(isFALSE(legend)) {
+      p <- p + guides(color = FALSE)
+    }
+
+  } else {
+   p <- ggplot(test, aes(theta, value)) + 
+      geom_line() + 
+      facet_wrap(~key, ncol = 5) +  # You can adjust ncol to the number of columns you prefer
+      labs(x = expression(theta), 
+           y = expression(I(theta)), 
+           title = title) +
+      theme_minimal() 
+  }
+  return(p)
+}
+
+itemInfoPlot(fit, facet = TRUE, title = "Item Information Curves of the RWA Scale")
 ```
@@
 
-The output of this code is {apafg-fig6}, and according to this, the RWA scale as a whole is informative for measuring a group of individuals with a wide range of RWA levels, i.e., between -2*SD* to +4*SD*.
-However, the RWA scale is not optimal for measuring individuals with RWA levels below or beyond this range.
+The output of this code is {apafg-fig5}, which we can see that the RWA scale as a whole is informative for measuring a group of individuals with a wide range of RWA levels, i.e., between -2*SD* (low) to +4*SD* (very high).
+Moreover, the RWA scale is not optimal for measuring individuals with RWA levels below or beyond this range, as we can see in {apafg-fig5} that standard error increases below -3*SD*.
 
@@
 
-```{r fig6}
+```{r fig5}
 #| output: true
 #| echo: false
-#| label: apafg-fig6
+#| label: apafg-fig5
 #| apa-cap: Test Information Curve of the RWA Scale
@@
 
-## Step 7: Computing Reliability
+## Step 6: Computing Reliability
 
@@
 
-The output of the above code is `r m_rel`, which indicates that the overall RWA scale is reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution [@chalmersAnswerDifferenceEmpirical2019].
-Since reliability can vary across different levels of $\theta$, readers can also visualize the scale's reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
+The output of the above code is `r m_rel`, which indicates that the overall RWA scale is highly reliable, assuming that the underlying $\theta$ distribution follows the Gaussian or normal distribution.
+Since marginal reliability can vary across different levels of $\theta$, readers can also visualize the marginal reliability given the levels of $\theta$ by running the function of *ggmirt* package, as follows:
 
@@
 
-The output of this code is {apafg-fig7}, which shows that the RWA scale can measure individuals with $\theta$ levels between -2*SD* and +4*SD* with sufficient reliability, i.e., *r*~xx~ $\geq$ 0.75.
+The output of this code is {apafg-fig6}, which shows that the RWA scale can measure individuals with $\theta$ levels between approximately -1.75*SD* and +2.75*SD* with optimal reliability, i.e., *r*~xx~ $\geq$ 0.80.
+This means that the RWA scale is most reliable for participants with low to high levels of RWA, but it becomes less reliable when measuring participants with extremely low ($\theta$ \< -1.75*SD*) or extremely high levels of RWA ($\theta$ \> 2.75*SD*).
 
@@
 
-```{r fig7}
+```{r fig6}
 #| output: true
 #| echo: false
-#| label: apafg-fig7
+#| label: apafg-fig6
 #| apa-cap: Reliability of the RWA Scale Given to the θ Level
@@
 
-*mirt* can also calculate the RWA scale overall reliability using $\theta$ predicted by the model.
-To compute empirical reliability, one needs to calculate the estimated $\theta$ value of each participant first, and then, calculate reliability based on these values.
+*mirt* can also compute the overall reliability of the RWA scale, assuming the model-predicted $\theta$ distribution (i.e., factor scores) and its associated standard errors.
+If item discrimination (*a*) and thresholds (*b*) we showed earlier reflect *item parameters*, then the estimated $\theta$ or factor scores we compute here are the *person parameters*, since they represent each participant's "position" on the $\theta$ continuum.
+To compute empirical reliability, one needs to calculate the estimated $\theta$ value, and its associated standard errors, of each participant first, and then, calculate empirical reliability based on these values.
 To do this, readers can run these two lines of codes:
@@
 
-The `fscores()` function is used to compute the estimated $\theta$ value for each participant predicted by the `fit` model.
-The `full.scores.SE` is set to `TRUE` because the package uses the $\theta$ value and standard error of each participant (*SE*$\theta$) to compute the empirical reliability.
-We store the estimated $\theta$ and its *SE*$\theta$ in a new data frame, namely `theta_se`, and then run `empirical_rxx()` function to calculate empirical reliability.
-The output of these codes is `r e_rel`, which is very close to marginal reliability we estimated before.
-Notably, while marginal and empirical reliability aim to quantify the overall reliability of the scale, they base the calculations on different assumptions.
-To summarize, marginal reliability assumes that $\theta$ is normally distributed while empirical reliability uses the $\theta$ distribution predicted by the model, which still contains measurement error yet more realistic.
+The output of these codes is `r e_rel`, which is rather close to marginal reliability we estimated before.
+This implies that RWA scale is overall highly reliable in measuring RWA trait across all participants in the sample.
+Generally, reliability analysis aligns with the IPFs and IIFs we saw in the previous step, i.e., the RWA scale is highly reliable overall, but works best to measure the RWA construct across participants with RWA levels between ~2*SD* below the mean and ~3*SD* above the mean.
 
@@
 
-Construct validation is an ongoing process [@messickValidityPsychologicalAssessment1995], so reporting evidence of validity should always be an important part of the routine.
-In practice, however, researchers are less interested in examining the performance of the measures they use in their study, making it difficult to assess the credibility of their research findings [@flakeConstructValidationSocial2017; @husseyHiddenInvalidity152020].
-In this tutorial, we demonstrate the applicability of GRM analysis as part of the IRT family to help applied psychology researchers assess their measurement quality.
-We provide a non-technical guide to implementing a GRM analysis through a simple 7-step process using a real, openly available dataset.
-To maximize the effectiveness of this tutorial, we show how to perform a GRM analysis using R [@rcoreteamLanguageEnvironmentStatistical2023], an open source statistical software, and make all materials publicly available.
+In this tutorial, we have demonstrated the applicability of GRM analysis as part of the IRT family to help applied psychology researchers assess their measurement quality.
+We provide a non-technical guide to implementing a GRM analysis through a simple 6-step process using a real, openly available dataset.
+To maximize the effectiveness of this tutorial, we show how to perform a GRM analysis using R, an open-source statistical software, and make all materials publicly available.
 
-We begin the tutorial with a theoretical overview of IRT, which underlies GRM, so that readers can relate the practical steps to the theory behind the analysis.
-Since IRT is less popular than CTT, we also briefly explain how IRT differs from CTT in its assumptions.
-However, we want to emphasize that our goal here is not to argue for the superiority of CTT over IRT, since the choice of analytic tool depends largely on the specific research question at hand.
-It is important to highlight that researchers should be aware of the merits and limitations of their chosen methods.
+We begin the tutorial with a theoretical overview of IRT, which underlies GRM, so that readers can relate the practical steps to the theory behind the analysis, including an explanation of how IRT differs from CTT in its assumptions.
+In general, GRM offers several benefits and is useful as a complement to CTT analysis, especially when researchers focus on closely examining the precision of their measures at the item and person levels.
+However, we emphasize that our goal here is not to argue for the superiority of IRT over CTT, as the choice of analytic tool depends largely on the specific research question at hand.
+It is important to emphasize that researchers should be aware of the merits and limitations of their chosen methods.
 Therefore, researchers should always justify why they choose a particular method over many available alternatives.
 
-Note that the model we estimated has a poor fit, perhaps due to local dependency, as we showed in steps 4 and 5.
-In practice, we recommend addressing model fitting issues before interpreting measurement precision or drawing substantive conclusions based on these estimates.
-One solution is to rephrase or to combine the content of the problematic items that indicate local dependency.
-Alternatively, readers may need to reconsider the $\theta$ structure.
-If the data is unidimensional but some of the items are locally dependent, this may indicate the existence of multiple $\theta$ within the data structure.
-In this sense, modeling the test data as a correlated multidimensional model or a bifactor model (i.e., multidimensional models with a *g* factor) may be a solution, given that a previous study shows that the RWA scale is multidimensional [@duckittMultidimensionalityRightWingAuthoritarian2013].
-Removing locally dependent items should be a last resort, as it may improve model fit but may also compromise measurement precision.
+We have described the process of conducting a GRM analysis, starting with testing dimensionality, fitting the model, calculating and plotting item parameters, and calculating scale reliability.
+To help readers intuitively understand the process, we have summarized the steps we demonstrate in this tutorial in an annotated flowchart ({apafg-fig7}).
 
-Finally, we support the call for psychological researchers to shift their focus from improving their methodological practices to advancing the process of theory building [@eronenTheoryCrisisPsychology2021; @grahekAnatomyPsychologicalTheory2021; @proulxStatisticalRitualTheory2021], because formulating a sound theory always precedes the creation of a high-quality psychological measure.
-It is important to note, however, that construct validation is a critical step in the iterative process of theorizing a psychological phenomenon [@grahekAnatomyPsychologicalTheory2021].
-Therefore, we encourage applied psychology researchers to report evidence of measurement quality to ensure the validity of their findings and contribute to cumulative psychological science [@floraPurposePracticeExploratory2017].
-One way to do this is to conduct and report a GRM analysis of their measures.
-We hope that this tutorial can be seen as a small step towards the larger goal of building robust psychological science.
+{{< pagebreak >}}
+
+```{r}
+#| label: apafg-fig7
+#| apa-cap: An Annotated Flowchart Depicting the Process of Fitting A GRM Model
+#| apa-note: NULL
+#| output: true
+#| echo: false
+
+knitr::include_graphics("flowchart.png")
+```
+
+{{< pagebreak >}}
+
+Note that the model we estimate does not fit the data perfectly due to local dependency, as we showed in steps #3 and #4.
+If researchers encounter this problem when evaluating their scale data, we recommend tentatively rejecting the model and then locating the source of the model misfit before interpreting measurement precision or drawing substantive conclusions based on these estimates [@klinePrinciplesPracticeStructural2023].
+In doing so, researchers can take a closer look at residual correlations to identify the source and magnitude of misfit [@klinePrinciplesPracticeStructural2023; @maydeu-olivaresEvaluatingFitIRT2015].
+
+Once the sources of misfit are identified, one solution to address them is to rephrase or combine the content of the problematic, locally dependent items and then cross-validate the modified scale on another sample.
+Alternatively, researchers may need to reconsider the $\theta$ structure.
+If the data are unidimensional, but some of the items are locally dependent, this may indicate the existence of multiple $\theta$ within the data structure.
+In this sense, modeling the test data as a correlated multidimensional model or a bifactor model (i.e., multidimensional models with a *g* factor) may be a viable solution.
+Another solution to consider is to group locally dependent items by modeling them together as a "testlet" [@cookComparisonThreePolytomous1999], or to combine locally dependent items into a single composite score (i.e., item parceling), especially when the goal of the analysis is to understand the construct being measured rather than to identify the relationship between items and the $\theta$ [@littleWhyItemsParcels2013].
+Removing locally dependent items should be a last resort, as it may improve model fit, but can jeopardize measurement precision.
+
+Finally, while it is important to acknowledge that while a poorly fitted model may result in biased parameters, in reality, no IRT model can be expected to fit the data perfectly [@maydeu-olivaresEvaluatingFitIRT2015].
+That said, some models may be useful even if they are wrong to some degree [@boxScienceStatistics1976].
+Therefore, researchers are encouraged to not only evaluate the overall fit of their model, but also perform a piece-wise evaluation in some parts of their model [@maydeu-olivaresEvaluatingFitIRT2015] to get a comprehensive picture of the performance of their measures.
 

### 2024-08-19 annotated_codes_for_review.R

@@ -1,12 +1,17 @@
-# Tutorial on running a Graded Response Model, initiated on 09.11.2023
+# Tutorial on running a Graded Response Model, revised on 06.08.2024
 
 # Welcome to the tutorial!  ------
 # This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
 # or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
 # examining the performance of a scale with polytomous responses (Likert-type scale).
 
-# To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
+# To this end, in the first part, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
 # the right-wing authoritarianism (RWA) scale (Altemeyer). 
+
+# And in the second part, we will show you how to run a GRM using a simulated dataset.
+# To optimally use this material, we strongly recommend to go through the first part (RWA) and then the second part (simulated data).
+
+##### THE FIRST PART: RWA SCALE ----
 
 ## Step 1a: Preparation - Install and activate the packages ##  ------
 
@@ -301,6 +306,37 @@ omega(rwa) # This script computes several reliability coefficients
 # As we see here, the RWA scale is internally consistent.
 
 om <- omega(rwa)
+
+
+
+##### THE SECOND PART: SIMULATED DATASET ----
+
+# To give readers a clearer picture of the implementation of GRM, in the second part, we would like to demonstrate 
+# how to simulate a dataset using `simdata()` function in `mirt` package. 
+# We will simulate a dataset which contains RWA so that readers can compare the first and the second part.
+# Simulating a data set should always start with specifying the parameters, and to that end, let's use the parameters
+# that we have estimated in the first part.
+
+
+## Step 1: Simulate the dataset using `mirt` package ## ----
+
+sim_data <- simdata(model=fit, N=800); sim_data <- as.data.frame(sim_data)
+
+sim_model <- 'rwa=1-22'
+
+fit_sim <- mirt(data=sim_data, 1, model=model, itemtype="graded", SE=T, verbose=F)
+
+summary(fit_sim)
+
+itemfit(fit_sim)
+
+M2(fit_sim, type="C2")
+
+## Step 2: Examining dimensionality ## ----
+## Step 3: Model estimation, parameters, and fit statistics ## ----
+## Step 4: Inspecting residuals ## ----
[…]

### 2024-08-19 annotated_codes_for_review.R
delete everything

@@ -1,343 +1,0 @@
-# Tutorial on running a Graded Response Model, revised on 06.08.2024
-
-# Welcome to the tutorial!  ------
-# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
-# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
-# examining the performance of a scale with polytomous responses (Likert-type scale).
-
-# To this end, in the first part, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
-# the right-wing authoritarianism (RWA) scale (Altemeyer). 
-
-# And in the second part, we will show you how to run a GRM using a simulated dataset.
-# To optimally use this material, we strongly recommend to go through the first part (RWA) and then the second part (simulated data).
-
-##### THE FIRST PART: RWA SCALE ----
-
-## Step 1a: Preparation - Install and activate the packages ##  ------
-
-# First of all, we should install the packages we need for the analysis. If you already have these packages  
-# already installed in your device, you can safely skip this step.
-
-# install.packages("tidyverse", # for data wrangling
-# "psych", # for descriptive statistics and unidimensionality test
-# "devtools", # for installing R package that is not available on CRAN
-# "mirt", # for conducting the main GRM analysis
-# "caret", # for helping us detecting large residuals correlation (local independence test)
-# dependencies=TRUE)
-
-## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
-
-devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
-
-# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
-
-devtools::install_github("masurp/ggmirt")
-
-# Now, we activate the package:
-
-library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
-
-## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
-
-# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
-# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
-
-url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
-
[…]

### 2024-08-19 annotated_codes.Rmd
Revision round 1

---
title: "Tutorial on running a Graded Response Model"
author: "Rizqy Amelia Zein & Muhamad Hanif Akhtar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome to the tutorial!

This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for examining the performance of a scale with polytomous responses (Likert-type scale).

To this end, in ***the first part***, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically the right-wing authoritarianism (RWA) scale (Altemeyer). In ***the second part***, we will show you how to run a GRM using a simulated dataset.

To optimally use this material, we strongly recommend to go through the first part (RWA) and then the second part (simulated data).

## THE FIRST PART: RWA Scale

### Step 1a: Preparation - Install and activate the packages

First of all, we should install the packages we need for the analysis. If you already have these packages already installed in your device, you can safely skip this step.

```{r, include=FALSE}
install.packages("tidyverse", # for data wrangling
"psych", # for descriptive statistics and unidimensionality test
"devtools", # for installing R package that is not available on CRAN
"mirt", # for conducting the main GRM analysis
"caret", # for helping us detecting large residuals correlation (local independence test)
dependencies=TRUE)
```

Run the above codes only if you have not had them installed.

Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.

```{r, include=FALSE}
devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
devtools::install_github("masurp/ggmirt")
```

Now, we activate the package.

```{r, include=FALSE}
library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
```

### Step 1b: Preparation - Downloading, storing, and preparing the data for analysis

Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically download the file from the Open Psychometric database. You can always adjust these codes according to your needs.

```{r}
url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
```

If you look closely at the .zip folder, there are two files in there; one is a `.csv` file (this is the dataset), and two, a `.txt` file (a codebook). Since we need them both, we will extract them and make them readable in R environment.

```{r}
zip <- tempfile(fileext = ".zip") # Defining the path to temporarily save the downloaded zip file
download.file(url, zip, mode = "wb") # Downloading the zip file
do <- tempdir() # Defining the path to extract the contents of the zip file
unzip(zip, exdir = do) # Unzipping the .zip file
files <- list.files(do, recursive = TRUE, full.names = TRUE) # List all the files in the extracted directory, including subdirectories

csv <- grep("\\.csv$", files, value = TRUE) # Filtering for .csv files
txt <- grep("\\.txt$", files, value = TRUE) # Filtering for .txt files

if (length(csv) == 0) {
  stop("no .csv found")
} # now checking if there are any .csv files, and if that's the case, the script gives no error message

if (length(txt) == 0) {
  stop("no .txt found")
} # do the same thing for .txt file

ds <- read.csv(csv[1]) # Importing the .csv file.
codebook <- readLines(txt[1]) # Importing the .txt file.

unlink(zip)
unlink(do, recursive = TRUE)
rm(csv, txt, do, files, url, zip)
# This three lines of script are used to clean up the temporary files and values remaining in the R environment

str(ds) # Now we are checking the structure of data frame "ds", which contains our data so that we can work with it!
```

By looking at the structure, it's very likely that columns "Q1-Q22" are RWA items, because RWA consists of 22 items. but let's check the code book just to make sure...

```{r}
print(codebook)
```

If we look at the codebook, columns "Q1-Q22" indeed are the RWA data (see line 5-7), so our next step is to create a new data frame that contains only RWA items because this what we are interested in.

```{r}
data <- subset(ds, select = Q1:Q22) # now we subset our data because we are only interested in RWA items.
rm(codebook) # now we delete the codebook since we no longer need it.
```

After executing this line of code above, we shall see in the R environment that we have a new data frame, namely `data`, which contains of 22 columns (variable) and 9881 data points (participants).

Now let's check the structure of our new data frame containing only RWA items.

```{r}
str(data)
```

The structure seems correct, so we can proceed to the next step.

### Step 2: Inspecting key descriptive statistics

This part is fairly straightforward. Before performing analysis, it is very important to explore key descriptive statistics of the data. We are using a neat function in `psych` package: (`describe()`)

```{r}
describe(data)
```

Why there are `0` values in all columns (see column `min`)? The items are not supposed to have `0` value because the responses are ranging from 1-9.

Let's count how many `0` we have in our data.

```{r}
zero <- colSums(data == 0) / nrow(data) * 100 # Computing the percentage of "0" in each column.
print(zero) # Showing the percentage of "0" for each item.
rm(zero) # Removing the unused vector
```

We have a few cases with `0` in all items. There is no explanation what `0` means in the codebook, but it is very likely that `0` is used to code a missing response. It is actually still possible to run an IRT analysis with missing data, but we have to ensure that the data are missing at random (MAR). One solution for this is simply exclude all cases with missing responses.

Let's assume then that `0` means missing response, and then delete all cases with missing responses.

```{r}
data <- data %>%
  mutate_all(~na_if(., 0)) %>%  # Replacing 0 with NA in all columns.
  drop_na()  # Removing cases with any NA values.

describe(data)
```

As we see here, mean score of the items differ - some items have small mean scores (\~2-3), while the others are quite large (\~6-7). The reason for this is that the RWA scale has unfavorable items so to simplify the interpretation, we should reverse their scores.

Unfavorable items are Q4, Q6, Q8, Q9, Q11, Q13, Q15, Q18, Q20, and Q21

```{r}
unfav <- c("Q4","Q6","Q8","Q9","Q11","Q13","Q15","Q18","Q20","Q21") # Now we create a vector defining which items will be coded reversely.
data <- data %>% 
  mutate(across(all_of(unfav), ~ 10 - .))# We simply subtract the scores from 9 (the maximum) + 1 
# to reverse code the unfavorable items.
rm(unfav) # We don't need the vector, so we remove it now to keep our workspace clean.
```

Then let's check our data again.

```{r}
describe(data)
```

Now all cases with missing responses have been excluded, and unfavorable items have been reverse scored but we lost a few proportion of our sample. Losing some cases is indeed a downside of our decision, but we since it is unclear what `0` means (it is safer to assume that it a code for missing responses) and we still have a sizeable sample (\>9000), let's proceed to the next step!

### Step 3: Examining dimensionality

While now it is computationally possible to run a multidimensional IRT analysis, in general, an IRT model assumes that the scale is unidimensional. Bob Altemeyer (1996) argues in his book that while the RWA scale consists of three sub-dimensions, which are submissiveness, aggression, and conventionalism, the RWA scale is essentially unidimensional because these three sub-dimensions are strongly intercorrelated. Therefore, we may assume that the scale is supposed to be unidimensional.

To check the unidimensionality of the RWA scale, we can implement two approaches:

First, we can run an exploratory factor analysis (EFA) using a polychoric correlation matrix. This approach is generally recommended if we have a Likert scale with 4-7 possible responses. This can be neatly done using a simple script (`psych`) below:

```{r}
irt.fa(data, nfactors = 1, fm = "minres")
```

The option `fm = "minres"` implies that we choose minimum residual as a factoring method due to its effectiveness in handling non-normally distributed data. However, as we see in the console, there is an error message telling us that R stopped the analysis. This is because performing parallel analysis or EFA using a polychoric correlation matrix is not needed when we have more than 8 categories (responses) in our scale. This means we can treat our data as continuous (instead of ordinal). Since the RWA scale has nine responses, let's do EFA and parallel analysis manually using a correlation matrix instead.

Before running an EFA, we need to check whether our data is normally distributed by calling this command:

```{r}
skim(data)
```

As seen in the console, the function creates an intuitive visualization of data distribution (look at `hist` column in the right), which shows that our data is heavily skewed. Therefore, we could use a Spearman's correlation matrix as an input for our EFA.

```{r}
cor <- cor(data, method="spearman") # First, creating a (spearman) correlation matrix.
efa <- fa(cor, nfactors=1, fm="minres") # Now, running exploratory factor analysis. 
print(efa) # Print the results.
```

Let's look at the output.

MR1 reflects factor loadings of each item. As we see, all items are strongly loaded to the single factor. The rule of thumb is `0.3`, and we can see here all the loadings are more than `0.3`. We also see that the proportion of total variance that is explained by the factor (see `Proportion Var`) shows `0.56`, this means that the factor accounts for a significant portion (56%) of the variance of the data. In general, our assumption regarding the unidimensionality of the RWA scale holds, but to paint a clearer picture, let's look at the scree plot.

```{r}
plot(efa$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
```

The first line of code is a function to plot the eigenvalues (`efa$values`, x-axis) given the number of latent factors (y-axis). The option `type = "b"` implies that we ask R to plot the eigenvalues at exact points and a line connecting these points along the number of factors. The second line of code aims to display a horizontal red line (i.e., a reference line) to see which factors have eigenvalues greater than one, which is a common criterion for factor retention.

As we see in the plot, the eigenvalue significantly levels off after one factor, which further substantiates our assumption.

In a case where we are unsure about the number of possible factors underlying the data, we can run a parallel analysis also with a polychoric correlation matrix. This approach is, in general, better than EFA because a parallel analysis compares eigenvalues (a scalar which measures the amount of variance that is accounted for by each latent factor) from a set of simulated data with eigenvalues of our data. As recommended by @guoAssessingDimensionalityIRT2023, we will also use principal component analysis (`fa="pc"`). Again, to perform this, we need to run a simple command:

```{r}
fa.parallel(data, fm="minres", fa="pc")
```

Here, we use minimum residuals (`minres`) algorithm to extract/identify latent factors because it is considered suitable for dealing with non-normally distributed data. Parallel analysis shows that 2 components are suggested. Then what if we run EFA again, now with two latent factors as an assumption?

```{r}
efa <- fa(cor, nfactors=2, fm="minres") # Running exploratory factor analysis with 2 factors. 
print(efa) # Print the results.
```

### Step 4: Model estimation, parameters, and fit statistics

We have evidence that the scale is unidimensional, now it is the time to estimate our model. As the first step, let's define our model:

```{r}
model <- 'theta = 1-22' # This script means that our model consists of a latent factor namely theta
# and consists of 22 items (column 1 to column 22).
```

Now, we estimate our model...

```{r}
fit <- mirt(data=data, 1, model=model, itemtype="graded", SE=T, verbose=F) # This script means we're running a GRM analysis by assuming that the RWA scale as a unidimensional construct 
```

The number `1` indicates that we assume that the model contains only one $\theta$, i.e., unidimensional. We also set the model specification to `model = model`, which we have previously determined. We set `itemtype` to `"graded"` because we want to run a GRM model. The `SE` option is set to `TRUE` because we ask R to also estimate the standard error. At last, we set the `verbose` option to `FALSE` to avoid R displaying unnecessary information during the model fitting process, so the `mirt()` function can run quietly.

Now we store the model parameters in a data frame.

```{r}
coefs <- coef(fit, IRTpars=T, simplify=T) # Storing model parameters in a data frame.
```

The first line of code indicates that we are calling a `coef()` function to calculate item parameters from `fit` model, and then, store them in a new data frame called `coefs`. The `IRTpars` and `simplify` option is set to `TRUE` because we want to display the traditional IRT parameters (*a* and *b*) in a simple, readable format without showing the standard errors.

Let's take a closer look at the model parameters!

```{r}
print(coefs) # Yielding model parameters: item discrimination (a) and threshold (b).
```

Now we can see item discrimination (a), which indicates how well an item differentiates participant with different levels of authoritarian personality. To interpret this, we could use a guideline from Baker (2017). RWA items, in general, have a moderate to very high ability to differentiate participants with different theta levels. We can see that most items have 8 item threshold each (b1-b8), and this is because we have nine response options.

```{r}
summary(fit) # Displaying factor loadings and commonality.
```

Before estimating a graded response model, `mirt` ran an EFA, and now as we can see in the console, we are looking at the EFA results. The results are slightly different from our previous EFA analysis, because `mirt` runs EFA using a quasi polychoric correlation matrix, while the one we ran earlier used a pearson correlation matrix. However, most importantly, we see that all items are significantly loaded to one factor, and the factor now substantially accounts for 65.1% of the variance in the data, which strengthens our assumption that the RWA scale is unidimensional.

Now, let's look at the (model and item) fit statistics

```{r}
M2(fit, type="C2") # Running model fit analysis.
```

Apparently, our model, overall, does not fit well with the data. Could it be a problem of model misspecification?

```{r}
itemfit(fit) # Yielding item fit statistics.
```

Looking at RMSEA and p values of the scaled X2 statistics, we can see here that only Q2, Q4, and Q12 fit to our data.

Taking account the model and item fit statistics, it is very likely that we have problems with our model. It could be a problem of model misspecification, or something else. We can identify potential problems by looking at local dependency statistics (Step 6) and the plots (Step 7).

### Step 5: Probing model misspecification by examining residuals

While we have evidence that the RWA scale is unidimensional, our model does not fit well with the data. Therefore, it is reasonable to suspect that our model is locally dependent, thus violating IRT assumption.

We will then further examine the possibility of model misspecification by looking at model residuals. In this tutorial, we will introduce two ways to examine residuals. First, we will inspect a local dependence matrix derived from the X2 statistics (Chen & Thissen, 1997), and second, we will look at Yen's Q3 statistics.

```{r}
ld <- residuals(fit, type = "LD") # Running local dependency (LD) statistics.
up <- which(upper.tri(ld), arr.ind = T) # Creating a new matrix containing values only on the upper side of the diagonal (correlations).
lar <- up[ld[up] > 0.2 | ld[up] < -0.2, ] # A vector defining unusually large residuals ( > |0.2|).

for (i in 1:nrow(lar)) {
  row <- lar[i, 1]
  col <- lar[i, 2]
  value <- ld[row, col]
  cat(sprintf("A large residual correlation is found between item %d and item %d: %f\n", row, col, value))
} # Now we detect the problematic pairs.
```

According to this, it seems that there is no local dependency. Let's see how Yen's Q3 statistics look like.

```{r}
q3 <- residuals(fit, type = "Q3") # Running Yen's Q3 statistics
findCorrelation(q3, cutoff = 0.2, verbose = T) # Flagging problematic item pairwise correlations.
```

This code asks R to run `residuals()` function with `"Q3"` as the `type`, and then keep the value as a new matrix, namely `q3`.

As we see here in the console that items Q3, Q4, Q5, Q7, Q11, Q13, Q14, Q18, Q19, and Q21 are problematic.

### Step 6: Plots (item characteristics curve, item information curve, and test information curve)

From the previous step, we found some problems with model misspecification. Let's take a look at the curves to closely examine the items.

```{r}
# Plotting Item Probability Functions (CPF)
tracePlot(fit, title = "Item Probability Functions of RWA Scale") + labs(color="Response Categories")
```

The `labs(color)` function is to assign different colors to each curve representing a response category.

All CPFs of RWA items seem to be significantly overlapping, and are peaked on the right side of the curves. This implies that RWA items are more sensitive to differentiate participants with high levels of authoritarian personality.

```{r}
# Plotting Item Information Curve (IIC).
itemInfoPlot(fit, facet = TRUE, title = "Item Information Functions of the RWA Scale")
```

The `facet` option is set to `TRUE` so that R displays IIF for each item. Some items (Q1, Q5, Q6, Q8, Q9, Q11) seem to yield the least information compared to other items.

```{r}
# Plotting Test Information Curve.
testInfoPlot(fit, title="Test Information Function of the RWA Scale")
```

Apparently, the RWA scale is informative to measure participants with theta levels between -2SD to +4SD.

### Step 7: Computing reliability

At last, we want to examine the reliability of the RWA scale. In IRT, there are two ways to estimate reliability, which are: marginal and empirical reliability.

To calculate empirical reliability, we have to compute participants' theta (factor scores) estimated by the model. To do this, we only need to run a simple script below:

```{r}
theta_se <- fscores(fit, full.scores.SE = T) # Extracting the estimated theta score of each participant.
```

The `fscores()` function is used to compute the estimated $\theta$ value for each participant predicted by the `fit` model. The `full.scores.SE` is set to `TRUE` because the package uses the $\theta$ value and standard error of each participant (*SE*$\theta$) to compute the empirical reliability. We store the estimated $\theta$ and its *SE*$\theta$ in a new data frame, namely `theta_se`. And then, we can use the estimated theta to compute empirical reliability.

```{r}
empirical_rxx(theta_se) # Then use the estimated theta to calculate empirical reliability.
```

Reliability seems to be pretty good. Now, we need to calculate marginal reliability.

```{r}
marginal_rxx(fit) # Calculating marginal reliability.
# Marginal reliability is almost similar to empirical reliability.
```

...and then plot the marginal reliability across the latent trait spectrum.

```{r}
conRelPlot(fit, title="Reliability of the RWA Scale Given to the θ Level")
```

The RWA scale seems to be optimal (having sufficient reliability, \~0.75) for measuring participants with theta levels between -2SD and +4SD.

Let's compare IRT-based reliability and unweighted sum-score based reliability.

```{r}
omega(data) # This script computes several reliability coefficients
```

As we see here, the RWA scale is internally consistent.

## THE SECOND PART: Simulated Dataset

To give readers a clearer picture of the implementation of GRM, in the second part, we will demonstrate how to simulate a dataset using `simdata()` function in `mirt` package. We will simulate a new dataset using model and item parameters that we estimated with the real data in **the first part** so that readers can compare the first (real) and the second (ideal) model.

### Step 1: Simulate the dataset using `mirt` package

Simulating a data set should always start with specifying the parameters, and to that end, we will replicate a dataset using model and item parameters that we have estimated in **the first part**. `mirt` package also provides the option to simulate response patterns (i.e., scale data) from a custom input matrix of theta, but we don't include the example here in the material. Those who are interested in simulating response patterns from a custom theta matrix are advised to read the examples provided in [`mirt` documentation](https://cran.r-project.org/web/packages/mirt/mirt.pdf).

It's important to remember that the simulated data is constructed by strictly adhering to the model assumptions and parameters. Therefore, model and item parameters here are just statistical artifacts that should not be taken at face value. The purpose of implementing GRM with simulated data here is to show how the "ideal" scenario looks like.

To simulate response patterns from estimated RWA model we have shown in the first part, type the codes below.

```{r}
sim_data <- simdata(model=fit, N=800) # simulating 800 response patterns from RWA scale we previously estimated in the first part
sim_data <- as.data.frame(sim_data) # and then set the data to a data frame
```

We now have a newly created data frame, `sim_data`, containing 800 response patterns estimated from the model and item parameters we already had.

Now, let's take a glimpse at the dataset.

```{r}
describe(sim_data) # descriptive stats of items in the dataset
```

The items look good and are coded correctly. We don't need to reverse any items because our dataset is built upon a GRM model estimated from a cleaned dataset.

Then we can continue to examine the dimensionality of the simulated dataset.

### Step 2: Examining dimensionality

In the first part, we saw that `irt.fa()` and factor analysis with polychoric correlations are not needed when response categories of the scale are more than 8. Therefore, we will examine the dimensionality by running an exploratory factor analysis, just as we did in the previous part.

```{r}
cor_sim <- cor(sim_data, method="spearman") # First, creating a (Spearman) correlation matrix.
efa_sim <- fa(cor_sim, nfactors=1, fm="minres") # Now, running exploratory factor analysis. 
print(efa_sim) # Print the results.
```

Let's take a closer look at the output.

Note that the simulated response patterns are a different set of data than we had in the first part, even though they were constructed using the model and item parameters estimated in the first part. Therefore, the numbers here are changed, but as we can see here, the unidimensionality evidence remains. All items are loaded strongly on to one latent dimension as no loadings are smaller than `0.3`. Proportion of total variance explained by the latent factor is `0.54`, which further shows that the simulated data is unidimensional.

```{r}
plot(efa_sim$values, type = "b", main = "Scree Plot", xlab = "Factor", ylab = "Eigenvalue") # Scree plot
abline(h = 1, col = "red", lty = 2) # Add new line to eigenvalue = 1.
```

As we can see in the plot, the eigenvalue levels off exactly after one factor, which further supports our assumption. However, let's do a parallel analysis as we did in the first part.

```{r}
pa <- fa.parallel(sim_data, nfactors = 1, fm="minres", fa="fa") # Running a parallel analysis.
pa$fa.values # Seeing the eigenvalues of each factor.
```

Again, from the plot and the eigenvalues (`11.9/0.21`), we can conclude that one latent factor is sufficient for the simulated data.

### Step 3: Model estimation, parameters, and fit statistics

```{r}
sim_model <- 'theta=1-22' # specifiying the model
fit_sim <- mirt(data=sim_data, 1, model=model, itemtype="graded", SE=T, verbose=F) # estimating the GRM model
summary(fit_sim) # # Displaying factor loadings and commonality.
```

Compared to the real dataset, the loadings here don't differ much. We can see here that all items are properly loaded on to a single latent factor. However, it's interesting to see if the overall model fit differs from the real dataset we analyzed in the first part.

```{r}
M2(fit_sim, type="C2")
```

As we can see here, the model fit indices appear to be perfect, unlike the previous model we had.

Let's now look at the item fit indices by running this simple command below.

```{r}
itemfit(fit_sim)
```

Similarly, the item fit indices appear to be perfect. All RMSEA values are below `0.08` and the *p* values are also above `0.05`. Of course, this is not surprising since we are analyzing simulated response patterns, not a real data.

Next, we will look at the IRT plots as we did in the previous part. We will skip the residual analysis part because it is not necessary since the model we estimated here is *near* perfect.

### Step 4: Plots (item characteristics curve, item information curve, and test information curve)

To examine the items in detail, we can start by plotting the item probability functions by running the following line of code.

```{r}
# Plotting Item Probability Functions (CPF)
tracePlot(fit_sim, title = "Item Probability Functions of the Simulated Dataset") + labs(color="Response Categories")
```

Similarly, the CPFs overlap significantly and peak on the right side of the curves. This suggests that our simulated dataset reflects the real dataset, in which items are more sensitive to discriminating participants with high theta, but much less sensitive to discriminating participants whose theta is below the mean.

```{r}
# Plotting Item Information Curve (IIC).
itemInfoPlot(fit_sim, facet = TRUE, title = "Item Information Functions of the Simulated Dataset")
```

Similar to the real data, some items (Q1, Q5, Q6, Q8, Q9, Q11, Q20) seem to yield the least information compared to other items.

Now let's see what happens when we combine item information functions into a test information function.

```{r}
# Plotting Test Information Curve.
testInfoPlot(fit_sim, title="Test Information Function of the Simulated Dataset")
```

Similarly, the RWA scale is informative to measure participants with theta levels between -2SD to +4SD.

### Step 5: Computing reliability

At last, we want to examine the reliability of the RWA scale. In IRT, there are two ways to estimate reliability, which are: marginal and empirical reliability.

To calculate empirical reliability, we have to compute participants' theta (factor scores) estimated by the model. To do this, we only need to run a simple script below:

```{r}
theta_se_sim <- fscores(fit_sim, full.scores.SE = T) # Extracting the estimated theta score of each participant.
empirical_rxx(theta_se_sim) # Then use the estimated theta to calculate empirical reliability.
```

Reliability is slightly different from the real data, but still pretty good.

Now, we need to calculate marginal reliability and then plot the marginal reliability across the latent trait spectrum.

```{r}
marginal_rxx(fit_sim) # Calculating marginal reliability.
conRelPlot(fit_sim, title="Reliability of the Simulated Dataset Given to the θ Level")
```

The simulated data shows the same pattern as the real one, which shows that the scale as a whole is optimal (having sufficient reliability, \~0.8) for measuring participants with theta levels between -2SD and +4SD.

Thank you for getting through this tutorial until the very end! We hope that this tutorial is useful!

If you have any feedback, please get in touch and let us know by email here: [amelia.zein\@psikologi.unair.ac.id](mailto:amelia.zein@psikologi.unair.ac.id).

# Session Info

```{r}
sessionInfo()
```

### 2024-08-19 manuscript.qmd
Revision round 1

@@
 | Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-|-----------------|--------------------|-----------------|-----------------|
+|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
 | 1-PL Model (Rasch Model)    | 1\.
@@
 This implies that RWA scale is overall highly reliable in measuring RWA trait across all participants in the sample.
-Generally, reliability analysis aligns with the IPFs and IIFs we saw in the previous step, i.e., the RWA scale is highly reliable overall, but works best to measure the RWA construct across participants with RWA levels between ~2*SD* below the mean and ~3*SD* above the mean.
+Generally, reliability analysis aligns with the IPFs and IIFs we saw in the previous step, i.e., the RWA scale is highly reliable overall, but works best to measure the RWA construct across participants with RWA levels between \~2*SD* below the mean and \~3*SD* above the mean.
 

### 2024-08-19 annotated_codes.R

@@ -1,0 +1,309 @@
+# Tutorial on running a Graded Response Model, initiated on 09.11.2023
+# by Rizqy Amelia Zein and Hanif Akhtar
+# LMU Munich, Universitas Airlangga (UNAIR), ELTE Eötvös Loránd University, and Universitas Muhammadiyah Malang (UMM)
+
+# Welcome to the tutorial!  ------
+# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
+# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
+# examining the performance of a scale with polytomous responses (Likert-type scale).
+
+# To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
+# the right-wing authoritarianism (RWA) scale (Altemeyer). 
+
+## Step 1a: Preparation - Install and activate the packages ##  ------
+
+# First of all, we should install the packages we need for the analysis. If you already have these packages  
+# already installed in your device, you can safely skip this step.
+
+# install.packages("tidyverse", # for data wrangling
+# "psych", # for descriptive statistics and unidimensionality test
+# "devtools", # for installing R package that is not available on CRAN
+# "mirt", # for conducting the main GRM analysis
+# "caret", # for helping us detecting large residuals correlation (local independence test)
+# dependencies=TRUE)
+
+## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
+
+devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
+
+# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
+
+devtools::install_github("masurp/ggmirt")
+
+# Now, we activate the package:
+
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+
+## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
+
+# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
+# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
+
+url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
+
+# If you look closely at the .zip folder, there are two files in there; one is a .csv file (this is the dataset),
[…]

### 2024-08-19 annotated_codes_for_review.R

@@ -1,0 +1,343 @@
+# Tutorial on running a Graded Response Model, revised on 06.08.2024
+
+# Welcome to the tutorial!  ------
+# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
+# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
+# examining the performance of a scale with polytomous responses (Likert-type scale).
+
+# To this end, in the first part, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
+# the right-wing authoritarianism (RWA) scale (Altemeyer). 
+
+# And in the second part, we will show you how to run a GRM using a simulated dataset.
+# To optimally use this material, we strongly recommend to go through the first part (RWA) and then the second part (simulated data).
+
+##### THE FIRST PART: RWA SCALE ----
+
+## Step 1a: Preparation - Install and activate the packages ##  ------
+
+# First of all, we should install the packages we need for the analysis. If you already have these packages  
+# already installed in your device, you can safely skip this step.
+
+# install.packages("tidyverse", # for data wrangling
+# "psych", # for descriptive statistics and unidimensionality test
+# "devtools", # for installing R package that is not available on CRAN
+# "mirt", # for conducting the main GRM analysis
+# "caret", # for helping us detecting large residuals correlation (local independence test)
+# dependencies=TRUE)
+
+## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
+
+devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
+
+# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
+
+devtools::install_github("masurp/ggmirt")
+
+# Now, we activate the package:
+
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+
+## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
+
+# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
+# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
+
+url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
+
[…]

### 2024-08-27 annotated_codes_for_blind_review.Rmd
Revision 2 submitted

--- 2024-08-19 annotated_codes.Rmd
@@
 title: "Tutorial on running a Graded Response Model"
-author: "Rizqy Amelia Zein & Muhamad Hanif Akhtar"
+author: "Anonymized Authors"
 date: "`r Sys.Date()`"
@@
 "caret", # for helping us detecting large residuals correlation (local independence test)
+"skimr", # for visualizing data distribution in a data frame at glance
 dependencies=TRUE)
@@
 ```{r, include=FALSE}
-library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
+library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret); library(skimr)
 ```
@@
 
-After executing this line of code above, we shall see in the R environment that we have a new data frame, namely `data`, which contains of 22 columns (variable) and 9881 data points (participants).
+After executing this line of code above, we shall see in the R environment that we have a new data frame, namely `data`, which contains of 22 columns (variable) and 9,881 data points (participants).
 
@@
 As seen in the console, the function creates an intuitive visualization of data distribution (look at `hist` column in the right), which shows that our data is heavily skewed.
-Therefore, we could use a Spearman's correlation matrix as an input for our EFA.
+Therefore, we could use a Spearman correlation matrix as an input for our EFA.
 
@@
 To interpret this, we could use a guideline from Baker (2017).
-RWA items, in general, have a moderate to very high ability to differentiate participants with different theta levels.
+RWA items, in general, have a moderate to very high ability to differentiate participants with different $\theta$ levels.
 We can see that most items have 8 item threshold each (b1-b8), and this is because we have nine response options.
@@
 
-Apparently, the RWA scale is informative to measure participants with theta levels between -2SD to +4SD.
+Apparently, the RWA scale is informative to measure participants with $\theta$ levels between -2SD to +4SD.
 
@@
 
-To calculate empirical reliability, we have to compute participants' theta (factor scores) estimated by the model. To do this, we only need to run a simple script below:
+To calculate empirical reliability, we have to compute participants' $\theta$ (factor scores) estimated by the model. To do this, we only need to run a simple script below:
 
@@
 
-The RWA scale seems to be optimal (having sufficient reliability, \~0.75) for measuring participants with theta levels between -2SD and +4SD.
+The RWA scale seems to be optimal (having sufficient reliability, \~0.75) for measuring participants with $\theta$ levels between -2SD and +4SD.
 
@@
 Simulating a data set should always start with specifying the parameters, and to that end, we will replicate a dataset using model and item parameters that we have estimated in **the first part**.
-`mirt` package also provides the option to simulate response patterns (i.e., scale data) from a custom input matrix of theta, but we don't include the example here in the material.
-Those who are interested in simulating response patterns from a custom theta matrix are advised to read the examples provided in [`mirt` documentation](https://cran.r-project.org/web/packages/mirt/mirt.pdf).
+`mirt` package also provides the option to simulate response patterns (i.e., scale data) from a custom input matrix of $\theta$, but we don't include the example here in the material.
+Those who are interested in simulating response patterns from a custom $\theta$ matrix are advised to read the examples provided in [`mirt` documentation](https://cran.r-project.org/web/packages/mirt/mirt.pdf).
 
@@
 Similarly, the CPFs overlap significantly and peak on the right side of the curves.
-This suggests that our simulated dataset reflects the real dataset, in which items are more sensitive to discriminating participants with high theta, but much less sensitive to discriminating participants whose theta is below the mean.
+This suggests that our simulated dataset reflects the real dataset, in which items are more sensitive to discriminating participants with high theta, but much less sensitive to discriminating participants whose $\theta$ is below the mean.
 
@@
 
-Similarly, the RWA scale is informative to measure participants with theta levels between -2SD to +4SD.
+Similarly, the RWA scale is informative to measure participants with $\theta$ levels between -2SD to +4SD.
 
@@
 
-The simulated data shows the same pattern as the real one, which shows that the scale as a whole is optimal (having sufficient reliability, \~0.8) for measuring participants with theta levels between -2SD and +4SD.
+The simulated data shows the same pattern as the real one, which shows that the scale as a whole is optimal (having sufficient reliability, \~0.8) for measuring participants with $\theta$ levels between -2SD and +4SD.
 
@@
 
-If you have any feedback, please get in touch and let us know by email here: [amelia.zein\@psikologi.unair.ac.id](mailto:amelia.zein@psikologi.unair.ac.id).
+If you have any feedback, please get in touch and let us know by email here: [email anonymized].
 

### 2024-08-27 manuscript.qmd
Revision 2 submitted

@@
     orcid: 0000-0001-7840-0299
-    email: amelia.zein@psikologi.unair.ac.id
+    email: Amelia.Zein@psy.lmu.de
     affiliations:
@@
     affiliations:
-      - name: ELTE Eötvös Loránd University
-        department: Doctoral School of Psychology
-        country: Hungary
       - name: Universitas Muhammadiyah Malang
@@
   disclosures:
-    conflict-of-interest: "We declare we have no competing interests."
+    conflict-of-interest: "We declare that we have no competing interests."
     financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD), award number 91803023."
@@
 | Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
+|------------|-------------------------------------|------------|------------|
 | 1-PL Model (Rasch Model)    | 1\.
@@
 To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
-We also include a longer, annotated R Markdown file (.Rmd) for the example we used as a supplementary document, which we highly recommend to use for a didactic purpose.
+We also include a longer, annotated R Markdown file (.Rmd) for the example we used as a supplementary document, which we highly recommend using for a didactic purpose.
 In the same file, we also include a part where we demonstrate the application of GRM using a simulated dataset, which we do not include in the article, so that readers can compare the example we present here against an ideal scenario.

### 2024-10-24 annotated_codes.Rmd
final revision

@@
 title: "Tutorial on running a Graded Response Model"
-author: "Rizqy Amelia Zein & Muhamad Hanif Akhtar"
+author: "Rizqy Amelia Zein & Hanif Akhtar"
 date: "`r Sys.Date()`"
@@
 
-The simulated data shows the same pattern as the real one, which shows that the scale as a whole is optimal (having sufficient reliability, \~0.8) for measuring participants with theta levels between -2SD and +4SD.
+The simulated data shows the same pattern as the real one, which shows that the scale as a whole is optimal (having sufficient reliability, \~0.8) for measuring participants with $\theta$ levels between -2SD and +4SD.
+
+## Contact
 
@@
 
-If you have any feedback, please get in touch and let us know by email here: [amelia.zein\@psikologi.unair.ac.id](mailto:amelia.zein@psikologi.unair.ac.id).
+If you have any feedback or questions, please get in touch and let us know by email: [Amelia.Zein\@psy.lmu.de](mailto:Amelia.Zein@psy.lmu.de?subject=GRM%20Tutorial), [amelia.zein\@psikologi.unair.ac.id](mailto:amelia.zein@psikologi.unair.ac.id?subject=GRM%20Tutorial), or [hanifakhtar\@umm.ac.id](mailto:hanifakhtar@umm.ac.id?subject=GRM%20Tutorial).
 

### 2024-10-24 manuscript.qmd
final revision

@@
     conflict-of-interest: "We declare that we have no competing interests."
-    financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD), award number 91803023."
+    financial-support: "The first author receives a PhD scholarship from the German Academic Exchange Service (Deutscher Akademischer Austauschdienst, DAAD), award number 91803023, and thanks DAAD for its financial support."
 lang: en
@@
 | Model                       | Key Characteristics                                                                                                                                                                                                                                          | Data Type   | Response Options        |
-|------------|-------------------------------------|------------|------------|
+|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
 | 1-PL Model (Rasch Model)    | 1\.
@@
 
-To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document, where we integrate the R codes used in the analysis as well as its outputs.
+To maximize the reproducibility of our illustrative example, we wrote the article as a Quarto (.qmd) document [@schneiderWjschneApaquarto2024], where we integrate the R codes used in the analysis as well as its outputs.
 We also include a longer, annotated R Markdown file (.Rmd) for the example we used as a supplementary document, which we highly recommend using for a didactic purpose.
 In the same file, we also include a part where we demonstrate the application of GRM using a simulated dataset, which we do not include in the article, so that readers can compare the example we present here against an ideal scenario.
-The Quarto file (and its corresponding .docx and .pdf output) and an annotated R Markdown file are publicly available on [a Github repository]() (*unlinked for blind review*).
+The Quarto file (and its corresponding .docx and .pdf output) and an annotated R Markdown file are publicly available on [a Github repository](https://github.com/rameliaz/grm-tutorial-paper).
 The dataset we used in this tutorial paper was obtained from a publicly accessible [Open-Source Psychometrics Project](http://openpsychometrics.org/_rawdata/).
@@
 
-Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2023a; @chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023], *ggmirt* [@masurGgmirt2023], and *caret* [@kuhnCaretClassificationRegression2024], and *skimr* [@waringSkimrCompactFlexible2024] with these following commands:
+Before running the analysis, we need to install the necessary R packages, which are, *mirt* [@chalmersMirtMultidimensionalItem2012], *psych* [@revellePsychProceduresPsychological2023], *ggmirt* [@masurGgmirt2023], and *caret* [@kuhnCaretClassificationRegression2024], and *skimr* [@waringSkimrCompactFlexible2024] with these following commands:
 

### 2024-10-24 annotated_codes.R
remove submitted manuscript due to Wiley's policy

@@ -1,309 +1,0 @@
-# Tutorial on running a Graded Response Model, initiated on 09.11.2023
-# by Rizqy Amelia Zein and Hanif Akhtar
-# LMU Munich, Universitas Airlangga (UNAIR), ELTE Eötvös Loránd University, and Universitas Muhammadiyah Malang (UMM)
-
-# Welcome to the tutorial!  ------
-# This tutorial aims to familiarize applied psychological researchers to item response theory (IRT) modeling, 
-# or more specifically, a graded response model (GRM). GRM is a part of IRT family, specifically designed for
-# examining the performance of a scale with polytomous responses (Likert-type scale).
-
-# To this end, we will show you how to run a GRM, using data from the Open Psychometric Database, specifically 
-# the right-wing authoritarianism (RWA) scale (Altemeyer). 
-
-## Step 1a: Preparation - Install and activate the packages ##  ------
-
-# First of all, we should install the packages we need for the analysis. If you already have these packages  
-# already installed in your device, you can safely skip this step.
-
-# install.packages("tidyverse", # for data wrangling
-# "psych", # for descriptive statistics and unidimensionality test
-# "devtools", # for installing R package that is not available on CRAN
-# "mirt", # for conducting the main GRM analysis
-# "caret", # for helping us detecting large residuals correlation (local independence test)
-# dependencies=TRUE)
-
-## INFO: Remove the hashtag before install.package() to start installing packages (only if you have not had them installed) ##
-
-devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
-
-# Package `ggmirt` is not available in CRAN, so we have to do a remote installation by downloading the package from its Github repository.
-
-devtools::install_github("masurp/ggmirt")
-
-# Now, we activate the package:
-
-library(tidyverse); library(psych); library(mirt); library(ggmirt); library(caret)
-
-## Step 1b: Preparation - Downloading, storing, and preparing the data for analysis ##   ------
-
-# Before running our analysis, of course we should download our dataset first. Here, we have written codes to automatically
-# download the file from the Open Psychometric database. You can always adjust these codes according to your needs.
-
-url <- "https://openpsychometrics.org/_rawdata/RWAS.zip" # Defining the URL of the zip file
-
-# If you look closely at the .zip folder, there are two files in there; one is a .csv file (this is the dataset),
[…]

### 2025-01-14 manuscript.qmd
Adding link, vol, number to the bibtex entry in README

@@
 | Model | Key Characteristics | Data Type | Response Options |
-|-----------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------------|-------------------------|
+|----|----|----|----|
 | 1-PL Model (Rasch Model) | 1\.

### 2025-08-21 manuscript.qmd
{{< include _extensions -- is no longer needed with the new version of apaquarto

@@
   apaquarto-docx: default
-editor: visual
+editor: source
 execute: 
@@
 ---
-
-{{< include _extensions/wjschne/apaquarto/_apa_title.qmd >}}
 
@@
 | Model | Key Characteristics | Data Type | Response Options |
-|----|----|----|----|
+|------------------|------------------|------------------|------------------|
 | 1-PL Model (Rasch Model) | 1\.

### 2025-08-21 annotated_codes.Rmd
updated Rmd codes

@@
 In ***the second part***, we will show you how to run a GRM using a simulated dataset.
+
+This annotated R Markdown file is attached as supplementary material for the tutorial manuscript, which can be downloaded from our [Github repository](https://github.com/rameliaz/grm-tutorial-paper).
 
@@
 devtools::install_github("masurp/ggmirt") # remote ggmirt installation through GitHub repository
-devtools::install_github("masurp/ggmirt")
 ```
